### 2018-06-13 docs/mvfits_paper/mvf.tex
adding dev folder for documents

\documentclass[twocolumn,aps,prd,floatfix,preprintnumbers,a4paper,nofootinbib,
superscriptaddress,10pt]{revtex4-1}

\usepackage{epsfig}
\usepackage{graphics}
\usepackage{graphicx}
\usepackage{amsmath,amssymb,mathtools}
\usepackage{amsfonts}
\usepackage{bm,soul}
\usepackage[usenames,dvipsnames]{color}
\usepackage{amssymb}
\usepackage{url}
\usepackage{psfrag}
\usepackage{times}
\usepackage[varg]{txfonts}
\usepackage[colorlinks, pdfborder={0 0 0}]{hyperref}
\usepackage{lineno}
\usepackage{verbatim}
\definecolor{LinkColor}{rgb}{0.75, 0, 0}
\definecolor{CiteColor}{rgb}{0.75, 0, 0}
\definecolor{UrlColor}{rgb}{0, 0, 0.75}
\hypersetup{linkcolor=LinkColor}
\hypersetup{citecolor=CiteColor}
\hypersetup{urlcolor=UrlColor}
\usepackage[utf8]{inputenc}
\usepackage{ulem}
\normalem
\hoffset -0.17in
\voffset 0.3in
\textheight 10in

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Useful Definitions %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\input{src/definitions}
\def\check#1{\red{#1}}
\def\remove#1{\hlred{#1}}
\newcommand{\cw}{\tilde{\omega}}
\newcommand{\CW}{\tilde{\Omega}}
\newcommand{\CWr}{{\Omega}^{\mathrm{r}}}
\newcommand{\CWc}{{\Omega}^{\mathrm{c}}}
\newcommand{\SC}{\mathcal{K}}
\newcommand{\CC}{\mathcal{C}}
\newcommand{\SCr}{\mathcal{K}^{\mathrm{r}}}
\newcommand{\SCc}{\mathcal{K}^{\mathrm{c}}}
\newcommand{\lalapprox}{\texttt{MMRDNS}}
\def\jf{j_f}
\def\mf{M_f}
\newcommand{\LL}{\bar{l}}
\newcommand{\MM}{\bar{m}}
\def\lmn{_{\ell m n}}
\def\LM{_{\bar{\ell} \bar{m}}}
\def\LMlmn{_{\bar{\ell} \bar{m} \ell m n}}

\newcommand{\lmtitle}[2]{\vspace{-0.80cm} \begin{center} \noindent\rule{0.35\paperwidth}{0.3pt} \end{center} \vspace{-0.3cm}}

% Numbers that may change from time to time
\def\CwFitCalibrationRegion{\red{0.995} }
\def\NumCalibrationPointsPlotted{\red{21} }
\def\NumCalibrationPoints{\red{61} }

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Title page %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\title{Notes on modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients }

\author{L. T. London}
\affiliation{School of Physics and Astronomy, Cardiff University, The Parade, Cardiff, CF24 3AA, United Kingdom}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Abstract %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{abstract}
	%
	The ongoing direct detection of gravitational wave signals is aided by representative models of theoretical predictions. In particular, the process of model based detection, and subsequent comparison of signals the general relativity's predictions are aided by the modeling of information related to perturbed Kerr black holes. Here, we summarize recent methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
	%
\end{abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% Preprint numbers %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\preprint{LIGO-P1500185-v10}
\date{\today}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\maketitle

% \begin{itemize}
% 	\item BH detections happen, and use fits at various levels
% 	\item Fits for Kerr are important for modeling and testing GR, they are fast to eval comapred to formal calculations which has data analysis implications
% 	\item Many fits have been done for perturbative Kerr parameters: QNM frequencies most prominently.
% 	\item The problem/motivation:
% 		\begin{itemize}
% 			\item 1. There are many fits, and we would like to provide a reference for many of them, including key methods
% 			\item 2. Methods for fits: basis learning
% 			\item 3. (results) Summarize "simple fits": QNM frequencies and decay times, enforcing zero damping
% 			\item 4. (results) Summarize more general fits: mixing coefficients
% 		\end{itemize}
% 	\item (discussion) We have presented ...
% \end{itemize}

\paragraph*{Introduction -- }
%
In the coming years, expectations for frequent \gw{} detections of increasing \snr{} are high.
%
Concurrent with \virgo{}, the \aligo{} detectors will enter their third observing run in \check{late 2018}.
%
At this time, \bbh{} detections are expected at a rate of \check{X} per month.
%
In this context, signal detection and subsequent inference of physical parameters hinges upon efficient models for source properties and dynamics.
%
Most prominently, there is ongoing interest in signal models for \bbh{} \imr{}.
%
As the merger of isolated \bh{s} is expected to result in a perturbed Kerr \bh{}, there is related interest in having computationally efficient models for perturbative parameters, namely those that enable evaluation of the related \rd{} radiation.
%
\par In particular, a perturbed Kerr \bh{} (e.g. resulting from \bbh{} merger) will have \gw{} radiation that rings down with characteristic frequencies,
%
$%\begin{align}
	\cw\lmn = \omega\lmn + i/\tau\lmn
$%\end{align}
.
%
These discrete frequencies have associated radial and spatial functions which are \textit{spheroidal} harmonic in nature.
%
These frequencies and harmonic functions are the so-called \qnm{s}.
%
They are the eigen-solutions of the source free linearized \ee{} (i.e. \tk{'s} equations) for a \bh{} will fixed (final) mass, $\mf$, and dimensionless spin, $\jf$.
%
The well known and effective completeness of these solutions allows \grad{} from generic perturbations to be well approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with the spin weight -2 spheroidal harmonics, $_{-2}S\lmn$.
%
\begin{align}
	%
	\label{hrd}
	%
	h &= h_{+} - i \, h_{\times}
	  \\ \nonumber
	  &= \frac{1}{r} \sum\lmn A\lmn \; e^{i\,\cw\lmn t} \; _{-2}S\lmn( \jf \cw\lmn,\theta,\phi)
		\\ \nonumber
		&= \frac{1}{r} \sum\LM h\LM(t) \; _{-2}Y\LM(\theta,\phi) \;  .
	%
\end{align}
%
\par In the first and second lines of \eqn{hrd}, we relate the observable \gw{} polarizations, $h_+$ and $h_\times$, with the analytically understood morphology of the time domain waveform.
%
Here, the labels $\ell$ and $m$ are eigenvalues of \tk{'s} angular equations, where units of $M=1$ (e.g. the initial mass of the \bbh{} system), and $c=1$.
%
In the third line of \eqn{hrd}, we represent $h$ in terms of \textit{spherical} harmonic multipoles.
%
This latter form is ubiquitous for the development and implementation of \imr{} signal models for \bbh{s}.
%
%
\par Towards the development of these models, \eqn{hrd} enters in many incarnations.
%
In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line.
%
This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where only $n=0$ is explicitly considered.
%
The consequences of this choice are discussed in reference \check{[X]}.
%
For the so-called \textit{Phenom} models, the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain.
%
\par Both Phenom and \eob{} approaches directly use phenomenological models (i.e. fits) for the \qnm{} frequencies, as these fits are more computationally efficient than the underlying analytic calculations, which involve the solving of continued fraction equations.
%
In the case of \texttt{PhenomHM} and derivative models, fits for the \qnm{} frequencies are used in the process of mapping $\tilde{h}_{22}(f)$ into other $\tilde{h}\LM(f)$ \check{[X]}.
%
In that setting, the \qnm{} frequencies impact the morphology of each $h\LM$ in not only \rd{}, but also merger and late inspiral.
%
%
\par For models that assist tests of the \nht{}, and thereby only include precise \rd{s}, the perspective of \eqn{hrd}'s second and third lines are used to write each spherical harmonic multipole moment as
%
\begin{align}
	\label{hlm}
	h\LM = \frac{1}{r} \sum\lmn \, A\lmn e^{i \cw\lmn t} \sigma\LMlmn
\end{align}
%
where, the spherical-spheroidal mixing coefficient, $\sigma\LMlmn$, is
%
\begin{align}
		\sigma\LMlmn = \int_{\Omega} {_{-2}S}\lmn \,  {_{-2}}Y\LM \, \mathrm{d} \Omega \; .
\end{align}
%
The view of \eqn{hlm} is computationally preferable:
%
The calculation of each ${_{-2}S}\lmn$ involves a series solution which slowly converges for $\jf$ near unity, it is more effective to have accurate models for $\sigma\LMlmn$, which can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.

% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %
\bibliographystyle{ieeetr}
\bibliography{src/mvf.bib}
\end{document}

### 2018-06-13 docs/mvfits_paper/mvf.tex
updating mvf paper

@@
 \def\LMlmn{_{\bar{\ell} \bar{m} \ell m n}}
+\def\gmvp#1{greedy-multivariate-polynomial#1
+  (\texttt{GMVP}#1)\gdef\gmvp{\texttt{GMVP}}}
+\def\gmvr#1{greedy-multivariate-rational#1
+  (\texttt{GMVR}#1)\gdef\gmvr{\texttt{GMVR}}}
 
@@
 
-\paragraph*{Introduction -- }
+\section{Introduction}
 %
@@
 %
-They are the eigen-solutions of the source free linearized \ee{} (i.e. \tk{'s} equations) for a \bh{} will fixed (final) mass, $\mf$, and dimensionless spin, $\jf$.
+They are the eigen-solutions of the source free linearized \ee{} (i.e. \tk{'s} equations) for a perturbed \bh{} with final mass, $\mf$, and dimensionless final spin, $\jf$.
 %
@@
 \begin{align}
-		\sigma\LMlmn = \int_{\Omega} {_{-2}S}\lmn \,  {_{-2}}Y\LM \, \mathrm{d} \Omega \; .
+		\label{sigma}
+		\sigma\LMlmn = \int_{\Omega} {_{-2}S}\lmn \,  {_{-2}}Y^*\LM \, \mathrm{d} \Omega \; .
 \end{align}
 %
-The view of \eqn{hlm} is computationally preferable:
+In \eqn{sigma}, $*$ denotes complex conjugation, and $\Omega$ is the standard solid angle in spherical polar coordinates.
 %
-The calculation of each ${_{-2}S}\lmn$ involves a series solution which slowly converges for $\jf$ near unity, it is more effective to have accurate models for $\sigma\LMlmn$, which can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.
+\par In practice, \eqn{hlm} is computationally preferable:
+%
+The calculation of each ${_{-2}S}\lmn$ involves a series solution which slowly converges for $\jf$ near unity.
+Therefore, it is more effective to have accurate models for $\sigma\LMlmn$, which can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.
+%
+%
+\par In this combined context, it is clear that the modeling of \qnm{} frequencies, $\cw\lmn$, and spherical-spheroidal mixing coefficients, $\sigma\LMlmn$, underpin a wide range of \gw{} signal models.
+%
+While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in many publications, there exist minor shortcomings which we wish to address here.
+%
+\par For the \qnm{} frequencies, it is well known that for nearly extremal \bh{s} (i.e. $\jf \rightarrow 1$) some of the frequencies have zero-damping (i.e. $\tau\lmn \rightarrow \infty$).
+%
+In the context of \aligo{} \da{}, where source parameters are estimated using routines which sample over the space of possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit.
+%
+Here, we present the first models for $\cw\lmn$ that explicitly account for zero-damping in the extremal Kerr limit.
+%
+\par For the modeling of $\sigma\LMlmn$, we note that the results presented in \red{[X]} are limited to cases where the azimuthal indices, $\ell$ and $\bar{\ell}$, are less than or equal to 3.
+%
+As the most advanced signal models include at least $\ell$ or $\bar{\ell}$ of 3, there is use in extending prior results.
+%
+In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole.
+%
+For consistency with the multipolar content of current ringdown models, here, we extend previous results to include the most significant multipoles with $\ell \leq 5$.
+%
+%
+\par In parallel, the methods for modeling $\cw\lmn$ and $\sigma\LMlmn$ have been dispersed: different phenomenological techniques have been used under no coherent framework.
+%
+Here we will present a series of linear modeling techniques, namely the \gmvp{} and \gmvr{} algorithms, in which model terms are iteratively learned with no initial guess.
+%
+The description of \gmvp{} given here is complementary to similar algorithms used to model \qnm{} excitation amplitudes, $A\lmn$, as present in reference \red{[cite]}.
+%
+As we will discuss, the \gmvr{} algorithm is an iterative approach to the (pseudo) non-linear modeling of multivariate rational functions.
+%
+Both \gmvp{} and \gmvr{} are intended for use with low noise data (e.g. the results of analytic calculations), and each employs a reverse (or negative) greedy algorithm to counter over modeling.
+%
+As the underlying process for \gmvp{} and \gmvr{} is stepwise regression, highly correlated basis vectors (i.e. polynomial terms) are handled via an approach we will call \textit{degree tempering}.
+%
+It will be demonstrated that these approaches are readily capable of modeling the complex valued $\cw\lmn$ and $\sigma\LMlmn$.
+%
+Results suggest that the versions of \gmvp{} and \gmvr{} presented here may have broad application in instances where training data are approximately noiseless, and an initial guess is difficult to obtain.
+%
+%
+\par The plan of the paper is as follows. In section \sec{meth}, blah. In \sec{results}, blah. In \sec{discuss}, blah.
+
+%
+\section{Methods}
+\label{meth}
+
+%
+\section{Results}
+\label{results}
+
+%
+\section{Discussion}
+\label{discuss}
 

### 2018-06-14 positive/plotting.py
minor change to 3d sphere

@@ -303,9 +303,9 @@ def plot_3d_mesh_sphere(ax=None,nth=30,nph=30,r=1,color='k',lw=1,alpha=0.1):
 
     # Label axes
     text_r = r*1.1
-    ax.text( text_r,0,0, '$x$', zdir='x', size=24, color='k', alpha = 0.17 )
-    ax.text( 0,text_r,0, '$y$', zdir='x', size=24, color='k', alpha = 0.17 )
-    ax.text( 0,0,text_r, '$z$', zdir='x', size=24, color='k', alpha = 0.17 )
+    ax.text( text_r,0,0, '$x$', zdir='x', size=24, color='k', alpha = 0.27 )
+    ax.text( 0,text_r,0, '$y$', zdir='x', size=24, color='k', alpha = 0.27 )
+    ax.text( 0,0,text_r, '$z$', zdir='x', size=24, color='k', alpha = 0.27 )
 
     # Plot the origin
     plot([0],[0],[0],'k+',alpha=0.35)

### 2018-06-16 docs/mvfits_paper/mvf.tex
adding python folder for issues and data; adding cw fit equations and related plots to draft

@@
 
-\author{L. T. London}
+\author{L. London}
 \affiliation{School of Physics and Astronomy, Cardiff University, The Parade, Cardiff, CF24 3AA, United Kingdom}
@@
 Here, we summarize recent methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
+Towards the construction of these models, two algorithms, GMVP and GMVR, for the automated polynomial and rational modeling of general dimensional complex scalars are presented.
 	%
@@
 %
-Here we will present a series of linear modeling techniques, namely the \gmvp{} and \gmvr{} algorithms, in which model terms are iteratively learned with no initial guess.
+Here we will present linear modeling techniques, namely the \gmvp{} and \gmvr{} algorithms, in which model terms are iteratively learned with no initial guess.
 %
@@
 
+% Equations for QNM frequency fits
+\begin{widetext}
+	\red{
+		\input{src/cwfit_eqns}
+	}
+\end{widetext}
+
+%
+\begin{figure*}
+  %
+  \begin{tabular}{lr}
+    \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
+  \end{tabular}
+  %
+	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+  %
+  Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$.
+Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
+  %
+  The grey dashed line marks the value of $\kappa$ where $\j{}=0$.
+Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+}
+  %
+\end{figure*}
+
 %

### 2018-06-16 positive/learning.py
adding string latex to rational learning; updating doc

@@ -2,6 +2,9 @@
 from maths import *
 from positive import *
 
+# Alias for scipy spline
+from scipy.interpolate import InterpolatedUnivariateSpline as spline
+
 #%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#
 # Low level methods for ration function modeling                                    #
 #%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#
@@ -192,7 +195,24 @@ class mvrfit:
 
     #
     def __str_latex__(this,labels=None,precision=8):
-        return None
+        #
+        fun,numerator_str = poly2latex( this.numerator_symbols, this.numerator_coeffs, precision=precision, latex_labels=labels ).split('\; &= \;')
+        #
+        fun = fun.replace(' ','')
+        #
+        denominator_str = poly2latex( this.denominator_symbols, this.denominator_coeffs, precision=precision, latex_labels=labels ).split('\; &= \;')[-1]
+        #
+        mu_str = ('%%1.%ie'%precision)%this.__mu__ if not isinstance(this.__mu__,complex) else complex2str(this.__mu__,latex=True,precision=precision)
+        #
+        sstr = ( ('%%.%ig'%precision) )%this.__sigma__
+        if 'e' in sstr:
+            a,b = sstr.split('e')
+            sstr = a+r' \times 10^{%i}'%int(b)
+        sigma_str = sstr if not isinstance(this.__sigma__,complex) else complex2str(this.__mu__,latex=True,precision=precision)
+        #
+        latex_str = r'%s \; &= \; %s \; + %s \; \frac{ %s  }{ 1 \; + \; %s }'%( fun,mu_str,sigma_str,numerator_str,denominator_str )
+        #
+        return latex_str
 
     # High level plotting function
     def plot(this,ax=None,show=False,fit_xmin=None,fit_xmax=None):

### 2018-06-16 positive/plotting.py

@@ -93,9 +93,10 @@ def rgb( N,                     #
             B = b*t
         # Ensure that all color vectors have a mean that is the golden ratio (less than one)
         V = abs(R+G+B)
-        V /= mean(V)*0.5*(1+sqrt(5))
-        # But make sure that all values are bounded by one
-        V = array([ min(v,1) for v in V ])
+        if not grayscale:
+            V /= mean(V)*0.5*(1+sqrt(5))
+            # But make sure that all values are bounded by one
+            V = array([ min(v,1) for v in V ])
         # Add color vector to output
         clr.append( V )
 

### 2018-06-16 positive/strings.py

@@ -50,6 +50,63 @@ def hlblack(string):
     return print_format.hlb + string + print_format.end
 
 
+#
+def poly2latex(basis_symbols,coeffs,latex_labels=None,precision=8,term_split=1000):
+
+    # Import useful things
+    from numpy import mod
+
+    #
+    split_state = False
+
+    # Count the number of unique domain variables
+    domain_dimension = len( set(''.join(basis_symbols).replace('K','')) )
+
+    #
+    if len(basis_symbols)==len(coeffs)==0:
+        basis_symbols=['']
+        coeffs = [0]
+
+    # Extract desired labels and handle defaults
+    funlabel = r'f(\vec{x})' if latex_labels is None else latex_labels[0]
+    varlabel = [ 'x%i'%k for k in range(domain_dimension) ] if latex_labels is None else latex_labels[1]
+    prefix = '' if latex_labels is None else latex_labels[2]
+    if varlabel is None:
+        varlabel = [ r'x_%i'%k for k in range(domain_dimension) ]
+    elif len(varlabel) != domain_dimension:
+        error( 'Number of variable labels, %i, is not equal to the number of domain dimensions found, %i.'%( len(varlabel), domain_dimension )  )
+
+    # Create a simple string representation of the fit
+    latex_str = r'%s  \; &= \; %s %s\,x%s%s' % ( funlabel,
+                                               (prefix+r' \, ( \,') if prefix else '',
+                                               complex2str(coeffs[0],
+                                               latex=True,precision=precision) if isinstance(coeffs[0],complex) else '%1.4e'%coeffs[0], r'\,x'.join( list(basis_symbols[0]) ), '' if len(coeffs)>1 else (r' \; )' if prefix else '') )
+    for k,b in enumerate(coeffs[1:]):
+        latex_str += r' \; + \; (%s)\,x%s%s' % ( complex2str(b,latex=True,precision=precision) if isinstance(b,complex) else '%1.4e'%b ,
+                                                 r'\,x'.join( list(basis_symbols[k+1]) ),
+                                                 (r' \; )' if prefix else '') if (k+1)==len(coeffs[1:]) else '' )
+        #
+        if ( not mod(k+2,term_split) ) and ( (k+1) < len(coeffs[1:]) ):
+            latex_str += '\n  \\\\ \\nonumber\n & \quad '
+            if not split_state:
+                split_state = not split_state
+
[…]

### 2018-06-16 docs/mvfits_paper/mvf.tex
adding string latex to rational learning; updating doc
adding greedy algo to doc

@@
 \textheight 10in
+
+\usepackage{algorithm}
+\usepackage{algpseudocode} % in place of algorithmic. Conflicts with revtex4 unless [H] option passed
+\usepackage{setspace} % for pleasent spacing in algorithm
 
@@
 %
-\par The plan of the paper is as follows. In section \sec{meth}, blah. In \sec{results}, blah. In \sec{discuss}, blah.
+\par The plan of the paper is as follows.
+%
+In section \sec{meth}, we outline the \gmvp{} and \gmvr{} algorithms.
+%
+In \sec{results}, we demonstrate the application of each algorithm.
+%
+We first consider the application of \gmvp{} to the modeling of \qnm{} frequencies.
+%
+We then consider the application of \gmvr{} to the modeling of spherical-spheroidal mixing coefficients.
+%
+In \sec{discuss}, we review the performance of \gmvp{} and \gmvr{}, and we discuss potential applications for these methods.
 
@@
 
+We begin by ...
+
+% Generic greedy algo
+\hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{A positive (forward) greedy algorithm, \texttt{PGREEDY}}
+  \label{alg:pgreedy}
+  %
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $ \{ \mlam_{bulk} = \text{basis symbols}$, $\mathcal{A} = \text{action}$, $tol=\text{greedy tolerance}\}$
+    \vskip 10pt
+    \State Define empty list of kept symbols: $\mlam_{kept} = \{\}$
+    \State Initialize estimator value and loop boolean: $\epsilon_{last} = \mathrm{inf}$, $done = \text{False}$
+    %
+    \While{not $done$}
+      \State $\epsilon_{min} = \epsilon_{last}$
+      %
+      \For { $\mlam$ in $\mlam^{bulk}$ }
+        \State $\mlam_{trial} = \mlam_{kept} \cup \mlam$ {\hskip0.525in} (add $\mlam$ to $\mlam_{kept}$)
+        \State $\epsilon = \mathcal{A}(\mlam_{trial})$ {\hskip0.725in} (apply action)
+        \If { $\epsilon < \epsilon_{min}$ }
+          \State $\epsilon_{min} = \epsilon$  {\hskip0.725in} (store trial min)
+          \State $\mlam_{min} = \mlam_{trial}$
+        \EndIf
+      \EndFor
+      %
+      \State $done = |\epsilon_{min}-\epsilon_{last}|<tol$ {\hskip0.4in} (determine if estimator has changed significantly)
+      \If { not $done$ }
+        \State $\epsilon_{last} = \epsilon_{min}$
+        \State $\mlam_{kept} = \mlam_{kept} \cup \mlam_{min}$ {\hskip0.4in} (update kept symbols)
+      \EndIf
+      %
+    \EndWhile
+    \vskip 10pt
+    \State {\bf Output:} Greedy Basis, $\{ \mlam_{kept} \}$
+    %
+  \end{algorithmic}
+  %
+\end{algorithm}
+}
+
+%
+\section{Results}
+\label{results}
+
 % Equations for QNM frequency fits
 \begin{widetext}
-	\red{
 	\input{src/cwfit_eqns}
-	}
 \end{widetext}
 
-%
+% Equations for mixing coefficients
+\begin{widetext}
+  \input{src/ysprod_eqns}
+\end{widetext}
+
+% Plots of QNM frequencies
 \begin{figure*}
   %
-  \begin{tabular}{lr}
+  \begin{tabular}{lcr}
     \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
@@
 
+% Plots of mixing coefficients
+\begin{figure*}
   %
-\section{Results}
-\label{results}
+  \begin{tabular}{lcr}
+    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf}
+  \end{tabular}
+  %
+	\caption{ Spherical-spheroidal harmonic mixing coefficients. }
+  %
+\end{figure*}
 

### 2018-06-17 docs/mvfits_paper/mvf.tex
updating doc with alos templates

@@
 
-% Generic greedy algo
+% Forward greedy algo
 \hspace{1cm}
@@
   %
-  \caption{A positive (forward) greedy algorithm, \texttt{PGREEDY}}
+  \caption{A positive (forward) greedy algorithm, \texttt{PGREEDY}.
+Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error.
+In this setting, $\mathcal{A}$ is assumed to have access to peropheral information, such as the training data.}
   \label{alg:pgreedy}
@@
         \State $\mlam_{trial} = \mlam_{kept} \cup \mlam$ {\hskip0.525in} (add $\mlam$ to $\mlam_{kept}$)
-        \State $\epsilon = \mathcal{A}(\mlam_{trial})$ {\hskip0.725in} (apply action)
+        \State $\epsilon = \mathcal{A}(\mlam_{trial})$ {\hskip0.70in} (action returns fit error)
         \If { $\epsilon < \epsilon_{min}$ }
-          \State $\epsilon_{min} = \epsilon$  {\hskip0.725in} (store trial min)
+          \State $\epsilon_{min} = \epsilon$  {\hskip0.825in} (store trial min)
           \State $\mlam_{min} = \mlam_{trial}$
@@
       %
-      \State $done = |\epsilon_{min}-\epsilon_{last}|<tol$ {\hskip0.4in} (determine if estimator has changed significantly)
+      \State $done = |\epsilon_{min}-\epsilon_{last}|<tol$ %{\hskip0.4in} (determine if estimator has changed significantly)
       \If { not $done$ }
@@
     \State {\bf Output:} Greedy Basis, $\{ \mlam_{kept} \}$
+    %
+  \end{algorithmic}
+  %
+\end{algorithm}
+}
+
+% GMVP
+\hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{\gmvp{}, a degree tempered stepwise algorithm for multivariate polynomial modeling of scalar data.}
+  \label{alg:pgreedy}
+  %
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $ \{ \bf{x}, \bf{y} \}$
+    \vskip 10pt
+    \State Define action using matrix least squares
+    \State Define bulk symbol space using cartesian inner-product
+    \State Define list of allowed polynomial degrees
+    \For { all degrees }
+      \State Select all symbols with degree less than or equal to current
+      \State Apply \texttt{PGREEDY} to get symbol subset and estimator val
+      \If  { estimator has stalled }
+        \State Break
+      \EndIf
+    \EndFor
+    \State Apply negative greedy to get final model
+    \vskip 10pt
+    \State {\bf Output:} Final model
+    %
+  \end{algorithmic}
+  %
+\end{algorithm}
+}
+
+% GMVR
+\hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{\gmvr{}, a degree tempered stepwise algorithm for multivariate rational modeling of scalar data.}
+  \label{alg:pgreedy}
+  %
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $ \{ \bf{x}, \bf{y} \}$
+    \vskip 10pt
+    \State Define action using matrix least squares
+    \State Define bulk symbol space using cartesian inner-product
+    \State Define list of allowed polynomial degrees
+    \For { all degrees }
+      \State Select all numerator symbols with degree less than or equal to current
+      \State Select all denominator symbols with degree less than or equal to current, enforcing no constant term
+      \State Construct new symbol space by tagging each polynomial symbol with a boolean denoting whether it is in the numerator or denominator
+      \State Apply \texttt{PGREEDY} to get symbol subset and estimator val
+      \If  { estimator has stalled }
+        \State Break
+      \EndIf
+    \EndFor
+    \State Apply negative greedy to get final model
+    \vskip 10pt
+    \State {\bf Output:} Final model
     %

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating doc

@@
 %
-\par In practice, \eqn{hlm} is computationally preferable:
+\par In practice, \eqn{hlm} is computationally efficient:
 %
@@
 \label{meth}
-
-We begin by ...
-
+%
+Within the topic of regression, linear regression has particular advantages:
+%
+its matrix based formulation can be computationally efficient, and it does not require initial guesses for model parameters.
+%
+Perhaps most intriguingly, the formal series expansions of smooth functions support linear and rational models (e.g. Pade approximants) having application to many datasets.
+%
+Here we will develop algorithms for the linear modeling of scalar functions (real or complex valued) of many variables.
+%
+\par If we consider a scalar function, $f$, of $N$ variables sampled in $j$, $\vec{x}_j = \{x_{\alpha j}\}_{\alpha=0}^{N}$, then $f(\vec{x})_j$ can be represented (possibly inaccurately) as a sum over $K$ linearly independent basis functions, $\phi_k(\vec{x}_j)$:
+%
+\begin{align}
+  \label{lin1}
+  f({\vec{x}})_j \; = \; \sum_{k=0}^{K} \; \mu_{k} \, \phi_{kj}\; .
+\end{align}
+%
+The central player is \eqn{lin1} is the set of basis coefficients $\mu_{k}$.
+%
+Typically, one chooses or derives $\phi_{k}(\vec{x}_j)$ to capture inherent features of $f(\vec{x}_j)$.
+%
+With $\phi_{k}(\vec{x}_j)$ assumed to be known, the linear representation (\ceqn{lin1}) lastly defined by the set of $\mu_k$.
+%
+\def\vecmu{\vec{\mu}}
+\def\vecf{\vec{f}}
+\def\hatU{\hat{U}}
+\def\hatP{\hat{P}}
+%
+\par From here it is useful to note that \eqn{lin1} has a linear homogeneous matrix form.
+In particular, defining $\hat{U} = \{\phi_{kj}\}$, and $\vec{f} = \{f_j\}$, then $\vec{f} = \hat{U} \; \vec{\mu}$.
+%
+This implies that
+%
+\begin{align}
+  \vecmu = \hatP \; \vecf \; ,
+\end{align}
+%
+where
+%
+\begin{align}
+  %
+  \label{pinv1}
+  \hatP = \left( \left( \hatU^{-1} \right)^T \hatU^{-1} \right)^{-1}
+\end{align}
+%
+is the \textit{pseudo-inverse} of $\hatU$.
+%
+Equations (\ref{lin1}), and related discussion through \eqn{pinv1} illustrate the most rudimentary solution to the linear modeling problem.
+%
+However, there are many ways to expand upon and refine the solution presented thus far.
+%
+In the following subsections we will consider two such approaches.
+%
+First we will consider the general polynomial modeling of multivariate scalar functions.
+%
+This will encompass the \gmvp{} algorithm.
+%
+Second, we will build upon the \gmvp{} approach by considering models of rational functions: polynomials divided by polynomilas.
+%
+To consider these two approaches in a largely automated way (i.e.
+where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach.
+%
+\subsection{A Generic Greedy Algorithm}
+%
+While we most often want a single model for a given dataset (e.g. some approximation of $\vecf$ from numerical calculation or experiment), there are often many more modeling choices than desired.
+%
+In particular, if we refer to our set of all possible basis functions as our ``\textit{symbol space}'', then the problem of determining how many, and which basis vectors (i.e.
+symbols) to use is a problem of combinatoric complexity.
+%
+\par A well known method for finding an approximate solution to this problem is the so-called ``greedy'' algorithm.
+%
+The premise is this:
+%
+We will iteratively construct models with increasing number of symbols.
+%
+The process begins by finding the single symbol (basis vector) that yields the most accurate model (in the sense of minimizing least-squares error).
+%
+That encompasses the first iteration of a process in which we will greedily add symbols to our model.
+%
+In each following iteration, an all remaining symbols are added to the model one at a time, and the single additional symbol which yields the greatest increase in model accuracy is kept for the following iteration.
+%
+In this way, a list of optimal model symbols is learned.
+%
+The forward process is to end when the model accuracy (or changes thereof) pass a specified threshold.
+%
+This rough algorithmic picture is spelled out in more Alg. \ref{alg:pgreedy}.
+%
+% \par
+%
 % Forward greedy algo
@@
 
+%
+\subsection{Greedy Multivariate Polynomial Fitting}
+%
+The preceeding ...
 % GMVP
@@
     \vskip 10pt
-    \State Define action using matrix least squares
+    \State \grey{\# Define action using matrix least squares}
+    \State $\mathcal{A}$: $\epsilon = \hat{U}$
     \State Define bulk symbol space using cartesian inner-product

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating doc

@@
 \par From here it is useful to note that \eqn{lin1} has a linear homogeneous matrix form.
+%
 In particular, defining $\hat{U} = \{\phi_{kj}\}$, and $\vec{f} = \{f_j\}$, then $\vec{f} = \hat{U} \; \vec{\mu}$.
@@
 \begin{align}
+  \label{eq:linsol1}
   \vecmu = \hatP \; \vecf \; ,
@@
 %
-This rough algorithmic picture is spelled out in more Alg. \ref{alg:pgreedy}.
+This rough algorithmic picture encapsulated in Alg. \ref{alg:pgreedy}.
+%
+\par Note that we will use the terms ``basis vector'' and ``model symbol'' interchangeably.
+However, in practice, it can be useful to represent basis vectors symbolically (e.g.
+with strings), and have a way of bijectively mapping between symbols and numerical basis vectors.
 %
@@
 Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error.
-In this setting, $\mathcal{A}$ is assumed to have access to peropheral information, such as the training data.}
+In this setting, $\mathcal{A}$ is assumed to have access to peripheral information, such as the training data.}
   \label{alg:pgreedy}
@@
 %
-The preceeding ...
+The study of smooth scalar functions (e.g. $\vecf$) often centers about the Taylor series expansion.
+%
+In that instance, it is clear that any infinitely differentiable scalar function of many variables can be represented in terms of its derivatives by
+%
+\begin{align}
+  \label{eq:mvt}
+  f( \vec{x} + \vec{h} ) &= e^{ \vec{x} \cdot \vec{\nabla}' } \, f(\vec{x}\,') |_{\vec{x}\,'=\vec{h}}
+  \\ \nonumber
+  &\approx \sum_{k=0}^{K} \, \frac{1}{k!} \, (\vec{x} \cdot \vec{\nabla}')^{k} \, f(\vec{x}\,') |_{\vec{x}\,'=\vec{h}}
+\end{align}
+%
+From the first to second line of \eqn{eq:mvt}, we have used the definition of the exponential function (i.e. its series expansion form).
+%
+In the second line, the equality has been replaced by an approximation as we have limited the linear representation to $K$ terms.
+%
+This latter point is key to the perspective of \gmvp{}: given training data thought to be related to a smooth multivariate function, it may be well approximated by a truncated series expansion in the appropriate coordinate basis.
+%
+\par This truncated expansion happens to be a polynomial in at most $N$ variables.
+%
+In this setting, the uncertainty of which and how many basis terms to include makes this a problem ripe for the application of \eqn{eq:linsol1} and Alg. (\ref{alg:pgreedy}) .
+%
+\par In the current setting, the basis symbols required by Alg. (\ref{alg:pgreedy}) are the multinomial terms in \eqn{eq:mvt}.
+%
+Each term is an element of the cartesian inner-product of the power-set of each model dimension. That is $\mlam_{bulk} = \{x_0,x_1 .. x_N, ... x_0^1, x_0^2, x_0^3, ...  , (x_0^K x_1^K ... x_N^K) \}$.
+%
+Note that in practice it may be useful to encode elements of $\mlam_{bulk}$ with strings representing their constituents (e.g. $x_0 x_0 x_1 x_2 x_2 x_4$ could be represented by the string ``001224'').
+%
+\par The action, $\mathcal{A}(\mlam_{trial})$, required by Alg.
+(\ref{alg:pgreedy}) encompasses the evaluation of \eqn{eq:linsol1} to solve for the basis coefficients, $\mu_k$, and the calculation of the modeling error.
+%
+An explicit sktech of this is given by Alg. (\ref{alg:A_gmvp}).
+%
+\hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{$\mathcal{A}_{\gmvp}$, the action for \gmvp. Model calculation given basis symbols, and output of model error estimate.}
+  %
+  \label{alg:A_gmvp}
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $\mlam_{trial}$
+    \vskip 10pt
+    \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
+    \State Calculate the model representation error, e.g.: $\epsilon = |var(\hatU \vecmu - \vec{f})|/var(\vec{f})$, where $var$ is the variance of the respective list.
+    \vskip 10pt
+    \State {\bf Output:} $\epsilon$
+  \end{algorithmic}
+\end{algorithm}
+}
+%
+\par The combination of these two ideas alone results in an algorithm prone to a deficit of stepwise methods: there is the very likely possibility that the algorithm would confuse correlated basis vectors (e.g.
+$x^2$ may be confused for $x^4$).
+%
+To counter this, we may incrementally increase, or \textit{temper}, the maximum allowed multinomial order.
+%
+Recall that a term such as $x_0x_1x_3^2$ has an effective order of 4.
+%
+The combination of degree tempering with the greedy approach results in the \gmvp{} algorithm as presented in Alg. (\ref{alg:gmvp})
+%
 % GMVP
@@
   \caption{\gmvp{}, a degree tempered stepwise algorithm for multivariate polynomial modeling of scalar data.}
-  \label{alg:pgreedy}
+  \label{alg:gmvp}
   %
@@
     %
-    \State {\bf Input:} $ \{ \bf{x}, \bf{y} \}$
+    \State {\bf Input:} $ \{ \bf{x}, \bf{y}, $max\_order = 6$ \}$
     \vskip 10pt
-    \State \grey{\# Define action using matrix least squares}
-    \State $\mathcal{A}$: $\epsilon = \hat{U}$
-    \State Define bulk symbol space using cartesian inner-product
+    \State Define bulk symbol space using cartesian inner-product of the power set of each basis symbol
     \State Define list of allowed polynomial degrees
@@
   \caption{\gmvr{}, a degree tempered stepwise algorithm for multivariate rational modeling of scalar data.}
-  \label{alg:pgreedy}
+  \label{alg:gmvr}
   %

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating doc

@@
 \hspace{1cm}
+\def\pgreedy{\texttt{PGREEDY}}
 {\scriptsize
@@
   %
-  \caption{A positive (forward) greedy algorithm, \texttt{PGREEDY}.
+  \caption{A positive (forward) greedy algorithm, \pgreedy{}, \texttt{PGREEDY}.
 Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error.
@@
     \vskip 10pt
-    \State {\bf Output:} Greedy Basis, $\{ \mlam_{kept} \}$
+    \State {\bf Output:} $\{ \mlam_{kept} \}$ (the Greedy Basis)
     %
@@
 %
-Each term is an element of the cartesian inner-product of the power-set of each model dimension. That is $\mlam_{bulk} = \{x_0,x_1 .. x_N, ... x_0^1, x_0^2, x_0^3, ...  , (x_0^K x_1^K ... x_N^K) \}$.
+Each term is an element of the n-fold cartesian inner-product of the power-sets of each model dimension.
+That is $\mlam_{bulk} = \{x_0,x_1 ..
+x_N, ...
+x_0^1, x_0^2, x_0^3, ...
+, (x_0^K x_1^K ...
+x_N^K) \}$.
 %
@@
 %
-Recall that a term such as $x_0x_1x_3^2$ has an effective order of 4.
+Recall that a term such as $x_0x_1x_3^2$ has an effective degree of 4.
 %
-The combination of degree tempering with the greedy approach results in the \gmvp{} algorithm as presented in Alg. (\ref{alg:gmvp})
+The combination of degree tempering with the greedy approach results in the \gmvp{} algorithm as presented in Alg. (\ref{alg:gmvp}).
 %
@@
     %
-    \State {\bf Input:} $ \{ \bf{x}, \bf{y}, $max\_order = 6$ \}$
+    \State {\bf Input:} $ \{ \bf{x}, \bf{y}, $max\_degree = 6$, tol \}$
     \vskip 10pt
-    \State Define bulk symbol space using cartesian inner-product of the power set of each basis symbol
-    \State Define list of allowed polynomial degrees
-    \For { all degrees }
-      \State Select all symbols with degree less than or equal to current
-      \State Apply \texttt{PGREEDY} to get symbol subset and estimator val
-      \If  { estimator has stalled }
-        \State Break
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the n-fold cartesian inner-product of the power set of each basis symbol
+    \State Define $\mathcal{A}_{\gmvp{}}$ according to Alg. (\ref{alg:A_gmvp}).
+    \State Given $max\_order$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
+    \For {$d$ \textbf{in}  ${ D}$ }
+      \State Select all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
+      \State Apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
+      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
+        \State \textbf{break}
       \EndIf
     \EndFor
-    \State Apply negative greedy to get final model
     \vskip 10pt
-    \State {\bf Output:} Final model
+    \State {\bf Output:} $\mlam^{(d)}_{opt}$
     %
@@
 }
-
+%
+%
+\subsection{Greedy Multivariate Rational Fitting}
+%
+%
+\par Despite the apparent universality of of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a multinomial (historically, this is equivalent to ``Runge's phenomenon'').
+%
+Of the simplest examples are the rational functions of the form
+%
+\def\muf{\bar{\mu}}
+\def\sif{\bar{\sigma}_f}
+\begin{align}
+  \label{eq:rat1}
+  f(\vec{x}) = \muf + \sif \; \frac{ \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) }{ 1 - \sum_{v=0}^{V} b_v \, \phi_{v}(\vec{x}) } \;,
+\end{align}
+%
+where $\muf$ is the additive mean of $f(\vec{x})$, and $\sif$ is the standard deviation of $f(\vec{x})$ from its mean.
+%
+\par While it is tempting to embrace \eqn{eq:rat1}'s $f({\vec{x}})$ as a nonlinear function and so resort to nonlinear modeling methods, note that a reformulation reveals an underlying linear structure.
+%
+Namely, if we let
+%
+\begin{align}
+  g = (f - \muf)/\sif
+\end{align}
+%
+then the algebraic manipulation of \eqn{eq:rat1} results in
+%
+\begin{align}
+  \label{eq:rat2}
+  g = \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) + g\, \sum_{v=0}^{V} b_v \, \phi_{v}(\vec{x}) \; .
+\end{align}
+%
+We are free to relabel the indices such that \eqn{eq:rat2} is manifestly linear in a single index.
+%
+At this stage, we will also explicitely consider the $j^\mathrm{th}$ samples of the domain, and so refer to $\vec{x}$ as $\vec{x}_j$.
+%
+The adjustments of perspective result in
+%
+\begin{align}
+  \label{eq:rat3}
+  g_j = \sum_{k=0}^{R+V+1} \, z_{k} \, \psi_k(\vec{x}_j) \;,
+\end{align}
+%
+where
+%
+\begin{align}
+  %
+  z_k = \left\{ \begin{array}{cc}
+        a_k,      & \text{for }0\leq k\leq R\\
+        b_k, & \quad \;\; \;\text{for }R+1\leq k\leq R+V+1
+      \end{array} \right\}
+\end{align}
+%
+and
+%
+\begin{align}
+  %
+  \psi_k(\vec{x}_j) = \left\{\begin{array}{cc}
+        \phi_k(\vec{x}_j),      & \text{for }0\leq k\leq R\\
+        \phi_k(\vec{x}_j) g , & \quad \;\; \;\text{for }R+1\leq k\leq R+V+1
+        \end{array} \right\}
+\end{align}
+%
+\par Recalling \eqns{eq:linsol1}{pinv1}, it follows that the coefficients of interest ($a_k$ and $b_k$), may be estimated according to
+%
+\begin{align}
+  \label{eq:pinv2}
+  \vec{\alpha} = \hat{P} \; \vec{g} \;.
+\end{align}
+%
+where, here, $\hat{P}$ is the pseudo-inverse of the matrix whose elements are $\psi_k(\vec{x}_j)$.
+%
+\par But note that $\hat{P}$'s depending on $g$ signals that there is more to be done.
+%
+In particular, let us briefly consider the effect of noise on $g$, e.g. $g \rightarrow g+n$.
+%
+In this contemplation, it may be that shown that $n$ may be entirely regelated to $\hat{P}$.
+%
+It is in this sense that \eqn{eq:pinv2} is insufficient to generally solve for $\vec{\alpha}$.
+%
+\par The key to robustly solving for $\vec{\alpha}$ lies in iterative refinement.
+%
+Specifically, we note that \eqn{eq:rat2} may be modified iteratively minimize the impact of numerical noise on the eventual solution, $\vec{\alpha}$.
+%
+To this end, if we define $g^{(0)}$ to be \eqn{eq:rat2} evaluated with $\vec{\alpha}$ as given by \eqn{eq:pinv2}, and note that by construction, $g^{(0)}$ is less effected by (zero mean) noise in $g$, then a further refinement may be obtained by
+%
+\begin{align}
+  \label{eq:rat2}
+  g^{(1)} = \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) + g^{(0)}\, \sum_{v=0}^{V} b_v \, \phi_{v}(\vec{x}) \; .
+\end{align}
+%
+\eqn{eq:rat2} straightforwardly generalizes to
+%
+\begin{align}
+  \label{eq:rat3}
+  g^{(n+1)} = \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) + g^{(n)}\, \sum_{v=0}^{V} b_v \, \phi_{v}(\vec{x}) \; .
+\end{align}
+%
 % GMVR
@@
     \vskip 10pt
-    \State Define action using matrix least squares
-    \State Define bulk symbol space using cartesian inner-product
+    \State Define $\mathcal{A}_{\gmvp}$ as in Alg. (\ref{alg:A})
+    \State Define, $\mlam_{bulk}$, bulk symbol space using the n-fold cartesian inner-product
     \State Define list of allowed polynomial degrees
-    \For { all degrees }
+    \For { $d_k$ in  }
       \State Select all numerator symbols with degree less than or equal to current
@@
       \State Construct new symbol space by tagging each polynomial symbol with a boolean denoting whether it is in the numerator or denominator
-      \State Apply \texttt{PGREEDY} to get symbol subset and estimator val
+      \State Apply \pgreedy{} to get the optimal symbol subset, $\mlam_{opt}$, and estimator value, $\epsilon_{opt}$.
       \If  { estimator has stalled }

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating doc

@@
 %
-\par The combination of these two ideas alone results in an algorithm prone to a deficit of stepwise methods: there is the very likely possibility that the algorithm would confuse correlated basis vectors (e.g.
-$x^2$ may be confused for $x^4$).
+\par The combination of these two ideas alone results in an algorithm prone to a deficit of stepwise methods: the algorithm may confuse correlated basis vectors (e.g. $x^2$ may be confused for $x^4$).
 %
@@
   \label{eq:rat1}
-  f(\vec{x}) = \muf + \sif \; \frac{ \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) }{ 1 - \sum_{v=0}^{V} b_v \, \phi_{v}(\vec{x}) } \;,
+  f(\vec{x}) = \muf + \sif \; \frac{ \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) }{ 1 - \sum_{v=1}^{V} b_v \, \phi_{v}(\vec{x}) } \;,
 \end{align}
 %
-where $\muf$ is the additive mean of $f(\vec{x})$, and $\sif$ is the standard deviation of $f(\vec{x})$ from its mean.
+where $\muf$ is the additive mean of $f(\vec{x})$, and $\sif$ is the standard deviation of $f(\vec{x})$ from its mean, and $\phi_k$ are the multinomials basis functions considered in the previous section.
 %
-\par While it is tempting to embrace \eqn{eq:rat1}'s $f({\vec{x}})$ as a nonlinear function and so resort to nonlinear modeling methods, note that a reformulation reveals an underlying linear structure.
+Note that, in \eqn{eq:rat1}, the sum over $v$ does not include the constant term associated with $\phi_0$.
+%
+\par While it is tempting to embrace \eqn{eq:rat1}'s $f({\vec{x}})$ as a nonlinear function and so resort to nonlinear modeling methods, a reformulation reveals an underlying linear structure.
 %
@@
   \label{eq:rat2}
-  g = \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) + g\, \sum_{v=0}^{V} b_v \, \phi_{v}(\vec{x}) \; .
+  g = \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) + g\, \sum_{v=1}^{V} b_v \, \phi_{v}(\vec{x}) \; .
 \end{align}
@@
         a_k,      & \text{for }0\leq k\leq R\\
-        b_k, & \quad \;\; \;\text{for }R+1\leq k\leq R+V+1
+        b_k, & \quad \;\; \;\text{for }R+1\leq k\leq R+V
       \end{array} \right\}
@@
         \phi_k(\vec{x}_j),      & \text{for }0\leq k\leq R\\
-        \phi_k(\vec{x}_j) g , & \quad \;\; \;\text{for }R+1\leq k\leq R+V+1
+        \phi_k(\vec{x}_j)\, g , & \quad \;\; \;\text{for }R+1\leq k\leq R+V
         \end{array} \right\}
@@
 %
-\par But note that $\hat{P}$'s depending on $g$ signals that there is more to be done.
+\par However, we note that $\hat{P}$'s depending on $g$ signals that there is more to be done.
 %
-In particular, let us briefly consider the effect of noise on $g$, e.g. $g \rightarrow g+n$.
+In particular, let us briefly consider the effect of zero-mean noise on $g$, e.g. $g \rightarrow g+n$.
 %
@@
 %
-\par The key to robustly solving for $\vec{\alpha}$ lies in iterative refinement.
+\par The key to robustly solving for $\vec{\alpha}$ lies in the iterative refinement of $\vec{\alpha}$.
 %
-Specifically, we note that \eqn{eq:rat2} may be modified iteratively minimize the impact of numerical noise on the eventual solution, $\vec{\alpha}$.
+Specifically, we note that \eqn{eq:rat2} may be modified to iteratively minimize the impact of numerical noise on $\hat{P}$.
 %
-To this end, if we define $g^{(0)}$ to be \eqn{eq:rat2} evaluated with $\vec{\alpha}$ as given by \eqn{eq:pinv2}, and note that by construction, $g^{(0)}$ is less effected by (zero mean) noise in $g$, then a further refinement may be obtained by
+That is, to reduce the impact of noise on $\hat{P}$, we are free to calculate it using model evaluations of $g$ rather than the original training data.
+%
+To this end, if we define $g^{(0)}=g$ (i.e. the training data) then, with $\hat{P} = \hat{P}( \vec{g}^{\,(n)} )$, \eqn{eq:pinv2} generalizes to
 %
 \begin{align}
-  \label{eq:rat2}
-  g^{(1)} = \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) + g^{(0)}\, \sum_{v=0}^{V} b_v \, \phi_{v}(\vec{x}) \; .
+  \label{eq:pinv3}
+  \vec{\alpha}^{(n+1)} = \hat{P}(\vec{g}^{\,(n)}) \, \vec{g}^{(0)}\;.
 \end{align}
 %
-\eqn{eq:rat2} straightforwardly generalizes to
+In practice, one solves \eqn{eq:pinv3} for $\vec{\alpha}^{(n)}$, and then uses the related $a_r^{(n)}$ and $b_v^{(n)}$ to calculate $g^{(n+1)}$ via
 %
 \begin{align}
-  \label{eq:rat3}
-  g^{(n+1)} = \sum_{r=0}^{R} a_r \, \phi_{r}(\vec{x}) + g^{(n)}\, \sum_{v=0}^{V} b_v \, \phi_{v}(\vec{x}) \; .
+  \label{eq:rat4}
+  g^{(n+1)} =  \frac{ \sum_{r=0}^{R} a^{(n+1)}_r \, \phi_{r}(\vec{x}) }{ 1\;-\;  \sum_{v=1}^{V} b^{(n+1)}_v \, \phi_{v}(\vec{x}) } \; ,
 \end{align}
+%
+which is then fed back into \eqn{q:pinv3} for further refinement.
+%
+The refinement process is to terminate when a measure of model error (e.g. $||g^{(0)}-g^{(n)}||$) passes a predetermined threshold.
+%
+\par Much as in the case of multivariate polynomial fitting, we are left with an un unknown number and content of basis symbols.
+%
+In principle, the existence of $a_r$ and $b_v$ makes the problem more complicated, as one could imagine optimizing over each symbol space independently.
+%
+To broach these complications, we again use a greedy algorithm with degree tempering.
+%
+However, rather than independent greedy optimizations for the numerator and denominator bases symbols, \eqn{eq:rat3} suggests that the appropriate labeling of symbols (e.g.
+``numerator'' or ``denominator'') may yield an effective flattening of the supposed 2D basis selection problem.
+%
+Put another way, rather than two greedy optimizations over $R$ and $V-1$ symbols (with $(V-1)R$ iterations), a single greedy process over $V+R$ symbols is performed.
+%
+\par With the conceptual tools in hand, we may proceed to constructing \gmvr{} be first defining its action, $\mathcal{A}_{\gmvr}$.
+%
+This is done in Alg. (\ref{alg:A_gmvr}).
+%
+\hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{$\mathcal{A}_{\gmvr}$, the action for \gmvr. Model calculation given basis symbols, and output of model error estimate.}
+  %
+  \label{alg:A_gmvr}
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $\mlam_{trial}$
+    \vskip 10pt
+    \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
+    \State Calculate the model representation error, e.g.: $\epsilon = |var(\hatU \vecmu - \vec{f})|/var(\vec{f})$, where $var$ is the variance of the respective list.
+    \vskip 10pt
+    \State {\bf Output:} $\epsilon$
+  \end{algorithmic}
+\end{algorithm}
+}
 %

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating docs, adding setup.py

@@
     %
-    \State {\bf Input:} $ \{ \bf{x}, \bf{y}, $max\_degree = 6$, tol \}$
+    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
     \vskip 10pt
@@
     \For {$d$ \textbf{in}  ${ D}$ }
-      \State Select all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
-      \State Apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
+      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
+      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
       \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
@@
 %
-which is then fed back into \eqn{q:pinv3} for further refinement.
+which is then fed back into \eqn{eq:pinv3} for further refinement.
 %
@@
 %
-\par With the conceptual tools in hand, we may proceed to constructing \gmvr{} be first defining its action, $\mathcal{A}_{\gmvr}$.
+\par With the conceptual tools in hand, we may proceed to constructing \gmvr{} by first defining its action, $\mathcal{A}_{\gmvr}$.
 %
@@
     %
-    \State {\bf Input:} $\mlam_{trial}$
+    \State {\bf Input:} \{ $\mlam_{trial}$, $tol=10^{-3}$ \}
     \vskip 10pt
-    \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
-    \State Calculate the model representation error, e.g.: $\epsilon = |var(\hatU \vecmu - \vec{f})|/var(\vec{f})$, where $var$ is the variance of the respective list.
+    \State Calculate $\alpha^{(1)}_k$ via \eqn{eq:pinv3}. Implicitly, $n=1$.
+    \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
+    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = |var(g^{(n)} - g^{(0)})|/var(g^{(0)})$.
+    \State $done = False$
+    \While { not $done$ }
+      \State Calculate $\alpha^{n+1}_{k}$  via \eqn{eq:pinv3}.
+      \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
+      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = |var(g^{(n)} - g^{(0)})|/var(g^{(0)})$.
+      \State $done = |\epsilon^{(n)}-\epsilon^{(n-1)}| < tol$
+      \State Implicitly, $n = n+1$
+    \EndWhile
     \vskip 10pt
-    \State {\bf Output:} $\epsilon$
+    \State {\bf Output:} $\epsilon^{(n)}$
   \end{algorithmic}
@@
 }
+%
+\par The combination of \eqns{eq:pinv3} and \eqn{eq:rat4}, along with \pgreedy{} and degree tempering, results in the \gmvr{} algorithm as presented in Alg. (\ref{alg:gmvr}).
+%
+\par While not treated here, it is noted that Ref. \cite{London:2018gaq} utilizes \gmvp{} with a parameter dimension of 4.
+%
+\par In the following section we apply both \gmvp{} and \gmvr{} to the modeling of noiseless (up to roundoff error) data: the \qnm{} frequencies of Kerr \bh{s}, and the inner-products of the spherical and spheroidal harmonics.
+%
+In each case, the underlying 1D parameter in each case will be the dimensionless \bh{} spin, $\jf{}$.
 %
@@
     %
-    \State {\bf Input:} $ \{ \bf{x}, \bf{y} \}$
+    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
     \vskip 10pt
-    \State Define $\mathcal{A}_{\gmvp}$ as in Alg. (\ref{alg:A})
-    \State Define, $\mlam_{bulk}$, bulk symbol space using the n-fold cartesian inner-product
-    \State Define list of allowed polynomial degrees
-    \For { $d_k$ in  }
-      \State Select all numerator symbols with degree less than or equal to current
-      \State Select all denominator symbols with degree less than or equal to current, enforcing no constant term
-      \State Construct new symbol space by tagging each polynomial symbol with a boolean denoting whether it is in the numerator or denominator
-      \State Apply \pgreedy{} to get the optimal symbol subset, $\mlam_{opt}$, and estimator value, $\epsilon_{opt}$.
-      \If  { estimator has stalled }
-        \State Break
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the n-fold cartesian inner-product of the power set of each basis symbol.
+This is the combined bulk for numerator and denominator symbols.
+    \State Define $\mathcal{A}_{\gmvr{}}$ according to Alg. (\ref{alg:A_gmvr}).
+    \State Given $max\_order$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
+    \For {$d$ \textbf{in}  ${ D}$ }
+      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
+      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
+      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
+        \State \textbf{break}
       \EndIf
     \EndFor
-    \State Apply negative greedy to get final model
     \vskip 10pt
-    \State {\bf Output:} Final model
+    \State {\bf Output:} $\mlam^{(d)}_{opt}$
     %
@@
 }
-
+%
 %
@@
 \label{results}
-
+%
+\par We present the application of \gmvp{} and \gmvr{} to the respective modeling of \qnm{} frequencies, and harmonic mixing coefficients.
+%
+While each case is an instance of modeling on a 1D domain, we note that higher dimensional cases have been treated elsewhere \cite{London:2018gaq}.
+%
+\subsection{Modeling \qnm{} frequencies using \gmvp{}}
+%
+%
 % Equations for QNM frequency fits

### 2018-06-18 setup.py

@@ -5,15 +5,16 @@ from distutils.core import setup
 from setuptools import find_packages
 
 #
-setup(name='positive',
+setup(name='psitive',
       version='1.0',
-      description='Low Level Algorithms for Data Analysis and Manipulation',
+      description='Low level python API for NR+LIGO packages.',
       author='Lionel London',
       author_email='lionel.london@ligo.org',
       packages=find_packages(),
       include_package_data=True,
       package_dir={'positive': 'positive'},
+      package_data={'./': ['docs/*', 'examples/*', 'factory/*', 'gallery/*', 'issues/*']},
       url='https://github.com/llondon6/positive',
       download_url='https://github.com/llondon6/positive/archive/master.zip',
-      install_requires=['h5py','numpy','scipy','matplotlib'],
+      install_requires=['numpy','scipy','matplotlib'],
      )

### 2018-06-18 setup.py
psitive -> positive in steu[

@@ -5,7 +5,7 @@ from distutils.core import setup
 from setuptools import find_packages
 
 #
-setup(name='psitive',
+setup(name='positive',
       version='1.0',
       description='Low level python API for NR+LIGO packages.',
       author='Lionel London',

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating doc

@@
 %
+In seeking to apply \gmvp{} to select \qnm{} frequencies, we wish to impose a zero-damping constraint, namely that some frequencies are real as $\jf \rightarrow 1$.
+%
+We also wish the impose a domain transformation, $\kappa(\jf)$, such that $0 \leq \kappa \leq 1$ and the individual \qnm{} frequencies are morphologically simplified.
+%
+\par For the domain transformation, inspection of \qnm{} frequencies with $\ell \leq 5$ suggest that
+%
+\begin{align}
+  \kappa(\jf) = \left( \ln( 2 - \jf ) / \ln(3) \right)^{1/(2-\ell+|m|)}
+\end{align}
+%
+appropriately linearizes the sharp behavior of each frequency near $\jf=1$.
+%
+This implies that
+%
+\begin{align}
+  \cw_{\lmn} = m/2 + \kappa \sum_{j=1}^{J} c_j \kappa^k
+\end{align}
+%
+In the case of the non-zero damped \qnm{s}, (e.g. $(\ell,m)=(3,2)$), a more general polynomial form may be adopted, namely,
+%
+\begin{align}
+  \cw_{\lmn} = \sum_{j=0}^{J} c_j \kappa^k
+\end{align}
+%
+\par For the zero-damping constraint, when considering a \qnm{} frequency $\cw_{\lmn}$, zero-damping at $\jf=1$ implies that $\cw_{\lmn}(\kappa \approx 0)-m/2 \propto \kappa$, where $m/2$ is the well known limiting value for each \qnm{} frequencies real part as $\jf\rightarrow 1$.
 %

### 2018-06-18 docs/mvfits_paper/mvf.tex
updating doc

@@
 %
-This implies that
-%
-\begin{align}
-  \cw_{\lmn} = m/2 + \kappa \sum_{j=1}^{J} c_j \kappa^k
-\end{align}
-%
-In the case of the non-zero damped \qnm{s}, (e.g. $(\ell,m)=(3,2)$), a more general polynomial form may be adopted, namely,
-%
-\begin{align}
-  \cw_{\lmn} = \sum_{j=0}^{J} c_j \kappa^k
-\end{align}
-%
 \par For the zero-damping constraint, when considering a \qnm{} frequency $\cw_{\lmn}$, zero-damping at $\jf=1$ implies that $\cw_{\lmn}(\kappa \approx 0)-m/2 \propto \kappa$, where $m/2$ is the well known limiting value for each \qnm{} frequencies real part as $\jf\rightarrow 1$.
 %
-% Equations for QNM frequency fits
-\begin{widetext}
-	\input{src/cwfit_eqns}
-\end{widetext}
-
-% Equations for mixing coefficients
-\begin{widetext}
-  \input{src/ysprod_eqns}
-\end{widetext}
-
 % Plots of QNM frequencies
@@
   %
+  \label{fig:qnms}
+  %
 \end{figure*}
+%
+This implies that
+%
+\begin{align}
+  \label{eq:zd}
+  \cw_{\lmn} = m/2 + \kappa \sum_{j=1}^{J} c_j \kappa^k \; .
+\end{align}
+%
+In the case of the non-zero damped \qnm{s}, (e.g. $(\ell,m)=(3,2)$), a more general polynomial form may be adopted, namely,
+%
+\begin{align}
+  \label{eq:nzd}
+  \cw_{\lmn} = \sum_{j=0}^{J} c_j \kappa^k \; .
+\end{align}
+%
+\par The polynomial content of \eqn{eq:zd} and \eqn{eq:nzd} is determined by \gmvp{}.
+%
+\eqns{eq:cw_fit_1}{eq:cw_fit_9} display the resulting polynomial models.
+%
+Although each model's fractional error is within 2\%, each is error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current \gw{} efforts.
+%
+\par \fig{fig:qnms} displays select training points, as well as model fits for $\cw_{lmn}$'s real and imaginary parts.
+%
+For the right and left panels, simple polynomial behavior of each curve is a result of the displayed linear domain in $\kappa(\jf)$.
+%
+In the left panel, we have scaled $1/\tau_{\lmn}$ by factors for $m/(n+1/2)$ to place the \qnm{s} with $n=0$ and $n=1$ at approximately the same scale.
+%
+% Equations for QNM frequency fits
+\begin{widetext}
+	\input{src/cwfit_eqns}
+\end{widetext}
+%
+%
+\subsection{Modeling spherical-spheroidal inner-products using \gmvr{}}
+%
+%
+% Equations for mixing coefficients
+\begin{widetext}
+  \input{src/ysprod_eqns}
+\end{widetext}
 

### 2018-06-19 positive/learning.py
minor update to strings

@@ -2321,44 +2321,6 @@ def gmvpfit( domain,              # The N-D domain over which a scalar will be m
     return ans
 
 
-# Given a string with repeated symbols, convert the repetitions to power notation
-def rep2pwr( string,        # String to be processed
-             pattern,       # Pattern to look for
-             delimiter,     # Delimeter
-             latex=True,
-             pwrfun=None ): # Operation to apply to repetitios of the pattern, eg pwrfun = lambda pattern,N: '%s^%i'%(pattern,N)
-    '''
-    Given a string with repeated symbols, convert the repetitions to power notation.
-
-    Example:
-
-    >> a = '*x*x*x'
-    >> enpower(a,'*x')
-
-        x^{3}
-
-    '''
-
-    # Handle the power-function input
-    pwrfun = (lambda pattern,N: '{%s}^{%i}'%(pattern,N)) if pwrfun is None else pwrfun
-
-    # Find the maximum number of repetitions by noting it is bound above by the total number of parrtern instances
-    maxdeg = len(string.split(pattern)) # Technically there should be a -1 here, but let's leave it out to simplify things later on, and avoid buggy behavior
-
-    # Copy the input
-    ans = str(string) # .replace(' ','')
-
-    # Look for repetitions
-    for deg in range( maxdeg, 1, -1 ):
-        # Create a repeated pattern
-        reppat = delimiter.join( [ pattern for k in range(deg) ] )
-        # Look for the pattern, and replace it with the power representation
-        ans = ans.replace( reppat, pwrfun(pattern,deg) )
-
-    # Return the answer
-    return ans
-
-
 
 #%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#
 # Given a 1D array, determine the set of N lines that are optimally representative  #

### 2018-06-19 positive/strings.py

@@ -260,3 +260,42 @@ def rand_str(size=2**4, characters=string.ascii_uppercase + string.digits):
     characters = ''.join(set(characters))
     # return the random string
     return ''.join(random.choice(characters) for _ in range(size))
+
+
+
+# Given a string with repeated symbols, convert the repetitions to power notation
+def rep2pwr( string,        # String to be processed
+             pattern,       # Pattern to look for
+             delimiter,     # Delimeter
+             latex=True,
+             pwrfun=None ): # Operation to apply to repetitios of the pattern, eg pwrfun = lambda pattern,N: '%s^%i'%(pattern,N)
+    '''
+    Given a string with repeated symbols, convert the repetitions to power notation.
+
+    Example:
+
+    >> a = '*x*x*x'
+    >> enpower(a,'*x')
+
+        x^{3}
+
+    '''
+
+    # Handle the power-function input
+    pwrfun = (lambda pattern,N: '{%s}^{%i}'%(pattern,N)) if pwrfun is None else pwrfun
+
+    # Find the maximum number of repetitions by noting it is bound above by the total number of parrtern instances
+    maxdeg = len(string.split(pattern)) # Technically there should be a -1 here, but let's leave it out to simplify things later on, and avoid buggy behavior
+
+    # Copy the input
+    ans = str(string) # .replace(' ','')
+
+    # Look for repetitions
+    for deg in range( maxdeg, 1, -1 ):
+        # Create a repeated pattern
+        reppat = delimiter.join( [ pattern for k in range(deg) ] )
+        # Look for the pattern, and replace it with the power representation
+        ans = ans.replace( reppat, pwrfun(pattern,deg) )
+
+    # Return the answer
+    return ans

### 2018-06-23 docs/mvfits_paper/mvf.tex
misc

@@
 %
-Each term is an element of the n-fold cartesian inner-product of the power-sets of each model dimension.
+Each term is an element of the $n$-fold cartesian inner-product of the power-sets of each model dimension.
 That is $\mlam_{bulk} = \{x_0,x_1 ..
@@
     \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the n-fold cartesian inner-product of the power set of each basis symbol
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol
     \State Define $\mathcal{A}_{\gmvp{}}$ according to Alg. (\ref{alg:A_gmvp}).
-    \State Given $max\_order$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
+    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
     \For {$d$ \textbf{in}  ${ D}$ }
@@
     \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the n-fold cartesian inner-product of the power set of each basis symbol.
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol.
 This is the combined bulk for numerator and denominator symbols.
     \State Define $\mathcal{A}_{\gmvr{}}$ according to Alg. (\ref{alg:A_gmvr}).
-    \State Given $max\_order$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
+    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
     \For {$d$ \textbf{in}  ${ D}$ }

### 2018-06-23 positive/maths.py

@@ -2049,3 +2049,9 @@ def rotate3(vector,alpha,beta,gamma,invert=False):
 
     #
     return ans
+
+#
+def hilbertclean( complex_data ):
+
+    #
+    return None

### 2018-06-26 docs/mvfits_paper/mvf.tex
updating docs

@@
     \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
-    \State Calculate the model representation error, e.g.: $\epsilon = |var(\hatU \vecmu - \vec{f})|/var(\vec{f})$, where $var$ is the variance of the respective list.
+    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $var$ is the variance of the respective list.
     \vskip 10pt
@@
     \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
-    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = |var(g^{(n)} - g^{(0)})|/var(g^{(0)})$.
+    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$.
     \State $done = False$
@@
       \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
-      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = |var(g^{(n)} - g^{(0)})|/var(g^{(0)})$.
-      \State $done = |\epsilon^{(n)}-\epsilon^{(n-1)}| < tol$
-      \State Implicitly, $n = n+1$
+      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
+      \State $done = \epsilon^{(n-1)}-\epsilon^{(n)} < tol$
+      \State (Implicitly, $n = n+1$)
     \EndWhile
@@
 %
-\par We present the application of \gmvp{} and \gmvr{} to the respective modeling of \qnm{} frequencies, and harmonic mixing coefficients.
+\par We briefly review the application of \gmvr{} to a toy problem.
+%
+% Cross validation and removal of the last added basis symbol are used to assess model accuracy.
+%
+% \par
+%
+We then present the application of \gmvp{} and \gmvr{} to the respective modeling of \qnm{} frequencies, and harmonic mixing coefficients.
 %
 While each case is an instance of modeling on a 1D domain, we note that higher dimensional cases have been treated elsewhere \cite{London:2018gaq}.
+%
+\subsection{\gmvr{} Toy Problem}
+%
+Here
 %
@@
   \label{fig:qnms}
+  %
+\end{figure*}
+%
+% Plots of QNM frequencies
+\begin{figure*}
+  %
+  \begin{tabular}{lcr}
+    \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
+  \end{tabular}
+  %
+	\caption{ Fractional residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+}
+  %
+  \label{fig:qnm_err}
   %

### 2018-06-28 docs/mvfits_paper/mvf.tex
adding plots for toy problem and new python issues

@@
 %
-In that setting, the \qnm{} frequencies impact the morphology of each $h\LM$ in not only \rd{}, but also merger and late inspiral.
+In that setting, it is demonstrated that \qnm{} frequencies correlate with the morphology of each $h\LM$ in not only \rd{}, but also merger and late inspiral, as is implied by the causal connectedness of pre and post merger.
 %
@@
 %
-The study of smooth scalar functions (e.g. $\vecf$) often centers about the Taylor series expansion.
+The study of smooth scalar functions (e.g. $f(\vec{x})$) often centers about the Taylor series expansion.
 %
@@
 
+% Plots of mixing coefficients
+\begin{figure*}
+  %
+  \begin{tabular}{lcr}
+    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}
+  \end{tabular}
+  %
+	\caption{ Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
+  %
+\end{figure*}
+
 %

### 2018-06-30 docs/mvfits_paper/mvf.tex
updating docs

@@
 
-\title{Notes on modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients }
+\title{On modeling for Kerr black holes: Basis learning, QNM frequencies, and spherical-spheroidal mixing coefficients }
 
@@
 Towards the construction of these models, two algorithms, GMVP and GMVR, for the automated polynomial and rational modeling of general dimensional complex scalars are presented.
+GMVR is a quasi-linear numerical method for interpolating rational functions.
+It therefore represents a solution to the problem of Runge's phenomenon.
 	%
@@
 %
-From the first to second line of \eqn{eq:mvt}, we have used the definition of the exponential function (i.e. its series expansion form).
+From the first to second line of \eqn{eq:mvt}, we have used the definition of the exponential function (i.e. its series expansion).
 %
@@
 %
-The adjustments of perspective result in
+These adjustments of perspective result in
 %
@@
 %
-\par The key to robustly solving for $\vec{\alpha}$ lies in the iterative refinement of $\vec{\alpha}$.
+\par The key to robustly solving for $\vec{\alpha}$ lies in the iterative refinement.
 %
@@
 %
-\par We briefly review the application of \gmvr{} to a toy problem.
+\par We briefly review the application of \gmvr{} to a toy problem wherein a scalar rational function of two variables is treated.
 %
@@
 %
-We then present the application of \gmvp{} and \gmvr{} to the respective modeling of \qnm{} frequencies, and harmonic mixing coefficients.
+We then present two applications to \gw{s}.
 %
-While each case is an instance of modeling on a 1D domain, we note that higher dimensional cases have been treated elsewhere \cite{London:2018gaq}.
+First we apply \gmvp{} to the modeling of complex valued Kerr \qnm{} frequencies.
+%
+Second, we apply \gmvr{} to the modeling of spin -2 spherical-spheroidal harmonic mixing coefficients.
+%
+While only 1D and 2D domains are treated here, we note that Ref. \cite{London:2018gaq} has used a version of \gmvp{} to model the \qnm{} excitation amplitudes in a 4D parameter space.
 %
@@
 %
-Here
+Here we demonstrate \gmvr{}
+%
+\begin{figure*}
+  %
+  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}
+  %
+	\caption{ Standard summary plot for \gmvr. }
+  %
+\end{figure*}
+
+%
+\begin{figure}[htb]
+  %
+  \includegraphics[width=0.45\textwidth]{fig/issue3_pgreedy.pdf}
+  %
+	\caption{ Convergence of greedy process for \gmvr{} toy problem. }
+  %
+\end{figure}
+
 %

### 2018-07-04 docs/mvfits_paper/mvf.tex
updating docs and maths with reflect_unwrap for point reflections

@@
 %
-An explicit sktech of this is given by Alg. (\ref{alg:A_gmvp}).
+An explicit sketch of this is given by Alg. (\ref{alg:A_gmvp}).
 %
@@
     \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
-    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $var$ is the variance of the respective list.
+    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the L-2 norm of $a$.
     \vskip 10pt
@@
 %
-Here we demonstrate \gmvr{}
+Let's start by applying \gmvr{} to a fiducial scalar function,
+%
+\begin{align}
+  %
+  f(x_0,x_1) = 50 + \frac{1.1 +0.2 x_0+0.5 x_1+x_0 x_1}{ 0.9 + x_0^2 + x_1^2 }
+\end{align}
 %

### 2018-07-04 positive/learning.py

@@ -307,7 +307,7 @@ class mvrfit:
         from matplotlib.pyplot import plot,figure,title,xlabel,ylabel,legend,subplots,gca,sca,xlim,yticks
         from numpy import diff,linspace,meshgrid,amin,amax,ones,array,angle,ones,sqrt,pi,mean
         from mpl_toolkits.mplot3d import Axes3D
-        from scipy.stats import norm
+        from scipy.stats import norm,uniform
         from matplotlib.ticker import ScalarFormatter
 
         # Handle optinal map input: transform the range values for plotting use
@@ -334,8 +334,12 @@ class mvrfit:
         xmin,xmax=xlim()
         x = linspace( mu-3*std, mu+3*std, 2e2 )
         pdf =  norm.pdf( x, mu, std ) * sum(n) * (bins[1]-bins[0])
+
+        umu,ustd = uniform.fit( res )
+        updf =  uniform.pdf( x, umu, ustd ) * sum(n) * (bins[1]-bins[0])
         # pdf =  norm.pdf( x, mu, std ) * len(res) * (bins[1]-bins[0])
-        plot( x, pdf, color=color, label='Normal Approx.' )
+        plot( x, pdf, color=color, label='Normal Approx.', ls='-' )
+        plot( x, updf, color='k', label='Uniform Approx.', ls='--' )
         #xlim(lim(bins))
         xfmt = ScalarFormatter()
         xfmt.set_useOffset(0)
@@ -476,7 +480,7 @@ class mvrfit:
         scalar_range = this.scalar_range
 
         # Plot the raw data points
-        ax.scatter( domain[:,0], domain[:,1], _map(scalar_range), marker='o', color='k',zorder=1, facecolors='k',label='Raw Data')
+        ax.scatter( domain[:,0], domain[:,1], _map(scalar_range), marker='o', color='k',zorder=1, facecolors='k',label='Training Data')
 
         # Setup grid points for model
         padf = 0.1
@@ -495,6 +499,10 @@ class mvrfit:
         # ax = gcf().add_subplot(122,projection='3d')
         # ax.scatter( domain[:,0], domain[:,1], this.residuals.reshape( domain[:,0].shape ), marker='o', color='b',zorder=1, facecolors='k',label='Residuals')
         # legend(frameon=False)
+
+        #
+        ax.set_xlabel('$x_0$',size=24)
+        ax.set_ylabel('$x_1$',size=24)
 
         #
         if show:
[…]

### 2018-07-04 positive/maths.py

@@ -2050,8 +2050,33 @@ def rotate3(vector,alpha,beta,gamma,invert=False):
     #
     return ans
 
-#
-def hilbertclean( complex_data ):
+# Look for point reflections in vector and correct
+def reflect_unwrap( vec ):
+    '''Look for point reflections in vector and correct'''
 
     #
-    return None
+    from numpy import array,sign,zeros_like
+
+    #
+    ans = array(vec)
+
+    #
+    for k,v in enumerate(vec):
+
+        #
+        if (k>0) and ( (k+1) < len(vec) ):
+
+            #
+            l = vec[k-1]
+            c = vec[k]
+            r = vec[k+1]
+
+            #
+            apply_reflection = (sign(l)==sign(r)) and (sign(l)==-sign(c))
+            if apply_reflection:
+
+                #
+                ans[k] *= -1
+
+    #
+    return ans

### 2018-07-04 positive/strings.py

@@ -204,7 +204,7 @@ def complex2str( x, precision=None, latex=False ):
             # Write phase as positive number
             phase = phase+2*pi if phase<0 else phase
             # Create string
-            fmt = '%s.%ig'%(r'%',precision)
+            fmt = '%s.%if'%(r'%',precision)
             # fmt = '%s1.%if'%(r'%',precision)
             ans_ = '%s*%s%s%s' % (fmt, 'e^{' if latex else 'exp(' ,fmt, 'i}' if latex else 'j)') % (amp,phase)
             if latex: ans_ = ans_.replace('*',r'\,')

### 2018-07-09 positive/learning.py
Add proof of concept documentation with Sphinx
Provides a minimal welcome page and documentation for the two main
driver function `gmvpfit` and `gmvrfit`.

@@ -674,7 +674,46 @@ def gmvrfit( domain,
              take_raw_symbols = True,
              apply_negative = True,
              **kwargs ):
+    """Adaptive (Greedy) Multivariate rational fitting
 
+    Supports general domain dimension, but range must be 1D (possibly complex).
+
+    Parameters
+    ----------
+    domain: list
+        The N-D domain over which a scalar will be modeled. List of vector
+        coordinates.
+    scalar_range: list
+        The scalar range to model on the domain. 1d iterable of range values
+        corresponding to domain entries.
+    maxdeg: int, optional
+        Polynomial degrees of at most this order in domain variables will be
+        considered: e.g. x*y and y*y are both degree 2. NOTE that the effective
+        degree will be optimized over: increased incrementally until the model
+        becomes less optimal.
+    mindeg: int, optional
+        Minimum degree to consider for tempering.
+    fitatol: float, optional
+        Tolerance in fractional chance in estimator.
+    initial_boundary: list, optional
+        Seed boundary for positive greedy process.
+    plot: bool, optional
+        Toggle plotting.
+    show: bool, optional
+        Toggle for showing plots as they are created.
+    verbose: bool, optional
+        Let the people know.
+    take_raw_symbols: bool, optional
+        By defualt, adjust numerator symbols according to range centering.
+    apply_negative: bool, optional
+        Toggle for the application of a negtative greedy algorithm following
+        the positive one. This is set true by default to handle overmodelling.
+
+    Returns
+    -------
+    fit: :class:`positive.mvpolyfit`
+        Polynomial model fit over `scalar_range`.
+    """
     # Import stuff
     from itertools import combinations as combo
     from itertools import product as cartesian_product
@@ -2192,7 +2231,58 @@ def gmvpfit( domain,              # The N-D domain over which a scalar will be m
              homogeneous=False,     # Toggle for homogenous polynomials
              maxres_estimator = False, # Toggle for using abs of max residual as estimator rather then frmse
              **kwargs ):
-    '''Adaptive (Greedy) Multivariate polynomial fitting: general domain dimension, but range must be 1D (possibly complex).'''
+    """Adaptive (Greedy) Multivariate polynomial fitting
+
+    Supports general domain dimension, but range must be 1D (possibly complex).
+
+    Parameters
+    ----------
+    domain: list
+        The N-D domain over which a scalar will be modeled. List of vector
+        coordinates.
+    scalar_range: list
[…]

### 2018-07-12 docs/mvfits_paper/mvf.tex
adding Ed to doc

@@
 
+\newcommand{\Cardiff}{School of Physics and Astronomy, Cardiff University, Queens Buildings, Cardiff, CF24 3AA, United Kingdom}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 \author{L. London}
-\affiliation{School of Physics and Astronomy, Cardiff University, The Parade, Cardiff, CF24 3AA, United Kingdom}
+\affiliation{\Cardiff}
+\author{Edward Fauchon-Jones}
+\affiliation{\Cardiff}
 
@@
 %
-Let's start by applying \gmvr{} to a fiducial scalar function,
+Here, our goal is to very brielfy assess
+%
+Let's start by applying \gmvr{} to a fiducial scalar function of the form
 %
@@
   %
-  f(x_0,x_1) = 50 + \frac{1.1 +0.2 x_0+0.5 x_1+x_0 x_1}{ 0.9 + x_0^2 + x_1^2 }
+  % f(x_0,x_1) = 50 + \frac{1.1 +0.2 x_0+0.5 x_1+x_0 x_1}{ 0.9 + x_0^2 + x_1^2 }
+  %
+  f(x_0,x_1) = \mu + \sigma \, \left( \, \frac{a_0 +a_1  x_0 + a_2 x_1 + a_3 x_0 x_1}{ 1 + b_1 \, x_0^2 +  b_2 x_1^2 } \, \right) + 0.05 \, n \; ,
 \end{align}
+%
+where $n$ is a uniform random variable on $[-1,1]$.
+%
+Towards easily identifying test values for $a_j$ and $b_k$ with those recovered, it is more straightforward to distribute $\sigma$ to the denominator, yielding
+%
+\begin{align}
+  \label{eq:gmvrtoy1}
+  f(x_0,x_1) = \mu + \, \frac{a_0 +a_1  x_0 + a_2 x_1 + a_3 x_0 x_1}{ 1/\sigma + (b_1/\sigma) \, x_0^2 +  (b_2/\sigma) x_1^2 } + 0.05 \, n \; .
+\end{align}
+%
+Under this perspective we will consider test data generated with the following parameters:
+%
+$\mu = 50.0$,
+%
+$a_0 = 1.1$,
+%
+$a_1 = 0.2$,
+%
+$a_3 = 1.0$,
+%
+$1/\sigma = 0.9$,
+%
+$b_1/\sigma = b_2/\sigma = 1.0$.
+%
+\par To generate the test data, \eqn{eq:gmvrtoy1} is evaluated with 25 points in $x_0$ and $x_1$, where each is between -3 and 3.
+%
+\par \fig{fig:gmvrtoy} shows the application of \gmvr{} to this fiducial dataset.
+%
+\fig{fig:gmvrtoy}'s central bottom panel displays the distribution of fractional residuals, and demonstrates their approximately flat distribution.
+A gaussian fit to the fractional residuals is displayed only for optical comparison.
+%
+We find that the direct sample residuals are $99.46\%$ correlated with the input noise.
+%
+\par \fig{fig:gmvrtoy}'s left top and bottom panels show the convergence of Alg. (\ref{alg:A_gmvr})'s iterative refinement stage (i.e. its while-loop).
+%
+Here it is demonstrated that \gmvr{} converges exponentially, as expected given th.
+%
 %
@@
   %
+  \label{fig:gmvrtoy}
+  %
 \end{figure*}
@@
   \includegraphics[width=0.45\textwidth]{fig/issue3_pgreedy.pdf}
-  %
 	\caption{ Convergence of greedy process for \gmvr{} toy problem. }

### 2018-07-15 docs/mvfits_paper/mvf.tex
updating paper

@@
 \affiliation{\Cardiff}
-\author{Edward Fauchon-Jones}
+\author{E. Fauchon-Jones}
 \affiliation{\Cardiff}
@@
 %
-Here, our goal is to very brielfy assess
+Here, our goal is to very briefly overview the functionality of the \gmvr{} algorithm as implemented in Ref. \red{[positive]}.
 %
-Let's start by applying \gmvr{} to a fiducial scalar function of the form
+While it is possible to investigate the output of \gmvr{} with varying hyper-parameters (such as the tolerance input to Alg. \ref{alg:gmvr}), we will focus only on a simple usage case.
+%
+Similarly, we note that \gmvr{} as implemented in Ref. \red{[positive]} involves a reverse (or negative) greedy step to counter over-modeling in cases where the aforementioned $tol$ is too low.
+%
+For relevance of presentation to physics examples in subsequent sections, we will restrict ourselves to a case where numerical noise is low, and the negative greedy step does not alter the output of Alg.
+\ref{alg:gmvr}).
+%
+%
+\par Let's start by applying \gmvr{} to a fiducial scalar function of the form
 %
@@
 %
-Here it is demonstrated that \gmvr{} converges exponentially, as expected given th.
+Here it is demonstrated that \gmvr{} in a way that is approximately exponential, owing to the underlying analytic nature of the training data.
 %

### 2018-07-17 docs/mvfits_paper/mvf.tex

@@
 %
-is the \textit{pseudo-inverse} of $\hatU$.
+is the \textit{pseudo-inverse} \cite{Moore1920,Penrose:1955} of $\hatU$.
 %
@@
 %
-\par While it is tempting to embrace \eqn{eq:rat1}'s $f({\vec{x}})$ as a nonlinear function and so resort to nonlinear modeling methods, a reformulation reveals an underlying linear structure.
+\par While it is tempting to embrace \eqn{eq:rat1}'s $f({\vec{x}})$ as a nonlinear function and so resort to nonlinear modeling methods, a reformulation reveals an underlying linear structure \cite{Press:1992:NRC:148286}.
 %

### 2018-07-17 docs/mvfits_paper/mvf.tex
adding toy problem plots

@@
 %
-\par While it is tempting to embrace \eqn{eq:rat1}'s $f({\vec{x}})$ as a nonlinear function and so resort to nonlinear modeling methods, a reformulation reveals an underlying linear structure \cite{Press:1992:NRC:148286}.
+\par While it is tempting to embrace \eqn{eq:rat1}'s $f({\vec{x}})$ as a nonlinear function and so resort to nonlinear modeling methods, a reformulation reveals an underlying linear structure  \cite{Press:1992:NRC:148286}..
 %
@@
 %
-Put another way, rather than two greedy optimizations over $R$ and $V-1$ symbols (with $(V-1)R$ iterations), a single greedy process over $V+R$ symbols is performed.
+Put another way, rather than two simulteneous greedy optimizations over $R$ and $V-1$ symbols (with $(V-1)R$ iterations), a single greedy process over $V+R$ symbols is performed.
 %
@@
 $a_1 = 0.2$,
+%
+$a_2 = 0.5$,
 %

### 2018-07-23 docs/mvfits_paper/mvf.tex
completing gmvr topy problem section ... for now

@@
 %
-Under this perspective we will consider test data generated with the following parameters:
-%
-$\mu = 50.0$,
-%
-$a_0 = 1.1$,
-%
-$a_1 = 0.2$,
-%
-$a_2 = 0.5$,
-%
-$a_3 = 1.0$,
-%
-$1/\sigma = 0.9$,
-%
-$b_1/\sigma = b_2/\sigma = 1.0$.
+Under this perspective we will consider test data generated with the parameters listed in \tbl{tb:gmvrtoy}'s left two panels.
 %
@@
 \fig{fig:gmvrtoy}'s central bottom panel displays the distribution of fractional residuals, and demonstrates their approximately flat distribution.
-A gaussian fit to the fractional residuals is displayed only for optical comparison.
+A gaussian fit to the fractional residuals is displayed only for comparison.
+In particular, a biased fit will often have residuals that are approximately gaussian; we see that this is not the case here, and that the uniformly random noise distribution is approximately recovered.
 %
-We find that the direct sample residuals are $99.46\%$ correlated with the input noise.
+When considering many noise realizations, we find that sample noise and residuals have a typically correlation of $99.46\%$.
 %
@@
 Here it is demonstrated that \gmvr{} in a way that is approximately exponential, owing to the underlying analytic nature of the training data.
+%
+\tbl{tb:gmvrtoy} demonstrates \gmvr{}'s accurate recovery of the underlying model parameters.
+We note that that in going from \gmvr{}'s initial output contains terms in the numerator which correspond to the addition of a constant to the overall model, thus correcting for the difference between the offset parameter, $\mu$, and the true, but arbitrary, mean of the dataset.
+%
+%
+% $\mu = 50.0$,
+% %
+% $a_0 = 1.1$,
+% %
+% $a_1 = 0.2$,
+% %
+% $a_2 = 0.5$,
+% %
+% $a_3 = 1.0$,
+% %
+% $1/\sigma = 0.9$,
+% %
+% $b_1/\sigma = b_2/\sigma = 1.0$.
+%
+\begin{table}
+  \caption{Summary of recovered model parameters for \gmvr{} toy problem.}
+  \label{tb:gmvrtoy}
+  \begin{tabular}{|c|c|c|c|}
+    \hline
+    \hline
+    Parameter & Training Value & Modeled Value & Difference \\ \hline \hline
+    $\mu$ & 50.0 & 49.9915 & 0.0171 \% \\ \hline
+    $a_0$ & 1.1 & 1.1374 & 3.4002 \% \\ \hline
+    $a_1$ & 0.2 & 0.2000 & 0.0000 \% \\ \hline
+    $a_2$ & 0.5 & 0.5068 & 1.36784 \% \\ \hline
+    $a_3$ & 1.0 & 1.0063 & 0.6300 \% \\ \hline
+    $1/\sigma$ & 0.9 & 0.9375 & 4.1612 \% \\ \hline
+    $b_1/\sigma$ & 1.0 & 0.9941 & 0.5906 \% \\ \hline
+    $b_2/\sigma$ & 1.0 & 1.0000 & 0.0000 \% \\ \hline
+    \hline
+  \end{tabular}
+
+\end{table}
+%
+%
+\par Here, it is clear that \gmvr{} correctly recovers the functional form of the input data.
+In general, \gmvr{} and related techniques will attempt to model minor correlations and offsets within the training data's noise.
+%
+However, we have demonstrated the utility of \gmvr{} in a relatively ideal usage case where the underlying function is rational, and the training data is inly weakly contaminated with noise.
+%
+In the following sections, we consider cases where the functional form of the sample data is not known to be explicitly rational, but the amount of noise within the training data is negligible.
 %

### 2018-07-23 docs/mvfits_paper/mvf.tex
completing gmvr topy problem section ... for now

@@
 \tbl{tb:gmvrtoy} demonstrates \gmvr{}'s accurate recovery of the underlying model parameters.
-We note that that in going from \gmvr{}'s initial output contains terms in the numerator which correspond to the addition of a constant to the overall model, thus correcting for the difference between the offset parameter, $\mu$, and the true, but arbitrary, mean of the dataset.
+%
+We note that \gmvr{}'s initial output contains terms in the numerator which correspond to the addition of a constant to the overall model, thus correcting for the difference between the offset parameter, $\mu$, and the true, but arbitrary, mean of the dataset.
+%
+\tbl{tb:gmvrtoy} presents recovered model parameters after this effect has been accounted for with simple algebraic manipulation.
 %
@@
 %
-\par Here, it is clear that \gmvr{} correctly recovers the functional form of the input data.
-In general, \gmvr{} and related techniques will attempt to model minor correlations and offsets within the training data's noise.
+\par In this example case, \gmvr{} correctly recovers the functional form of the input data.
+But, in general, \gmvr{} and related techniques will attempt to model minor correlations and offsets within the training data's noise.
 %

### 2018-07-27 docs/mvfits_paper/mvf.tex
updating paper

@@
 %
-\par In particular, a perturbed Kerr \bh{} (e.g. resulting from \bbh{} merger) will have \gw{} radiation that rings down with characteristic frequencies,
+\par In particular, a perturbed Kerr \bh{} (e.g. resulting from \bbh{} merger) will have \gw{} radiation that rings down with characteristic \textit{dimensionless} frequencies,
 %
@@
 %
-When considering many noise realizations, we find that sample noise and residuals have a typically correlation of $99.46\%$.
+When considering many noise realizations, we find that sample noise and residuals have an average correlation of $99.46\%$.
 %
@@
 \par In this example case, \gmvr{} correctly recovers the functional form of the input data.
-But, in general, \gmvr{} and related techniques will attempt to model minor correlations and offsets within the training data's noise.
+But, in general, \gmvr{} and related techniques, having no knowledge of , will attempt to model minor correlations and offsets within the training data's noise.
 %
@@
 \end{figure}
-
 %
+%
+%
+%
+% %%%%%%
 \subsection{Modeling \qnm{} frequencies using \gmvp{}}
+% %%%%%%
 %
-In seeking to apply \gmvp{} to select \qnm{} frequencies, we wish to impose a zero-damping constraint, namely that some frequencies are real as $\jf \rightarrow 1$.
 %
-We also wish the impose a domain transformation, $\kappa(\jf)$, such that $0 \leq \kappa \leq 1$ and the individual \qnm{} frequencies are morphologically simplified.
+%
+In seeking to apply \gmvp{} to select \qnm{} frequencies, we wish to account for the known extremal Kerr behavior of some modes.
+%
+Namely, we will impose a zero-damping constraint: some frequencies are real as $\jf \rightarrow 1$.
+%
+We also wish the impose a domain transformation, $\kappa(\jf,\ell,m)$, such that $0 \leq \kappa \leq 1$ and the individual \qnm{} frequencies are made approx. polynomial in $\kappa$.
 %
@@
 \begin{align}
-  \kappa(\jf) = \left( \ln( 2 - \jf ) / \ln(3) \right)^{1/(2-\ell+|m|)}
+  \kappa(\jf,\ell,m) = \left( \log_3( 2 - \jf ) \right)^{1/(2-\ell+|m|)}
 \end{align}
 %
-appropriately linearizes the sharp behavior of each frequency near $\jf=1$.
+appropriately linearizes the sharp behavior of each frequency near $\jf=1$, and maps $-1 \le \jf \le 1$ onto $0 \le \kappa \le 1$.
 %
-\par For the zero-damping constraint, when considering a \qnm{} frequency $\cw_{\lmn}$, zero-damping at $\jf=1$ implies that $\cw_{\lmn}(\kappa \approx 0)-m/2 \propto \kappa$, where $m/2$ is the well known limiting value for each \qnm{} frequencies real part as $\jf\rightarrow 1$.
+\par Towards the zero-damping constraint, when considering a \qnm{} frequency $\cw_{\lmn}$, zero-damping at $\jf=1$ implies that $\cw_{\lmn}(\kappa \approx 0)-m/2 \propto \kappa$, where $m/2$ is the well known limiting value for each \qnm{} frequencies real part as $\jf\rightarrow 1$.
 %
@@
 %
-Although each model's fractional error is within 2\%, each is error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current \gw{} efforts.
+In particular, the domain map allows most \qnm frequencies to be well modeled by 4th order polynomials which include all lower degree terms; concurrently, the real and imaginary parts of each $\cw\lmn$ are modeled simultaneously.
 %
-\par \fig{fig:qnms} displays select training points, as well as model fits for $\cw_{lmn}$'s real and imaginary parts.
+Although each model's fractional error is within 2\%, each is error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current 2nd generation \gw{} efforts.
 %
-For the right and left panels, simple polynomial behavior of each curve is a result of the displayed linear domain in $\kappa(\jf)$.
+\par \fig{fig:qnms} displays select training points, as well as model fits for $\cw\lmn$'s real and imaginary parts.
 %
-In the left panel, we have scaled $1/\tau_{\lmn}$ by factors for $m/(n+1/2)$ to place the \qnm{s} with $n=0$ and $n=1$ at approximately the same scale.
+For the right and left panels, simple polynomial behavior of each curve is a result of the displayed linear domain in $\kappa(\jf,\ell,m)$.
+%
+In the left panel, we have scaled $1/\tau\lmn$ by factors for $m/(n+1/2)$ to place the \qnm{s} with $n=0$ and $n=1$ at approximately the same scale.
 %
@@
 %
+\par In each panel of \fig{fig:qnms}, the horizontal upper and lower demonstrate the effect of mapping $\jf$ onto $\kappa$.
+%
+In particular, it is shown that the two solution branches ($\jf>0$ and $\jf<0$) naturally form a single family of solutions when accounting for the sign of the \bh{}'s oriented spin.
+%
+Concurrently, the use of $\kappa$ as a domain variable has the desirable effect of making each $\cw\lmn$ and $\tau\lmn$ approximately parabolic.
+%
+We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate.
+%
+In allowing \eqns{eq:cw_fit_1}{eq:cw_fit_9} to extrapolate to $\jf \sim 1$, we do not explicitly account for this additional effect.
 %

### 2018-08-07 docs/mvfits_paper/mvf.tex
updating qnm freq section

@@
 %
-Second, we will build upon the \gmvp{} approach by considering models of rational functions: polynomials divided by polynomilas.
+Second, we will build upon the \gmvp{} approach by considering models of rational functions: polynomials divided by polynomials.
 %
@@
 %
-This latter point is key to the perspective of \gmvp{}: given training data thought to be related to a smooth multivariate function, it may be well approximated by a truncated series expansion in the appropriate coordinate basis.
+This latter point is key to the perspective of \gmvp{}: given training data thought to be related to a smooth multivariate function, it may be well approximated by a truncated series expansion in an appropriate coordinate basis.
 %
@@
 %
-At this stage, we will also explicitely consider the $j^\mathrm{th}$ samples of the domain, and so refer to $\vec{x}$ as $\vec{x}_j$.
+At this stage, we will also explicitly consider the $j^\mathrm{th}$ samples of the domain, and so refer to $\vec{x}$ as $\vec{x}_j$.
 %
@@
 %
-Put another way, rather than two simulteneous greedy optimizations over $R$ and $V-1$ symbols (with $(V-1)R$ iterations), a single greedy process over $V+R$ symbols is performed.
+Put another way, rather than two simultaneous greedy optimizations over $R$ and $V-1$ symbols (with $(V-1)R$ iterations), a single greedy process over $V+R$ symbols is performed.
 %
@@
 \begin{align}
+  \label{eq:kappa}
   \kappa(\jf,\ell,m) = \left( \log_3( 2 - \jf ) \right)^{1/(2-\ell+|m|)}
@@
 %
-Although each model's fractional error is within 2\%, each is error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current 2nd generation \gw{} efforts.
-%
 \par \fig{fig:qnms} displays select training points, as well as model fits for $\cw\lmn$'s real and imaginary parts.
@@
 %
+\par Lastly, \fig{fig:qnm_err} shows residual errors.
+%
+Although each model's fractional error is within 2\%, each is error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current 2nd generation \gw{} efforts.
+%
+\par Together, \eqns{eq:cw_fit_1}{eq:cw_fit_9} along with Figures (\ref{fig:qnms})-(\ref{fig:qnm_err}) present precise and accurate fits for the real and imaginary parts of \qnm{} frequencies for gravitational perturbations of Kerr \qnm{s}.
+%
 \subsection{Modeling spherical-spheroidal inner-products using \gmvr{}}
 %
+Here we apply \gmvr{} to the spherical-spheroidal mixing coefficients, $\sigma_{\LMlmn}$.
+%
+As in the case of the \qnm{} frequencies, we use the domain transformation defined by \eqn{eq:kappa} to simplify the functional form of each $\sigma_{\LMlmn}$.
+%
+\par While it is possible to enforce extremal Kerr conditions $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for all $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.
+%
+% \par \eqns{}
 %

### 2018-08-21 docs/mvfits_paper/mvf.tex
resutructuring draft to include appendix
fixing typo; adding to doc and paper

@@
 \def\NumCalibrationPoints{\red{61} }
+
+\def\pgreedy{\texttt{PGREEDY}}
 
@@
 %
-\par Note that we will use the terms ``basis vector'' and ``model symbol'' interchangeably.
-However, in practice, it can be useful to represent basis vectors symbolically (e.g.
-with strings), and have a way of bijectively mapping between symbols and numerical basis vectors.
-%
-% \par
-%
 % Forward greedy algo
 \hspace{1cm}
-\def\pgreedy{\texttt{PGREEDY}}
 {\scriptsize
@@
 }
-
+%
+%
+\par Note that we will use the terms ``basis vector'' and ``model symbol'' interchangeably.
+However, in practice, it can be useful to represent basis vectors symbolically (e.g.
+with strings), and have a way of bijectively mapping between symbols and numerical basis vectors.
+%
+% \par
+%
 %
@@
 %
-\hspace{1cm}
-{\scriptsize
-\begin{algorithm}[H]
-  %
-  \caption{$\mathcal{A}_{\gmvp}$, the action for \gmvp. Model calculation given basis symbols, and output of model error estimate.}
-  %
-  \label{alg:A_gmvp}
-  \begin{algorithmic}[1]
-    %
-    \State {\bf Input:} $\mlam_{trial}$
-    \vskip 10pt
-    \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
-    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the L-2 norm of $a$.
-    \vskip 10pt
-    \State {\bf Output:} $\epsilon$
-  \end{algorithmic}
-\end{algorithm}
-}
-%
 \par The combination of these two ideas alone results in an algorithm prone to a deficit of stepwise methods: the algorithm may confuse correlated basis vectors (e.g. $x^2$ may be confused for $x^4$).
@@
 The combination of degree tempering with the greedy approach results in the \gmvp{} algorithm as presented in Alg. (\ref{alg:gmvp}).
-%
-% GMVP
-\hspace{1cm}
-{\scriptsize
-\begin{algorithm}[H]
-  %
-  \caption{\gmvp{}, a degree tempered stepwise algorithm for multivariate polynomial modeling of scalar data.}
-  \label{alg:gmvp}
-  %
-  \begin{algorithmic}[1]
-    %
-    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
-    \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol
-    \State Define $\mathcal{A}_{\gmvp{}}$ according to Alg. (\ref{alg:A_gmvp}).
-    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
-    \For {$d$ \textbf{in}  ${ D}$ }
-      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
-      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
-      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
-        \State \textbf{break}
-      \EndIf
-    \EndFor
-    \vskip 10pt
-    \State {\bf Output:} $\mlam^{(d)}_{opt}$
-    %
-  \end{algorithmic}
-  %
-\end{algorithm}
-}
-%
 %
@@
 At this stage, we will also explicitly consider the $j^\mathrm{th}$ samples of the domain, and so refer to $\vec{x}$ as $\vec{x}_j$.
+%
+%
+\begin{figure*}[htb]
+  %
+  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}
+  %
+	\caption{ Standard summary plot for \gmvr. }
+  %
+  \label{fig:gmvrtoy}
+  %
+\end{figure*}
 %
@@
 %
-\hspace{1cm}
-{\scriptsize
-\begin{algorithm}[H]
-  %
-  \caption{$\mathcal{A}_{\gmvr}$, the action for \gmvr. Model calculation given basis symbols, and output of model error estimate.}
-  %
-  \label{alg:A_gmvr}
-  \begin{algorithmic}[1]
-    %
-    \State {\bf Input:} \{ $\mlam_{trial}$, $tol=10^{-3}$ \}
-    \vskip 10pt
-    \State Calculate $\alpha^{(1)}_k$ via \eqn{eq:pinv3}. Implicitly, $n=1$.
-    \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
-    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$.
-    \State $done = False$
-    \While { not $done$ }
-      \State Calculate $\alpha^{n+1}_{k}$  via \eqn{eq:pinv3}.
-      \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
-      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
-      \State $done = \epsilon^{(n-1)}-\epsilon^{(n)} < tol$
-      \State (Implicitly, $n = n+1$)
-    \EndWhile
-    \vskip 10pt
-    \State {\bf Output:} $\epsilon^{(n)}$
-  \end{algorithmic}
-\end{algorithm}
-}
-%
 \par The combination of \eqns{eq:pinv3} and \eqn{eq:rat4}, along with \pgreedy{} and degree tempering, results in the \gmvr{} algorithm as presented in Alg. (\ref{alg:gmvr}).
@@
 In each case, the underlying 1D parameter in each case will be the dimensionless \bh{} spin, $\jf{}$.
-%
-% GMVR
-\hspace{1cm}
-{\scriptsize
-\begin{algorithm}[H]
-  %
-  \caption{\gmvr{}, a degree tempered stepwise algorithm for multivariate rational modeling of scalar data.}
-  \label{alg:gmvr}
-  %
-  \begin{algorithmic}[1]
-    %
-    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
-    \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol.
-This is the combined bulk for numerator and denominator symbols.
-    \State Define $\mathcal{A}_{\gmvr{}}$ according to Alg. (\ref{alg:A_gmvr}).
-    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
-    \For {$d$ \textbf{in}  ${ D}$ }
-      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
-      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
-      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
-        \State \textbf{break}
-      \EndIf
-    \EndFor
-    \vskip 10pt
-    \State {\bf Output:} $\mlam^{(d)}_{opt}$
-    %
-  \end{algorithmic}
-  %
-\end{algorithm}
-}
 %
@@
 In the following sections, we consider cases where the functional form of the sample data is not known to be explicitly rational, but the amount of noise within the training data is negligible.
-%
-%
-\begin{figure*}
-  %
-  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}
-  %
-	\caption{ Standard summary plot for \gmvr. }
-  %
-  \label{fig:gmvrtoy}
-  %
-\end{figure*}
 
@@
 \par Towards the zero-damping constraint, when considering a \qnm{} frequency $\cw_{\lmn}$, zero-damping at $\jf=1$ implies that $\cw_{\lmn}(\kappa \approx 0)-m/2 \propto \kappa$, where $m/2$ is the well known limiting value for each \qnm{} frequencies real part as $\jf\rightarrow 1$.
-%
-% Plots of QNM frequencies
-\begin{figure*}
-  %
-  \begin{tabular}{lcr}
-    \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
-  \end{tabular}
-  %
-	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-  %
-  Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$.
-Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
-  %
-  The grey dashed line marks the value of $\kappa$ where $\j{}=0$.
-Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-}
-  %
-  \label{fig:qnms}
-  %
-\end{figure*}
-%
-% Plots of QNM frequencies
-\begin{figure*}
-  %
-  \begin{tabular}{lcr}
-    \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
-  \end{tabular}
-  %
-	\caption{ Fractional residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-}
-  %
-  \label{fig:qnm_err}
-  %
-\end{figure*}
 %
@@
 %
-\par While it is possible to enforce extremal Kerr conditions $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for all $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.
+\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for all $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.
 %
-% \par \eqns{}
+\eqns{eq:ys22220}{eq:ys55550} present the resulting model equations.
+%
+\fig{fig:ys} display comparisons of the fits with training data as well as related residuals.
+%
+For efficiency of presentation, each $\sigma_{\LMlmn}$ is plotted against its real and imaginary part.
+%
+In cases where $(\bar\ell,\bar{m})=(\ell,m)$, the real part of $\sigma_{\LMlmn}$ varies about unity in a manner consistent with the Schwarzschild limit, where $\sigma_{\LMlmn}=\delta_{\bar\ell}^{\ell}\;\delta_{\bar{m}}^{m}$.
+%
+This is equally true in cases where $(\bar\ell,\bar{m}) \neq (\ell,m)$.
+%
+As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent.
+
+%
+\section{Discussion}
+\label{discuss}
+
+%
+\appendix
+
+\section{Algorithms}
+\label{app:algos}
+
+% \begin{widetext}
+
+%
+% GMVR
+% \hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{\gmvr{}, a degree tempered stepwise algorithm for multivariate rational modeling of scalar data.}
+  \label{alg:gmvr}
+  %
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
+    \vskip 10pt
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol.
+This is the combined bulk for numerator and denominator symbols.
+    \State Define $\mathcal{A}_{\gmvr{}}$ according to Alg. (\ref{alg:A_gmvr}).
+    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
+    \For {$d$ \textbf{in}  ${ D}$ }
+      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
+      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
+      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
+        \State \textbf{break}
+      \EndIf
+    \EndFor
+    \vskip 10pt
+    \State {\bf Output:} $\mlam^{(d)}_{opt}$
+    %
+  \end{algorithmic}
+  %
+\end{algorithm}
+}
+%
+% GMVP
+% \hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{\gmvp{}, a degree tempered stepwise algorithm for multivariate polynomial modeling of scalar data.}
+  \label{alg:gmvp}
+  %
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
+    \vskip 10pt
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol
+    \State Define $\mathcal{A}_{\gmvp{}}$ according to Alg. (\ref{alg:A_gmvp}).
+    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
+    \For {$d$ \textbf{in}  ${ D}$ }
+      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
+      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
+      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
+        \State \textbf{break}
+      \EndIf
+    \EndFor
+    \vskip 10pt
+    \State {\bf Output:} $\mlam^{(d)}_{opt}$
+    %
+  \end{algorithmic}
+  %
+\end{algorithm}
+}
+%
+%
+% \hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{$\mathcal{A}_{\gmvr}$, the action for \gmvr. Model calculation given basis symbols, and output of model error estimate.}
+  %
+  \label{alg:A_gmvr}
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} \{ $\mlam_{trial}$, $tol=10^{-3}$ \}
+    \vskip 10pt
+    \State Calculate $\alpha^{(1)}_k$ via \eqn{eq:pinv3}. Implicitly, $n=1$.
+    \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
+    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$.
+    \State $done = False$
+    \While { not $done$ }
+      \State Calculate $\alpha^{n+1}_{k}$  via \eqn{eq:pinv3}.
+      \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
+      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
+      \State $done = \epsilon^{(n-1)}-\epsilon^{(n)} < tol$
+      \State (Implicitly, $n = n+1$)
+    \EndWhile
+    \vskip 10pt
+    \State {\bf Output:} $\epsilon^{(n)}$
+  \end{algorithmic}
+\end{algorithm}
+}
+%
+%
+% \hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{$\mathcal{A}_{\gmvp}$, the action for \gmvp. Model calculation given basis symbols, and output of model error estimate.}
+  %
+  \label{alg:A_gmvp}
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $\mlam_{trial}$
+    \vskip 10pt
+    \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
+    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the L-2 norm of $a$.
+    \vskip 10pt
+    \State {\bf Output:} $\epsilon$
+  \end{algorithmic}
+\end{algorithm}
+}
+
+% \end{widetext}
+
+\section{Equations}
+\label{app:eqns}
+
 %
 % Equations for mixing coefficients
+%
 \begin{widetext}
@@
 
-% Plots of mixing coefficients
+\section{Figures}
+\label{app:figs}
+
+%
+% Plots of QNM frequencies
 \begin{figure*}
   %
-  \begin{tabular}{lcr}
-    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf}
+  \begin{tabular}{lr}
+    \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
+    \\
+    \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
   \end{tabular}
   %
-	\caption{ Spherical-spheroidal harmonic mixing coefficients. }
+	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+  %
+  Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$.
+Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
+  %
+  The grey dashed line marks the value of $\kappa$ where $\j{}=0$.
+Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+(Bottom) Percentage residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+}
+  %
+  \label{fig:qnm}
   %
@@
   %
-  \begin{tabular}{lcr}
+  \begin{tabular}{lr}
+    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf} \\
     \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}
@@
   %
-	\caption{ Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
+	\caption{ Spherical-spheroidal harmonic mixing coefficients. Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
+  %
+  \label{fig:ys}
   %
 \end{figure*}
-
-%
-\section{Discussion}
-\label{discuss}
 

### 2018-08-21 positive/learning.py

@@ -743,6 +743,7 @@ def gmvrfit( domain,
         # estimator = foo.frmse
         estimator = foo.frmse
         return estimator,foo
+
     def mvplotfun( foo ): foo.plot(show=show)
 
     # Create a lexicon of symbols to consider for model learning
@@ -1706,8 +1707,8 @@ class mvpolyfit:
 
         # Decorate plot
         title(r'$frmse = %1.4e$, $\langle res \rangle =%1.4e$'%(this.frmse,mean(res)))
-        # xlabel('Fractional Residaul Error')
-        xlabel('Residaul Error')
+        # xlabel('Fractional Residual Error')
+        xlabel('Residual Error')
         ylabel('Count in Bin')
         # legend( frameon=False )
 

### 2018-08-21 positive/strings.py

@@ -204,8 +204,8 @@ def complex2str( x, precision=None, latex=False ):
             # Write phase as positive number
             phase = phase+2*pi if phase<0 else phase
             # Create string
-            fmt = '%s.%if'%(r'%',precision)
-            # fmt = '%s1.%if'%(r'%',precision)
+            # fmt = '%s.%ig'%(r'%',precision)
+            fmt = '%s1.%if'%(r'%',precision)
             ans_ = '%s*%s%s%s' % (fmt, 'e^{' if latex else 'exp(' ,fmt, 'i}' if latex else 'j)') % (amp,phase)
             if latex: ans_ = ans_.replace('*',r'\,')
 

### 2018-08-22 docs/mvfits_paper/mvf.tex
misc updates

@@
   %
-	The ongoing direct detection of gravitational wave signals is aided by representative models of theoretical predictions.
-In particular, the process of model based detection, and subsequent comparison of signals the general relativity's predictions are aided by the modeling of information related to perturbed Kerr black holes.
+  Models of black hole properties are an important component to the ongoing direct detection of gravitational waves from black hole binaries.
+  %
+  In particular, model based detection, and subsequent parameter estimation are directly enabled by the modeling of information related to perturbed Kerr black holes.
+  %
   Here, we summarize recent methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
-Towards the construction of these models, two algorithms, GMVP and GMVR, for the automated polynomial and rational modeling of general dimensional complex scalars are presented.
-GMVR is a quasi-linear numerical method for interpolating rational functions.
-It therefore represents a solution to the problem of Runge's phenomenon.
+  %
+  Towards the construction of these models, two algorithms are presented.
+  %
+  A greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method are presented for the automated modeling of polynomial and rational functions.
+  %
+  GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to the problem of Runge's phenomenon.
 	%
@@
 
-% \begin{itemize}
-% 	\item BH detections happen, and use fits at various levels
-% 	\item Fits for Kerr are important for modeling and testing GR, they are fast to eval comapred to formal calculations which has data analysis implications
-% 	\item Many fits have been done for perturbative Kerr parameters: QNM frequencies most prominently.
-% 	\item The problem/motivation:
-% 		\begin{itemize}
-% 			\item 1. There are many fits, and we would like to provide a reference for many of them, including key methods
-% 			\item 2. Methods for fits: basis learning
-% 			\item 3. (results) Summarize "simple fits": QNM frequencies and decay times, enforcing zero damping
-% 			\item 4. (results) Summarize more general fits: mixing coefficients
-% 		\end{itemize}
-% 	\item (discussion) We have presented ...
-% \end{itemize}
-
 \section{Introduction}
 %
-In the coming years, expectations for frequent \gw{} detections of increasing \snr{} are high.
+In the coming years, expectations for frequent \gw{} detections of increasing \snr{} are high \cite{TheLIGOScientific:2016pea,Abbott:2016nhf}.
 %
-Concurrent with \virgo{}, the \aligo{} detectors will enter their third observing run in \check{late 2018}.
+Concurrent with \virgo{}, the \aligo{} detectors will enter their third observing run in approximately late 2018.
 %
-At this time, \bbh{} detections are expected at a rate of \check{X} per month.
+During this period, a few to dozens of \bbh{} signals are likely to be detected. \cite{Abbott:2016nhf}.
 %
-In this context, signal detection and subsequent inference of physical parameters hinges upon efficient models for source properties and dynamics.
+In this context, signal detection and subsequent inference of physical parameters hinges upon efficient models for source properties and dynamics \cite{Abbott:2016wiq}.
 %
-Most prominently, there is ongoing interest in signal models for \bbh{} \imr{}.
+Most prominently, there is ongoing interest in signal models for \bbh{} \imr{} \cite{Blackman:2017dfb, London:2017bcn, Hannam:2013oca}.
 %
-As the merger of isolated \bh{s} is expected to result in a perturbed Kerr \bh{}, there is related interest in having computationally efficient models for perturbative parameters, namely those that enable evaluation of the related \rd{} radiation.
+As the merger of isolated \bh{s} is expected to result in a perturbed Kerr \bh{}, there is related interest in having computationally efficient models for perturbative parameters, namely those that enable evaluation of the related \rd{} radiation \cite{Berti:2005ys}.
 %
@@
 %
-These discrete frequencies have associated radial and spatial functions which are \textit{spheroidal} harmonic in nature.
+These discrete frequencies have associated radial and spatial functions which are \textit{spheroidal} harmonic in nature \cite{Leaver85,London:2014cma}.
 %
@@
 %
-\par In the first and second lines of \eqn{hrd}, we relate the observable \gw{} polarizations, $h_+$ and $h_\times$, with the analytically understood morphology of the time domain waveform.
+\par In the first and second lines of \eqn{hrd}, we relate the observable \gw{} polarizations, $h_+$ and $h_\times$, to the analytically understood morphology of the time domain waveform.
 %
@@
 In \sec{discuss}, we review the performance of \gmvp{} and \gmvr{}, and we discuss potential applications for these methods.
-
+%
 %
@@
 %
-\par \fig{fig:qnms} displays select training points, as well as model fits for $\cw\lmn$'s real and imaginary parts.
+\par \fig{fig:qnm} displays select training points, as well as model fits for $\cw\lmn$'s real and imaginary parts.
 %
@@
 %
-\par In each panel of \fig{fig:qnms}, the horizontal upper and lower demonstrate the effect of mapping $\jf$ onto $\kappa$.
+\par \fig{fig:qnm}'s top left and right panels demonstrate the effect of mapping $\jf$ onto $\kappa$.
 %
@@
 %
-\par Lastly, \fig{fig:qnm_err} shows residual errors.
+\par Lastly, \fig{fig:qnm}'s bottom two panels show residual errors.
 %
@@
 %
-\par Together, \eqns{eq:cw_fit_1}{eq:cw_fit_9} along with Figures (\ref{fig:qnms})-(\ref{fig:qnm_err}) present precise and accurate fits for the real and imaginary parts of \qnm{} frequencies for gravitational perturbations of Kerr \qnm{s}.
+\par Together, \eqns{eq:cw_fit_1}{eq:cw_fit_9} along with Figures (\ref{fig:qnm})-(\ref{fig:qnm_err}) present precise and accurate fits for the real and imaginary parts of \qnm{} frequencies for gravitational perturbations of Kerr \qnm{s}.
+%
 %
 \subsection{Modeling spherical-spheroidal inner-products using \gmvr{}}
+%
 %
@@
 %
-\fig{fig:ys} display comparisons of the fits with training data as well as related residuals.
+%
+\par \fig{fig:ys} displays fits, training data and related residuals.
 %
@@
 %
-As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent.
-
+As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values.
 %
@@
 \label{discuss}
-
+%
+\par We have developed upon previous techniques for the linear and pseudo-linear modeling of low noise data.
+%
+In particular, the \gmvp{} algorithm performs multivariate polynomial modeling of real and complex valued scalar functions.
+%
+The \gmvr{} algorithm does the same with multivariate rational functions.
+%
+%
+\par Treating a toy problem with \gmvr{} demonstrates \gmvr{}'s ability to faithfully recover underlying model parameters for a plausible dataset.
+%
+This treatment also demonstrates the convergence of the algorithm's greedy phase with increasing iterations, as well as the convergence of an underlying iterative refinement phase (\ceqn{eq:rat4}).
+%
+%
+\par Both \gmvp{} and \gmvr{} may be used to automatically determine the functional form and model for a given dataset that is expected to be respectively multinomial or rational.
+%
+An alternative use strategy is to use either \gmvp{} or \gmvr{} to determine a fitting ansatz for individual cases (e.g.
+individual \qnm{s}), and then use these results to develop a single ansatz for all cases.
+%
+This is what as been done for the modeling of \qnm{} frequencies and spherical-spheroidal mixing coefficients.
+%
+%
+\par \gmvp{} has been applied to the modeling \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit.
+%
+These models are found to have residual errors well below $1\%$ when $| \jf | \leq \CwFitCalibrationRegion$.
 %

### 2018-08-23 docs/mvfits_paper/mvf.tex
misc updates

@@
   %
-  Models of black hole properties are an important component to the ongoing direct detection of gravitational waves from black hole binaries.
-  %
-  In particular, model based detection, and subsequent parameter estimation are directly enabled by the modeling of information related to perturbed Kerr black holes.
+  Models of black hole properties play an important role in the ongoing direct detection of gravitational waves from black hole binaries.
+  %
+  In particular, model based gravitational wave detection, and subsequent estimation of source parameters are supported by the low level modeling of information related to perturbed Kerr black holes.
   %
@@
   %
-  A greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method are presented for the automated modeling of polynomial and rational functions.
+  A greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method are presented for the automated modeling of polynomial and rational functions respectively.
   %
@@
 %
-They are the eigen-solutions of the source free linearized \ee{} (i.e. \tk{'s} equations) for a perturbed \bh{} with final mass, $\mf$, and dimensionless final spin, $\jf$.
+They are the eigen-solutions of the source free linearized \ee{} (i.e. \tk{'s} equations \cite{PhysRevLett.29.1114}) for a perturbed \bh{} with final mass, $\mf$, and dimensionless final spin, $\jf$.
 %
@@
 %
-\par In the first and second lines of \eqn{hrd}, we relate the observable \gw{} polarizations, $h_+$ and $h_\times$, to the analytically understood morphology of the time domain waveform.
-%
-Here, the labels $\ell$ and $m$ are eigenvalues of \tk{'s} angular equations, where units of $M=1$ (e.g. the initial mass of the \bbh{} system), and $c=1$.
+\par In the first and second lines of \eqn{hrd}, we relate the observable \gw{} polarizations, $h_+$ and $h_\times$, to the analytically understood morphology of the time domain \rd{} waveform.
+%
+Here, the labels $\ell$ and $m$ are polar and azimuthal eigenvalues of \tk{'s} angular equations, where units of $M_i=1$ (e.g. the initial mass of the \bbh{} system), and $c=1$.
 %
@@
 %
-The consequences of this choice are discussed in reference \check{[X]}.
-%
-For the so-called \textit{Phenom} models, the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain.
+The consequences of this choice, in particular mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,London:2018gaq}.
+%
+For the so-called \textit{Phenom} models, the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain \cite{Hannam:2013oca,London:2017bcn,Khan:2015jqa,Schmidt:2014iyl}.
 %
 \par Both Phenom and \eob{} approaches directly use phenomenological models (i.e.
-fits) for the \qnm{} frequencies, as these fits are more computationally efficient than the underlying analytic calculations, which involve the solving of continued fraction equations.
-%
-In the case of \texttt{PhenomHM} and derivative models, fits for the \qnm{} frequencies are used in the process of mapping $\tilde{h}_{22}(f)$ into other $\tilde{h}\LM(f)$ \check{[X]}.
-%
-In that setting, it is demonstrated that \qnm{} frequencies correlate with the morphology of each $h\LM$ in not only \rd{}, but also merger and late inspiral, as is implied by the causal connectedness of pre and post merger.
-%
-%
-\par For models that assist tests of the \nht{}, and thereby only include precise \rd{s}, the perspective of \eqn{hrd}'s second and third lines are used to write each spherical harmonic multipole moment as
+fits) for the \qnm{} frequencies, as these fits are more computationally efficient than the underlying analytic calculations, which involve the solving of continued fraction equations \cite{Leaver85}.
+%
+In the case of \texttt{PhenomHM} and derivative models, fits for the \qnm{} frequencies are used in the process of mapping $\tilde{h}_{22}(f)$ into other $\tilde{h}\LM(f)$ \cite{London:2017bcn}.
+%
+In that setting, it is demonstrated that \qnm{} frequencies correlate with the morphology of each $h\LM$ in not only \rd{}, but also merger and late inspiral, as is implied by the source's causal connectedness pre and post merger.
+%
+%
+\par For models that assist tests of the \nht{} (e.g.
+\cite{Berti:2005ys,London:2018gaq,Carullo:2018sfu}), and thereby only include precise \rd{s}, the perspective of \eqn{hrd}'s second and third lines are used to write each spherical harmonic multipole moment as
 %
@@
 %
-\par In practice, \eqn{hlm} is computationally efficient:
-%
-The calculation of each ${_{-2}S}\lmn$ involves a series solution which slowly converges for $\jf$ near unity.
-Therefore, it is more effective to have accurate models for $\sigma\LMlmn$, which can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.
-%
-%
-\par In this combined context, it is clear that the modeling of \qnm{} frequencies, $\cw\lmn$, and spherical-spheroidal mixing coefficients, $\sigma\LMlmn$, underpin a wide range of \gw{} signal models.
-%
-While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in many publications, there exist minor shortcomings which we wish to address here.
-%
-\par For the \qnm{} frequencies, it is well known that for nearly extremal \bh{s} (i.e. $\jf \rightarrow 1$) some of the frequencies have zero-damping (i.e. $\tau\lmn \rightarrow \infty$).
-%
-In the context of \aligo{} \da{}, where source parameters are estimated using routines which sample over the space of possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit.
+\par In practice, using \eqn{hlm} is computationally efficient:
+%
+Whereas the calculation of each ${_{-2}S}\lmn$ involves a series solution which slowly converges for $\jf$ near unity, the calculation of each ${_{-2}Y}\LM$ is achieved using closed form expressions.
+%
+It is therefore efficient to avoid convergence issues by using accurate models for $\sigma\LMlmn$, which can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.
+%
+%
+\par In this combined context, it is clear that the modeling of \qnm{} frequencies, $\cw\lmn$, and spherical-spheroidal mixing coefficients, $\sigma\LMlmn$, are relevant for a range of \gw{} signal models.
+%
+While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in the literature, there exist minor shortcomings which we wish to address here \cite{Berti:2005ys,Berti:2014fga}.
+%
+\par For the \qnm{} frequencies, it is well known that for nearly extremal \bh{s} (i.e.
+$\jf \rightarrow 1$) some of the frequencies have zero-damping (i.e.
+$\tau\lmn \rightarrow \infty$) \cite{Zimmerman:2015trm}.
+%
+In the context of \aligo{} \da{}, where source parameters are estimated using routines which sample over the space of possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit \cite{TheLIGOScientific:2016wfe}.
 %
@@
 %
-\par For the modeling of $\sigma\LMlmn$, we note that the results presented in \red{[X]} are limited to cases where the azimuthal indices, $\ell$ and $\bar{\ell}$, are less than or equal to 3.
-%
-As the most advanced signal models include at least $\ell$ or $\bar{\ell}$ of 3, there is use in extending prior results.
-%
-In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole.
+\par For the modeling of $\sigma\LMlmn$, we note that the results presented in \cite{Berti:2014fga} are limited to cases where the azimuthal indices, $\ell$ and $\bar{\ell}$, are less than or equal to 3.
+%
+As the most advanced signal models include at least $\ell$ or $\bar{\ell}$ of 3, there is use in extending current results.
+%
+In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (See \ceqn{hlm}).
 %
@@
 %
-The description of \gmvp{} given here is complementary to similar algorithms used to model \qnm{} excitation amplitudes, $A\lmn$, as present in reference \red{[cite]}.
-%
-As we will discuss, the \gmvr{} algorithm is an iterative approach to the (pseudo) non-linear modeling of multivariate rational functions.
-%
-Both \gmvp{} and \gmvr{} are intended for use with low noise data (e.g. the results of analytic calculations), and each employs a reverse (or negative) greedy algorithm to counter over modeling.
+The description of \gmvp{} given here is complementary to similar algorithms used to model \qnm{} excitation amplitudes, $A\lmn$, as present in reference \cite{London:2018gaq,London:2014cma}.
+%
+As we will discuss, the \gmvr{} algorithm is an iterative approach to the (pseudo) linear modeling of multivariate rational functions, wherein iterations of linear inversions are used to refine the ultimately non-linear model.
+%
+\par In the rudimentary form presented here, both \gmvp{} and \gmvr{} are intended for use with low noise data (e.g.
+the results of analytic calculations), and each employs a reverse (or negative) greedy algorithm to counter over modeling \cite{Field:2011mf,Caudill:2011kv}.
 %
@@
 %
-In \sec{discuss}, we review the performance of \gmvp{} and \gmvr{}, and we discuss potential applications for these methods.
+In \sec{discuss}, we review the performance of \gmvp{} and \gmvr{}, and we discuss current and potential applications for these methods.
 %
@@
 %
-Within the topic of regression, linear regression has particular advantages:
-%
-its matrix based formulation can be computationally efficient, and it does not require initial guesses for model parameters.
-%
-Perhaps most intriguingly, the formal series expansions of smooth functions support linear and rational models (e.g. Pade approximants) having application to many datasets.
-%
-Here we will develop algorithms for the linear modeling of scalar functions (real or complex valued) of many variables.
+Within the topic of regression, linear regression has particular advantages.
+%
+Its matrix based formulation can be computationally efficient, and it does not require initial guesses for model parameters.
+%
+Perhaps most intriguingly, the formal series expansions of smooth functions support linear and rational models (e.g. Pad\'e approximants) having application to many datasets.
+%
+Here we will develop algorithms for the linear (polynomial and rational) modeling of scalar functions (real or complex valued) of many variables.
 %
@@
 %
-With $\phi_{k}(\vec{x}_j)$ assumed to be known, the linear representation (\ceqn{lin1}) lastly defined by the set of $\mu_k$.
+With $\phi_{k}(\vec{x}_j)$ assumed to be known, the linear representation (namely \ceqn{lin1}) is lastly defined the set of $\mu_k$.
 %
@@
 %
-In particular, defining $\hat{U} = \{\phi_{kj}\}$, and $\vec{f} = \{f_j\}$, then $\vec{f} = \hat{U} \; \vec{\mu}$.
-%
-This implies that
+In particular, defining $\hat{U} = \{\phi_{kj}\}$, and $\vec{f} = \{f_j\}$, then $\vec{f} = \hat{U} \; \vec{\mu}$, implies that
 %
@@
 %
-Equations (\ref{lin1}), and related discussion through \eqn{pinv1} illustrate the most rudimentary solution to the linear modeling problem.
+\par Equations (\ref{lin1}), and related discussion through \eqn{pinv1} illustrate the most rudimentary solution to the linear modeling problem.
 %
@@
 %
-Second, we will build upon the \gmvp{} approach by considering models of rational functions: polynomials divided by polynomials.
+Second, we will build upon the \gmvp{} approach by considering models of rational functions (polynomials divided by polynomials).
 %
 To consider these two approaches in a largely automated way (i.e.
-where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach.
+where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.
 %
@@
 %
-\par A well known method for finding an approximate solution to this problem is the so-called ``greedy'' algorithm.
-%
-The premise is this:
+\par A well known method for finding an approximate solution to this problem is the so-called ``greedy'' algorithm:
 %
@@
 %
-The process begins by finding the single symbol (basis vector) that yields the most accurate model (in the sense of minimizing least-squares error).
+The process begins by finding the single symbol (basis vector) that yields the most accurate model (e.g. in the sense of minimizing the least-squares error).
 %
@@
 %
-In each following iteration, an all remaining symbols are added to the model one at a time, and the single additional symbol which yields the greatest increase in model accuracy is kept for the following iteration.
+In each new iteration, an all remaining symbols are added to the model one at a time, resulting in many trial models.
+%
+When considering all trial models, the single models symbol which yields the greatest increase in model accuracy is kept for the subsequent greedy iteration.
 %
@@
 %
+\par The very similar ``negative'' greedy algorithm removes model symbols until representation error increases beyond a specified threshold.
 %
@@
 %
-This latter point is key to the perspective of \gmvp{}: given training data thought to be related to a smooth multivariate function, it may be well approximated by a truncated series expansion in an appropriate coordinate basis.
+\par This latter point is key to the perspective of \gmvp{}:
+%
+given training data thought to be related to a smooth multivariate function, it may in many cases be well approximated by a truncated series expansion in an appropriate coordinate basis.
 %
@@
 %
-In this setting, the uncertainty of which and how many basis terms to include makes this a problem ripe for the application of \eqn{eq:linsol1} and Alg. (\ref{alg:pgreedy}) .
-%
-\par In the current setting, the basis symbols required by Alg. (\ref{alg:pgreedy}) are the multinomial terms in \eqn{eq:mvt}.
+In this setting, the uncertainty of which and how many basis terms to include makes this a problem ripe for the application of linear modeling driven by a greedy process, namely \eqn{eq:linsol1} and Alg.
+(\ref{alg:pgreedy}) .
+%
+\par In this setting, the basis symbols required by Alg. (\ref{alg:pgreedy}) are the multinomial terms in \eqn{eq:mvt}.
 %
@@
 %
-To counter this, we may incrementally increase, or \textit{temper}, the maximum allowed multinomial order.
-%
-Recall that a term such as $x_0x_1x_3^2$ has an effective degree of 4.
-%
-The combination of degree tempering with the greedy approach results in the \gmvp{} algorithm as presented in Alg. (\ref{alg:gmvp}).
+To counter this, we may incrementally increase, or \textit{temper}, the maximum allowed multinomial degree.
+%
+For example, when iterating through allowed degrees, if the current maximum degree is 3, then degree 4 terms, such as $x_0x_1x_3^2$, will not be considered within the space of model symbols.
+%
+The degree tempering process halts when increasing the maximum allowed degree has no significant effect on model representation error.
+%
+\par The combination of degree tempering with the greedy approach results in the \gmvp{} algorithm as presented in Alg. (\ref{alg:gmvp}).
+%
 %
@@
 %
-\par Despite the apparent universality of of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a multinomial (historically, this is equivalent to ``Runge's phenomenon'').
-%
-Of the simplest examples are the rational functions of the form
+\par Despite the apparent universality of of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a multinomial.
+%
+Worst, in cases where the underlying dataset is best described by a rational function, no polynomial order will yield satisfactory results (i.e. the well known ``Runge's phenomenon'').
+%
+\par Of the simplest examples are rational functions of the form
 %
@@
 %
-where $\muf$ is the additive mean of $f(\vec{x})$, and $\sif$ is the standard deviation of $f(\vec{x})$ from its mean, and $\phi_k$ are the multinomials basis functions considered in the previous section.
+where $\muf$ is the additive mean of $f(\vec{x})$, and $\sif$ is the standard deviation of $f(\vec{x})$, and $\phi_k$ are the multinomials basis functions considered in the previous section.
 %
@@
 %
-then the algebraic manipulation of \eqn{eq:rat1} results in
+then algebraic manipulation of \eqn{eq:rat1} allows
 %
@@
 %
-At this stage, we will also explicitly consider the $j^\mathrm{th}$ samples of the domain, and so refer to $\vec{x}$ as $\vec{x}_j$.
+At this stage, we will also explicitly consider the $j^\mathrm{th}$ samples of the domain, and so refer to (e.g.) $\vec{x}$ as $\vec{x}_j$.
 %
@@
 %
-\par The key to robustly solving for $\vec{\alpha}$ lies in the iterative refinement.
+%
+\par The key to robustly solving for $\vec{\alpha}$ lies in iterative refinement \cite{Press:1992:NRC:148286}.
 %
@@
 %
-To this end, if we define $g^{(0)}=g$ (i.e. the training data) then, with $\hat{P} = \hat{P}( \vec{g}^{\,(n)} )$, \eqn{eq:pinv2} generalizes to
+To this end, if we define $g^{(0)}=g$ (i.e. $g$ is the training data) then, with $\hat{P} = \hat{P}( \vec{g}^{\,(n)} )$, then \eqn{eq:pinv2} generalizes to
 %
@@
   \label{eq:rat4}
-  g^{(n+1)} =  \frac{ \sum_{r=0}^{R} a^{(n+1)}_r \, \phi_{r}(\vec{x}) }{ 1\;-\;  \sum_{v=1}^{V} b^{(n+1)}_v \, \phi_{v}(\vec{x}) } \; ,
-\end{align}
-%
-which is then fed back into \eqn{eq:pinv3} for further refinement.
+  g^{(n+1)} =  \frac{ \sum_{r=0}^{R} a^{(n+1)}_r \, \phi_{r}(\vec{x}) }{ 1\;-\;  \sum_{v=1}^{V} b^{(n+1)}_v \, \phi_{v}(\vec{x}) } \; .
+\end{align}
+%
+Subsequently, $g^{(n+1)}$ is then fed back into \eqn{eq:pinv3} for further refinement.
 %
@@
 %
-In principle, the existence of $a_r$ and $b_v$ makes the problem more complicated, as one could imagine optimizing over each symbol space independently.
+In principle, the existence of $a_r$ and $b_v$ makes the problem more complicated, as one might imagine optimizing over each symbol space independently.
 %
@@
 However, rather than independent greedy optimizations for the numerator and denominator bases symbols, \eqn{eq:rat3} suggests that the appropriate labeling of symbols (e.g.
-``numerator'' or ``denominator'') may yield an effective flattening of the supposed 2D basis selection problem.
-%
-Put another way, rather than two simultaneous greedy optimizations over $R$ and $V-1$ symbols (with $(V-1)R$ iterations), a single greedy process over $V+R$ symbols is performed.
+``numerator'' or ``denominator'') may yield an effective flattening of the supposed 2D symbol selection problem.
+%
+Put another way, rather than two simultaneous greedy optimizations over $R+1$ and $V$ symbols (with $(R+1)V$ iterations), a single greedy process over $V+R+1$ symbols is performed.
 %
@@
 %
-\par The combination of \eqns{eq:pinv3} and \eqn{eq:rat4}, along with \pgreedy{} and degree tempering, results in the \gmvr{} algorithm as presented in Alg. (\ref{alg:gmvr}).
-%
-\par While not treated here, it is noted that Ref. \cite{London:2018gaq} utilizes \gmvp{} with a parameter dimension of 4.
-%
-\par In the following section we apply both \gmvp{} and \gmvr{} to the modeling of noiseless (up to roundoff error) data: the \qnm{} frequencies of Kerr \bh{s}, and the inner-products of the spherical and spheroidal harmonics.
-%
-In each case, the underlying 1D parameter in each case will be the dimensionless \bh{} spin, $\jf{}$.
+\par The combination of \eqn{eq:pinv3} and \eqn{eq:rat4}, along with \pgreedy{} and degree tempering, results in the \gmvr{} algorithm as presented in Alg. (\ref{alg:gmvr}).
+%
+%
+Both \gmvp{} and \gmvr{} are publicly available on Github through the \texttt{positive} repository \cite{lionel_london_2018_1402516}.
 %
@@
 %
-Here, our goal is to very briefly overview the functionality of the \gmvr{} algorithm as implemented in Ref. \red{[positive]}.
+Here, our goal is to very briefly overview the functionality of the \gmvr{} algorithm as implemented in Ref. \cite{lionel_london_2018_1402516}.
 %
@@
 %
-Similarly, we note that \gmvr{} as implemented in Ref. \red{[positive]} involves a reverse (or negative) greedy step to counter over-modeling in cases where the aforementioned $tol$ is too low.
+Similarly, we note that \gmvr{} as implemented in Ref. \cite{lionel_london_2018_1402516} involves a negative greedy phase to counter over-modeling in cases where the aforementioned $tol$ is too low.
 %
@@
 %
-\par Let's start by applying \gmvr{} to a fiducial scalar function of the form
-%
-\begin{align}
-  %
-  % f(x_0,x_1) = 50 + \frac{1.1 +0.2 x_0+0.5 x_1+x_0 x_1}{ 0.9 + x_0^2 + x_1^2 }
+\par Let us now consider the application of \gmvr{} to a fiducial scalar function of the form
+%
+\begin{align}
   %
@@
 \fig{fig:gmvrtoy}'s central bottom panel displays the distribution of fractional residuals, and demonstrates their approximately flat distribution.
-A gaussian fit to the fractional residuals is displayed only for comparison.
-In particular, a biased fit will often have residuals that are approximately gaussian; we see that this is not the case here, and that the uniformly random noise distribution is approximately recovered.
-%
-When considering many noise realizations, we find that sample noise and residuals have an average correlation of $99.46\%$.
+%
+A gaussian fit to the fractional residuals is displayed for comparison.
+%
+In particular, despite the uniform nature of the underlying noise distribution, a biased fit will often have residuals that are approximately gaussian.
+%
+We see that this is not the case here, and that the uniformly random noise distribution is approximately recovered.
+%
+Specifically, when considering many noise realizations, we find that sample noise and residuals have an average correlation of $99.46\%$.
 %
@@
 %
-Here it is demonstrated that \gmvr{} in a way that is approximately exponential, owing to the underlying analytic nature of the training data.
+Here it is demonstrated that \gmvr{} converges in a way that is approximately exponential, owing to the underlying analytic nature of the training data.
 %
@@
 %
-\par In this example case, \gmvr{} correctly recovers the functional form of the input data.
-But, in general, \gmvr{} and related techniques, having no knowledge of , will attempt to model minor correlations and offsets within the training data's noise.
+\par In this rudimentary example case, \gmvr{} correctly recovers the functional form of the input data.
+But, in general, \gmvr{} and related techniques, having no knowledge of the underlying noise distribution, will attempt to model minor correlations and offsets within the training data's noise.
 %
@@
 %
-In the following sections, we consider cases where the functional form of the sample data is not known to be explicitly rational, but the amount of noise within the training data is negligible.
-
+\par In the following sections, we consider still ideal cases, where the functional form of the sample data is not known to be explicitly polynomial or rational, but the amount of noise within the training data is negligible.
 %
@@
 %
-Namely, we will impose a zero-damping constraint: some frequencies are real as $\jf \rightarrow 1$.
+Namely, we will impose a zero-damping constraint: some frequencies are real as $\jf \rightarrow 1$ \cite{Zimmerman:2015trm}.
 %
@@
 %
-appropriately linearizes the sharp behavior of each frequency near $\jf=1$, and maps $-1 \le \jf \le 1$ onto $0 \le \kappa \le 1$.
+appropriately linearizes the sharp behavior of each frequency near $\jf=1$ while also mapping $-1 \le \jf \le 1$ onto $0 \le \kappa \le 1$.
 %
@@
 %
-For the right and left panels, simple polynomial behavior of each curve is a result of the displayed linear domain in $\kappa(\jf,\ell,m)$.
-%
-In the left panel, we have scaled $1/\tau\lmn$ by factors for $m/(n+1/2)$ to place the \qnm{s} with $n=0$ and $n=1$ at approximately the same scale.
+For the top right and top left panels, the simple polynomial behavior of each curve is a result of the displayed linear domain in $\kappa(\jf,\ell,m)$.
+%
+In the top left panel, we have scaled $1/\tau\lmn$ by factors for $m/(n+1/2)$ to place the \qnm{s} with $n=0$ and $n=1$ at approximately the same scale.
 %
@@
 %
-\par \fig{fig:qnm}'s top left and right panels demonstrate the effect of mapping $\jf$ onto $\kappa$.
-%
-In particular, it is shown that the two solution branches ($\jf>0$ and $\jf<0$) naturally form a single family of solutions when accounting for the sign of the \bh{}'s oriented spin.
-%
-Concurrently, the use of $\kappa$ as a domain variable has the desirable effect of making each $\cw\lmn$ and $\tau\lmn$ approximately parabolic.
-%
-We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate.
-%
-In allowing \eqns{eq:cw_fit_1}{eq:cw_fit_9} to extrapolate to $\jf \sim 1$, we do not explicitly account for this additional effect.
-%
-\par Lastly, \fig{fig:qnm}'s bottom two panels show residual errors.
+\par \fig{fig:qnm}'s top left and right panels' upper axis demonstrate the effect of mapping $\jf$ onto $\kappa$.
+%
+In particular, it is shown that the two solution branches ($\jf>0$ and $\jf<0$) naturally form a single family of solutions when accounting for the sign of the \bh{}'s oriented spin \cite{Husa:2007hp}.
+%
+Concurrently, the use of $\kappa$ as a domain variable has the desirable effect of making each $\cw\lmn$ and $\tau\lmn$ approximately quarctic.
+%
+We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Zimmerman:2015rua}.
+%
+In allowing \eqns{eq:cw_fit_1}{eq:cw_fit_9} to extrapolate to $\jf=1$, we do not explicitly account for this additional effect.
+%
+\par Lastly, \fig{fig:qnm}'s bottom two panels show fractional residual errors.
 %
@@
 %
-\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for all $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.
+\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for \textit{all} $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.
 %

### 2018-08-24 docs/mvfits_paper/mvf.tex
misc updates

@@
 %
-The forward process is to end when the model accuracy (or changes thereof) pass a specified threshold.
-%
-This rough algorithmic picture encapsulated in Alg. \ref{alg:pgreedy}.
+The forward process is to end when the model accuracy, or changes thereof, pass a specified threshold.
+%
+This rough algorithmic picture is encapsulated by Alg. \ref{alg:pgreedy}.
 %
@@
 %
-\par In this setting, the basis symbols required by Alg. (\ref{alg:pgreedy}) are the multinomial terms in \eqn{eq:mvt}.
+\par Here, the basis symbols required by Alg. (\ref{alg:pgreedy}) are the multinomial terms in \eqn{eq:mvt}.
 %
@@
         \phi_k(\vec{x}_j),      & \text{for }0\leq k\leq R\\
-        \phi_k(\vec{x}_j)\, g , & \quad \;\; \;\text{for }R+1\leq k\leq R+V
+        \phi_k(\vec{x}_j)\, g_j , & \quad \;\; \;\text{for }R+1\leq k\leq R+V
         \end{array} \right\}
@@
 %
-where, here, $\hat{P}$ is the pseudo-inverse of the matrix whose elements are $\psi_k(\vec{x}_j)$.
+where, $\hat{P}$ is the pseudo-inverse of the matrix whose elements are $\psi_k(\vec{x}_j)$, $\vec\alpha = ( z_0, z_1, ... z_{R+V-1},z_{R+V} )$, and $\vec{g} = ( g_0, g_1, ... g_{R+V-1},g_{R+V} )$.
 %
@@
 %
-In this contemplation, it may be that shown that $n$ may be entirely regelated to $\hat{P}$.
-%
-It is in this sense that \eqn{eq:pinv2} is insufficient to generally solve for $\vec{\alpha}$.
+In this, it may be that shown that $n$ may be entirely regelated to $\hat{P}$.
+%
+It is in this sense that \eqn{eq:pinv2} is insufficient to generally solve for $\vec{\alpha}$, as $\hat{P}$ may be adversely affected by noise.
 %
@@
 %
-That is, to reduce the impact of noise on $\hat{P}$, we are free to calculate it using model evaluations of $g$ rather than the original training data.
-%
-To this end, if we define $g^{(0)}=g$ (i.e. $g$ is the training data) then, with $\hat{P} = \hat{P}( \vec{g}^{\,(n)} )$, then \eqn{eq:pinv2} generalizes to
+That is, to reduce the impact of noise on $\hat{P}$, we are free to calculate it using model evaluations of $g$ rather than the original (noisy) training data.
+%
+To this end, if we define $g^{(0)}=g$ (i.e. $g$ is the training data), with $\hat{P} = \hat{P}( \vec{g}^{\,(n)} )$, then \eqn{eq:pinv2} generalizes to
 %
@@
 %
-In practice, one solves \eqn{eq:pinv3} for $\vec{\alpha}^{(n)}$, and then uses the related $a_r^{(n)}$ and $b_v^{(n)}$ to calculate $g^{(n+1)}$ via
+In practice, one solves \eqn{eq:pinv3} for $\vec{\alpha}^{(n+1)}$, and then uses the related $a_r^{(n+1)}$ and $b_v^{(n+1)}$ to calculate $g^{(n+1)}$ via
 %
@@
 %
-To broach these complications, we again use a greedy algorithm with degree tempering.
+To broach this complications, we again use a greedy algorithm with degree tempering.
 %
@@
 %
-Put another way, rather than two simultaneous greedy optimizations over $R+1$ and $V$ symbols (with $(R+1)V$ iterations), a single greedy process over $V+R+1$ symbols is performed.
+Put another way, rather than two simultaneous greedy optimizations over $R+1$ and $V$ symbols (with $(R+1)V$ iterations), a single greedy process over $V+R+1$ symbols is performed, where each symbol is additionally labeled as being in the numerator or denominator.
 %
@@
 %
-Both \gmvp{} and \gmvr{} are publicly available on Github through the \texttt{positive} repository \cite{lionel_london_2018_1402516}.
+Both \gmvp{} and \gmvr{} are publicly available on Github through the \texttt{positive} repository (Ref.
+\cite{lionel_london_2018_1402516}), and may be imported in python via {\small{\texttt{positive.learning.gmvpfit}}} and {\small{\texttt{positive.learning.gmvrfit}}}.
 %
@@
 %
-Second, we apply \gmvr{} to the modeling of spin -2 spherical-spheroidal harmonic mixing coefficients.
+Second, we apply \gmvr{} to the modeling of spin -2 spherical-spheroidal harmonic mixing coefficients (\ceqn{sigma}).
 %
@@
 For relevance of presentation to physics examples in subsequent sections, we will restrict ourselves to a case where numerical noise is low, and the negative greedy step does not alter the output of Alg.
-\ref{alg:gmvr}).
+\ref{alg:gmvr}.
 %
@@
 \par To generate the test data, \eqn{eq:gmvrtoy1} is evaluated with 25 points in $x_0$ and $x_1$, where each is between -3 and 3.
+Though not a requirement of \gmvr{}, for simplicity of presentation, domain points are equally spaced.
 %
@@
 %
-\par In this rudimentary example case, \gmvr{} correctly recovers the functional form of the input data.
+\par In this rudimentary example case, \gmvr{} correctly recovers the functional form of the input data, and accurately recovers the correct values of model parameters.
+%
 But, in general, \gmvr{} and related techniques, having no knowledge of the underlying noise distribution, will attempt to model minor correlations and offsets within the training data's noise.
 %
-However, we have demonstrated the utility of \gmvr{} in a relatively ideal usage case where the underlying function is rational, and the training data is inly weakly contaminated with noise.
-%
-\par In the following sections, we consider still ideal cases, where the functional form of the sample data is not known to be explicitly polynomial or rational, but the amount of noise within the training data is negligible.
+However, we have demonstrated the utility of \gmvr{} in a relatively ideal usage case where the underlying function is rational, and the training data is only weakly contaminated with noise.
+%
+\par In the following sections, we consider realistic, but similarly ideal cases, where the functional form of the sample data is not known to be explicitly polynomial or rational, but the amount of noise within the training data is negligible.
 %
@@
 % %%%%%%
-\subsection{Modeling \qnm{} frequencies using \gmvp{}}
+\subsection{Modeling \qnm{} frequencies with \gmvp{}}
 % %%%%%%
@@
 %
-\par \fig{fig:qnm}'s top left and right panels' upper axis demonstrate the effect of mapping $\jf$ onto $\kappa$.
-%
-In particular, it is shown that the two solution branches ($\jf>0$ and $\jf<0$) naturally form a single family of solutions when accounting for the sign of the \bh{}'s oriented spin \cite{Husa:2007hp}.
-%
-Concurrently, the use of $\kappa$ as a domain variable has the desirable effect of making each $\cw\lmn$ and $\tau\lmn$ approximately quarctic.
+\par \fig{fig:qnm}'s top left and right panels' upper axes demonstrate the effect of mapping $\jf$ onto $\kappa$.
+%
+In particular, it is shown that the two branches (namely $\jf>0$ and $\jf<0$) naturally form a single family of solutions when accounting for the sign of the \bh{}'s oriented spin \cite{Husa:2007hp}.
+%
+Concurrently, the use of $\kappa$ as a domain variable has the desirable effect of making each $\cw\lmn$ and $\tau\lmn$ approximately polynomial.
 %
@@
 %
-\subsection{Modeling spherical-spheroidal inner-products using \gmvr{}}
+\subsection{Modeling spherical-spheroidal inner-products with \gmvr{}}
 %
@@
 %
-For efficiency of presentation, each $\sigma_{\LMlmn}$ is plotted against its real and imaginary part.
+For efficiency of presentation, each $\sigma_{\LMlmn}$ is plotted via its real and imaginary part.
 %
@@
 %
-In particular, the \gmvp{} algorithm performs multivariate polynomial modeling of real and complex valued scalar functions.
+In particular, the \gmvp{} algorithm performs multivariate polynomial modeling of real and complex valued scalar functions with no inherent limitation on the number of domain parameters.
 %
@@
 %
-%
-\par Treating a toy problem with \gmvr{} demonstrates \gmvr{}'s ability to faithfully recover underlying model parameters for a plausible dataset.
+When applied to the modeling of analytically computed quantities, both algorithms perform extremely well in producing accurate and precise representations of training data, suggesting extended applicability of \gmvr{} and \gmvp{} similar problems.
+%
+\par Treating a toy problem with \gmvr{} demonstrates its ability to faithfully recover underlying model parameters for a plausible dataset.
 %
@@
 %
-\par Both \gmvp{} and \gmvr{} may be used to automatically determine the functional form and model for a given dataset that is expected to be respectively multinomial or rational.
+\par Both \gmvp{} and \gmvr{} may be used to automatically determine the functional form and model for a given dataset that is expected to be respectively polynomial or rational.
 %
@@
 %
-These models are found to have residual errors well below $1\%$ when $| \jf | \leq \CwFitCalibrationRegion$.
+The fits presented are of direct use in Ref.
+\cite{London:2017bcn}, where efficiently evaluable \qnm{} frequencies are required to general template waveforms for \gw{} searches and parameter estimation.
+%
+The fits presented may find future use in Phenom or EOB based \gw{} models.
+%
+\par \gmvr{} has been applied to the modeling of mixing coefficients between the spherical and spheroidal harmonics.
+%
+These fits are of direct use in Ref. \cite{Carullo:2018sfu}, and may be of future use in similar ringdown-only models for the purpose of testing \gr{}.
+%
+\par While \gmvr{} and \gmvp{} show promise in the cases shown here, in their presented rudimentary form, both posses a number of limitations.
+%
+Neither method directly accounts for information
 %

### 2018-08-24 docs/mvfits_paper/mvf.tex
misc updates

@@
 %
-Neither method directly accounts for information
+Neither currently performs cross-validation, given sufficiently dense training data.
+%
+And perhaps most notably, neither method directly accounts for information about the noise distribution within the training data.
+%
+As such, the methods presented are recommended primarily for datasets where noise is very small or negligible.
+%
+Nevertheless, the \gmvr{} toy problem demonstrates \gmvr{}'s ability to handle moderately noisy training data, suggesting current applicability to a large number of problems where polynomial interpolation is insufficient.
 %

### 2018-08-24 docs/mvfits_paper/mvf.tex
misc updates

@@
 %
+% GMVP
+\hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{\gmvp{}, a degree tempered stepwise algorithm for multivariate polynomial modeling of scalar data.}
+  \label{alg:gmvp}
+  %
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
+    \vskip 10pt
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol
+    \State Define $\mathcal{A}_{\gmvp{}}$ according to Alg. (\ref{alg:A_gmvp}).
+    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
+    \For {$d$ \textbf{in}  ${ D}$ }
+      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
+      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
+      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
+        \State \textbf{break}
+      \EndIf
+    \EndFor
+    \vskip 10pt
+    \State {\bf Output:} $\mlam^{(d)}_{opt}$
+    %
+  \end{algorithmic}
+  %
+\end{algorithm}
+}
+%
+%
 \par This truncated expansion happens to be a polynomial in at most $N$ variables.
@@
 (\ref{alg:pgreedy}) .
+%
+%
+% Plots of QNM frequencies
+\begin{figure*}[htb]
+  %
+  \begin{tabular}{lr}
+    \includegraphics[width=0.49\textwidth]{fig/fits_w.pdf} & \includegraphics[width=0.49\textwidth]{fig/fits_tau.pdf}
+    \\
+    \includegraphics[width=0.49\textwidth]{fig/res_w.pdf} & \includegraphics[width=0.49\textwidth]{fig/res_tau.pdf}
+  \end{tabular}
+  %
+	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+  %
+  Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$.
+Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
+  %
+  The grey dashed line marks the value of $\kappa$ where $\j{}=0$.
+Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+(Bottom) Percentage residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+}
+  %
+  \label{fig:qnm}
+  %
+\end{figure*}
 %
@@
 %
-\par The combination of these two ideas alone results in an algorithm prone to a deficit of stepwise methods: the algorithm may confuse correlated basis vectors (e.g. $x^2$ may be confused for $x^4$).
+\par The combination of these two ideas alone results in an algorithm prone to a deficit of stepwise methods: the algorithm may confuse correlated basis vectors (e.g.
+$x^2$ may be confused with $x^4$).
 %
@@
   %
-	\caption{ Standard summary plot for \gmvr. }
+	\caption{ Standard summary plot for Greedy Multivariate Rational fitting algorithm (\gmvr) as implemented in \cite{lionel_london_2018_1402516}.
+(\textit{left}) 3D plot of training data (black dots) and final fit (red mesh).
+(\textit{center top}) Same as left most panel, but in index space.
+(\textit{center bottom}) Fractional residual error (grey blocks) along with uniform (black) and gaussian (red) fits to error.
+(\textit{top right}) convergence of the L2 norm during iterative refinement.
+(\textit{bottom right}) Same as top right, but on log scale, where $\epsilon_0$ is the value of $\epsilon$ at the final $k^{\mathrm{th}}$ iteration of refinement.
+}
   %
@@
 The refinement process is to terminate when a measure of model error (e.g. $||g^{(0)}-g^{(n)}||$) passes a predetermined threshold.
+%
+%
+%
+% \hspace{1cm}
+{\scriptsize
+\begin{algorithm}[H]
+  %
+  \caption{$\mathcal{A}_{\gmvp}$, the action for \gmvp. Model calculation given basis symbols, and output of model error estimate.}
+  %
+  \label{alg:A_gmvp}
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $\mlam_{trial}$
+    \vskip 10pt
+    \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
+    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the L-2 norm of $a$.
+    \vskip 10pt
+    \State {\bf Output:} $\epsilon$
+  \end{algorithmic}
+\end{algorithm}
+}
 %
@@
 %
-In allowing \eqns{eq:cw_fit_1}{eq:cw_fit_9} to extrapolate to $\jf=1$, we do not explicitly account for this additional effect.
-%
-\par Lastly, \fig{fig:qnm}'s bottom two panels show fractional residual errors.
-%
-Although each model's fractional error is within 2\%, each is error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current 2nd generation \gw{} efforts.
-%
-\par Together, \eqns{eq:cw_fit_1}{eq:cw_fit_9} along with Figures (\ref{fig:qnm})-(\ref{fig:qnm_err}) present precise and accurate fits for the real and imaginary parts of \qnm{} frequencies for gravitational perturbations of Kerr \qnm{s}.
-%
-%
-\subsection{Modeling spherical-spheroidal inner-products with \gmvr{}}
-%
-%
-Here we apply \gmvr{} to the spherical-spheroidal mixing coefficients, $\sigma_{\LMlmn}$.
-%
-As in the case of the \qnm{} frequencies, we use the domain transformation defined by \eqn{eq:kappa} to simplify the functional form of each $\sigma_{\LMlmn}$.
-%
-\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for \textit{all} $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.
-%
-\eqns{eq:ys22220}{eq:ys55550} present the resulting model equations.
-%
-%
-\par \fig{fig:ys} displays fits, training data and related residuals.
-%
-For efficiency of presentation, each $\sigma_{\LMlmn}$ is plotted via its real and imaginary part.
-%
-In cases where $(\bar\ell,\bar{m})=(\ell,m)$, the real part of $\sigma_{\LMlmn}$ varies about unity in a manner consistent with the Schwarzschild limit, where $\sigma_{\LMlmn}=\delta_{\bar\ell}^{\ell}\;\delta_{\bar{m}}^{m}$.
-%
-This is equally true in cases where $(\bar\ell,\bar{m}) \neq (\ell,m)$.
-%
-As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values.
-%
-\section{Discussion}
-\label{discuss}
-%
-\par We have developed upon previous techniques for the linear and pseudo-linear modeling of low noise data.
-%
-In particular, the \gmvp{} algorithm performs multivariate polynomial modeling of real and complex valued scalar functions with no inherent limitation on the number of domain parameters.
-%
-The \gmvr{} algorithm does the same with multivariate rational functions.
-%
-When applied to the modeling of analytically computed quantities, both algorithms perform extremely well in producing accurate and precise representations of training data, suggesting extended applicability of \gmvr{} and \gmvp{} similar problems.
-%
-\par Treating a toy problem with \gmvr{} demonstrates its ability to faithfully recover underlying model parameters for a plausible dataset.
-%
-This treatment also demonstrates the convergence of the algorithm's greedy phase with increasing iterations, as well as the convergence of an underlying iterative refinement phase (\ceqn{eq:rat4}).
-%
-%
-\par Both \gmvp{} and \gmvr{} may be used to automatically determine the functional form and model for a given dataset that is expected to be respectively polynomial or rational.
-%
-An alternative use strategy is to use either \gmvp{} or \gmvr{} to determine a fitting ansatz for individual cases (e.g.
-individual \qnm{s}), and then use these results to develop a single ansatz for all cases.
-%
-This is what as been done for the modeling of \qnm{} frequencies and spherical-spheroidal mixing coefficients.
-%
-%
-\par \gmvp{} has been applied to the modeling \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit.
-%
-The fits presented are of direct use in Ref.
-\cite{London:2017bcn}, where efficiently evaluable \qnm{} frequencies are required to general template waveforms for \gw{} searches and parameter estimation.
-%
-The fits presented may find future use in Phenom or EOB based \gw{} models.
-%
-\par \gmvr{} has been applied to the modeling of mixing coefficients between the spherical and spheroidal harmonics.
-%
-These fits are of direct use in Ref. \cite{Carullo:2018sfu}, and may be of future use in similar ringdown-only models for the purpose of testing \gr{}.
-%
-\par While \gmvr{} and \gmvp{} show promise in the cases shown here, in their presented rudimentary form, both posses a number of limitations.
-%
-Neither currently performs cross-validation, given sufficiently dense training data.
-%
-And perhaps most notably, neither method directly accounts for information about the noise distribution within the training data.
-%
-As such, the methods presented are recommended primarily for datasets where noise is very small or negligible.
-%
-Nevertheless, the \gmvr{} toy problem demonstrates \gmvr{}'s ability to handle moderately noisy training data, suggesting current applicability to a large number of problems where polynomial interpolation is insufficient.
-%
-\appendix
-
-\section{Algorithms}
-\label{app:algos}
-
-% \begin{widetext}
-
-%
-% GMVR
-% \hspace{1cm}
-{\scriptsize
-\begin{algorithm}[H]
-  %
-  \caption{\gmvr{}, a degree tempered stepwise algorithm for multivariate rational modeling of scalar data.}
-  \label{alg:gmvr}
-  %
-  \begin{algorithmic}[1]
-    %
-    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
-    \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol.
-This is the combined bulk for numerator and denominator symbols.
-    \State Define $\mathcal{A}_{\gmvr{}}$ according to Alg. (\ref{alg:A_gmvr}).
-    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
-    \For {$d$ \textbf{in}  ${ D}$ }
-      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
-      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
-      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
-        \State \textbf{break}
-      \EndIf
-    \EndFor
-    \vskip 10pt
-    \State {\bf Output:} $\mlam^{(d)}_{opt}$
-    %
-  \end{algorithmic}
-  %
-\end{algorithm}
-}
-%
-% GMVP
-% \hspace{1cm}
-{\scriptsize
-\begin{algorithm}[H]
-  %
-  \caption{\gmvp{}, a degree tempered stepwise algorithm for multivariate polynomial modeling of scalar data.}
-  \label{alg:gmvp}
-  %
-  \begin{algorithmic}[1]
-    %
-    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
-    \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol
-    \State Define $\mathcal{A}_{\gmvp{}}$ according to Alg. (\ref{alg:A_gmvp}).
-    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
-    \For {$d$ \textbf{in}  ${ D}$ }
-      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
-      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
-      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
-        \State \textbf{break}
-      \EndIf
-    \EndFor
-    \vskip 10pt
-    \State {\bf Output:} $\mlam^{(d)}_{opt}$
-    %
-  \end{algorithmic}
-  %
-\end{algorithm}
-}
-%
-%
-% \hspace{1cm}
 {\scriptsize
@@
 }
-%
-%
-% \hspace{1cm}
-{\scriptsize
-\begin{algorithm}[H]
-  %
-  \caption{$\mathcal{A}_{\gmvp}$, the action for \gmvp. Model calculation given basis symbols, and output of model error estimate.}
-  %
-  \label{alg:A_gmvp}
-  \begin{algorithmic}[1]
-    %
-    \State {\bf Input:} $\mlam_{trial}$
-    \vskip 10pt
-    \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
-    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the L-2 norm of $a$.
-    \vskip 10pt
-    \State {\bf Output:} $\epsilon$
-  \end{algorithmic}
-\end{algorithm}
-}
-
 % \end{widetext}
-
-\section{Equations}
-\label{app:eqns}
-
-%
-% Equations for mixing coefficients
-%
-\begin{widetext}
-  \input{src/ysprod_eqns}
-\end{widetext}
-
-\section{Figures}
-\label{app:figs}
-
-%
-% Plots of QNM frequencies
-\begin{figure*}
-  %
-  \begin{tabular}{lr}
-    \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
-    \\
-    \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
-  \end{tabular}
-  %
-	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-  %
-  Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$.
-Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
-  %
-  The grey dashed line marks the value of $\kappa$ where $\j{}=0$.
-Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-(Bottom) Percentage residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-}
-  %
-  \label{fig:qnm}
-  %
-\end{figure*}
-
+%
+In allowing \eqns{eq:cw_fit_1}{eq:cw_fit_9} to extrapolate to $\jf=1$, we do not explicitly account for this additional effect.
+%
+\par Lastly, \fig{fig:qnm}'s bottom two panels show fractional residual errors.
+%
+Although each model's fractional error is within 2\%, each is error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current 2nd generation \gw{} efforts.
+%
+\par Together, \eqns{eq:cw_fit_1}{eq:cw_fit_9} along with \fig{fig:qnm} present precise and accurate fits for the real and imaginary parts of \qnm{} frequencies for gravitational perturbations of Kerr \qnm{s}.
+%
+%
+\subsection{Modeling spherical-spheroidal inner-products with \gmvr{}}
+%
+%
+Here we apply \gmvr{} to the spherical-spheroidal mixing coefficients, $\sigma_{\LMlmn}$.
+%
+As in the case of the \qnm{} frequencies, we use the domain transformation defined by \eqn{eq:kappa} to simplify the functional form of each $\sigma_{\LMlmn}$.
+%
+\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for \textit{all} $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.
+%
+\eqns{eq:ys22220}{eq:ys55550} present the resulting model equations.
+%
+%
+\par \fig{fig:ys} displays fits, training data and related residuals.
+%
+For efficiency of presentation, each $\sigma_{\LMlmn}$ is plotted via its real and imaginary part.
+%
 % Plots of mixing coefficients
-\begin{figure*}
+\begin{figure*}[htb]
   %
@@
 \end{figure*}
-
+%
+In cases where $(\bar\ell,\bar{m})=(\ell,m)$, the real part of $\sigma_{\LMlmn}$ varies about unity in a manner consistent with the Schwarzschild limit, where $\sigma_{\LMlmn}=\delta_{\bar\ell}^{\ell}\;\delta_{\bar{m}}^{m}$.
+%
+This is equally true in cases where $(\bar\ell,\bar{m}) \neq (\ell,m)$.
+%
+As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values.
+%
+\section{Discussion}
+\label{discuss}
+%
+\par We have developed upon previous techniques for the linear and pseudo-linear modeling of low noise data.
+%
+In particular, the \gmvp{} algorithm performs multivariate polynomial modeling of real and complex valued scalar functions with no inherent limitation on the number of domain parameters.
+%
+The \gmvr{} algorithm does the same with multivariate rational functions.
+%
+When applied to the modeling of analytically computed quantities, both algorithms perform extremely well in producing accurate and precise representations of training data, suggesting extended applicability of \gmvr{} and \gmvp{} similar problems.
+%
+\par Treating a toy problem with \gmvr{} demonstrates its ability to faithfully recover underlying model parameters for a plausible dataset.
+%
+This treatment also demonstrates the convergence of the algorithm's greedy phase with increasing iterations, as well as the convergence of an underlying iterative refinement phase (\ceqn{eq:rat4}).
+%
+%
+%
+% GMVR
+% \hspace{1cm}
+{\scriptsize
+\begin{algorithm}
+  %
+  \caption{\gmvr{}, a degree tempered stepwise algorithm for multivariate rational modeling of scalar data.}
+  \label{alg:gmvr}
+  %
+  \begin{algorithmic}[1]
+    %
+    \State {\bf Input:} $ \{ x, f, $max\_degree = 6$, tol \}$
+    \vskip 10pt
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol.
+This is the combined bulk for numerator and denominator symbols.
+    \State Define $\mathcal{A}_{\gmvr{}}$ according to Alg. (\ref{alg:A_gmvr}).
+    \State Given $max\_degree$, define, ${ D}$, a list of allowed polynomial degrees (e.g. $\{0,1,2,3,4,5,6\}$)
+    \For {$d$ \textbf{in}  ${ D}$ }
+      \State Define $\mlam_{bulk}^{(d)}$ as all symbols from $\mlam_{bulk}$ with degree less than or equal to current degree: $\mlam^{(d)}_{bulk}$
+      \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
+      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
+        \State \textbf{break}
+      \EndIf
+    \EndFor
+    \vskip 10pt
+    \State {\bf Output:} $\mlam^{(d)}_{opt}$
+    %
+  \end{algorithmic}
+  %
+\end{algorithm}
+}
+%
+\par Both \gmvp{} and \gmvr{} may be used to automatically determine the functional form and model for a given dataset that is expected to be respectively polynomial or rational.
+%
+An alternative use strategy is to use either \gmvp{} or \gmvr{} to determine a fitting ansatz for individual cases (e.g.
+individual \qnm{s}), and then use these results to develop a single ansatz for all cases.
+%
+This is what as been done for the modeling of \qnm{} frequencies and spherical-spheroidal mixing coefficients.
+%
+%
+\par \gmvp{} has been applied to the modeling \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit.
+%
+The fits presented are of direct use in Ref.
+\cite{London:2017bcn}, where efficiently evaluable \qnm{} frequencies are required to general template waveforms for \gw{} searches and parameter estimation.
+%
+The fits presented may find future use in Phenom or EOB based \gw{} models.
+%
+\par \gmvr{} has been applied to the modeling of mixing coefficients between the spherical and spheroidal harmonics.
+%
+These fits are of direct use in Ref. \cite{Carullo:2018sfu}, and may be of future use in similar ringdown-only models for the purpose of testing \gr{}.
+%
+\par While \gmvr{} and \gmvp{} show promise in the cases shown here, in their presented rudimentary form, both posses a number of limitations.
+%
+Neither currently performs cross-validation, given sufficiently dense training data.
+%
+And perhaps most notably, neither method directly accounts for information about the noise distribution within the training data.
+%
+As such, the methods presented are recommended primarily for datasets where noise is very small or negligible.
+%
+Nevertheless, the \gmvr{} toy problem demonstrates \gmvr{}'s ability to handle moderately noisy training data, suggesting current applicability to a variety of problems where polynomial interpolation is insufficient.
+%
+\par Of relevance to current and future \gw{} science, the models presented for \qnm{} frequencies and harmonic mixing coefficients have aided (e.g.
+Refs.
+\cite{Carullo:2018sfu,London:2018gaq,London:2017bcn} ), and are expected to continue aiding the development and implementation of \gw{} signal models.
+
+%--%%----%%----%%----%%----%%----%%----%%--%
+\section*{Acknowledgements}
+%--%%----%%----%%----%%----%%----%%----%%--%
+%
+The authors thank Mark Hannam for useful discussions.
+%
+The work presented in this paper was supported by Science and Technology Facilities Council (STFC)
+grant ST/L000962/1, and European Research Council Consolidator Grant 647839.
+%
+
+\newpage
+
+%
+\appendix
+
+% \section{Algorithms}
+% \label{app:algos}
+% % \begin{widetext}
+% %
+% \hspace{1cm}
+% {\scriptsize
+% \begin{algorithm}[H]
+%   %
+%   \caption{$\mathcal{A}_{\gmvr}$, the action for \gmvr. Model calculation given basis symbols, and output of model error estimate.}
+%   %
+%   \label{alg:A_gmvr}
+%   \begin{algorithmic}[1]
+%     %
+%     \State {\bf Input:} \{ $\mlam_{trial}$, $tol=10^{-3}$ \}
+%     \vskip 10pt
+%     \State Calculate $\alpha^{(1)}_k$ via \eqn{eq:pinv3}. Implicitly, $n=1$.
+%     \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
+%     \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$.
+%     \State $done = False$
+%     \While { not $done$ }
+%       \State Calculate $\alpha^{n+1}_{k}$  via \eqn{eq:pinv3}.
+%       \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
+%       \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
+%       \State $done = \epsilon^{(n-1)}-\epsilon^{(n)} < tol$
+%       \State (Implicitly, $n = n+1$)
+%     \EndWhile
+%     \vskip 10pt
+%     \State {\bf Output:} $\epsilon^{(n)}$
+%   \end{algorithmic}
+% \end{algorithm}
+% }
+% % \end{widetext}
+\newpage
+\section{Additional Equations}
+\label{app:eqns}
+
+%
+% Equations for mixing coefficients
+%
+\begin{widetext}
+  \input{src/ysprod_eqns}
+\end{widetext}
+
+% \section{Figures}
+% \label{app:figs}
+
+% %
+% % Plots of QNM frequencies
+% \begin{figure*}[htb]
+%   %
+%   \begin{tabular}{lr}
+%     \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
+%     \\
+%     \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
+%   \end{tabular}
+%   %
+% 	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+%   %
+%   Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$.
+Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
+%   %
+%   The grey dashed line marks the value of $\kappa$ where $\j{}=0$.
+Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+(Bottom) Percentage residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+}
+%   %
+%   \label{fig:qnm}
+%   %
+% \end{figure*}
+%
+% % Plots of mixing coefficients
+% \begin{figure*}[htb]
+%   %
+%   \begin{tabular}{lr}
+%     \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf} \\
+%     \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}
+%   \end{tabular}
+%   %
+% 	\caption{ Spherical-spheroidal harmonic mixing coefficients. Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
+%   %
+%   \label{fig:ys}
+%   %
+% \end{figure*}
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %
-\bibliographystyle{ieeetr}
+
+% %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %
+\newpage
+% \bibliographystyle{ieeetr}
+\bibliographystyle{mnras}
 \bibliography{src/mvf.bib}

### 2018-08-24 docs/mvfits_paper/mvf.tex
misc updates

@@
 %
-Perhaps most intriguingly, the formal series expansions of smooth functions support linear and rational models (e.g. Pad\'e approximants) having application to many datasets.
-%
-Here we will develop algorithms for the linear (polynomial and rational) modeling of scalar functions (real or complex valued) of many variables.
+Perhaps most intriguingly, the formal series expansions of smooth functions support linear and rational models (e.g. Pad\'e approximants) that have application to many datasets.
+%
+With this in mind, here, we will develop algorithms for the linear (polynomial and rational) modeling of scalar functions (real or complex valued) of many variables.
 %

### 2018-08-26 docs/mvfits_paper/mvf.tex
misc updates

@@
   %
-  GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to the problem of Runge's phenomenon.
+  GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to Runge's phenomenon.
 	%
@@
 %
-During this period, a few to dozens of \bbh{} signals are likely to be detected. \cite{Abbott:2016nhf}.
+During this period, a few to dozens of \bbh{} signals are likely to be detected \cite{Abbott:2016nhf}.
 %
@@
 %
-This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where only $n=0$ is explicitly considered.
-%
-The consequences of this choice, in particular mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,London:2018gaq}.
+This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where only $n=0$ is explicitly considered, and ${_{-2}}Y_{\ell m}$ are the spins weighted -2 spherical harmonics.
+%
+Only where $\jf \cw\lmn=0$ does $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.
+%
+The consequences of that choice, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,London:2018gaq}.
 %
@@
   \label{eq:rat3}
-  g_j = \sum_{k=0}^{R+V+1} \, z_{k} \, \psi_k(\vec{x}_j) \;,
+  g_j = \sum_{k=0}^{R+V} \, z_{k} \, \psi_k(\vec{x}_j) \;,
 \end{align}
@@
 %
-Neither currently performs cross-validation, given sufficiently dense training data.
+If given sufficiently dense training data, neither currently performs cross-validation.
 %

### 2018-08-26 docs/mvfits_paper/mvf.tex
misc updates

@@
 %
-\par Both Phenom and \eob{} approaches directly use phenomenological models (i.e.
-fits) for the \qnm{} frequencies, as these fits are more computationally efficient than the underlying analytic calculations, which involve the solving of continued fraction equations \cite{Leaver85}.
+\par Both Phenom and \eob{} approaches directly use phenomenological models for the \qnm{} frequencies, as these fits are more computationally efficient than the underlying analytic calculations, which involve the solving of continued fraction equations \cite{Leaver85}.
 %

### 2018-08-26 docs/mvfits_paper/mvf.tex
misc updates

@@
 %
-Only where $\jf \cw\lmn=0$ does $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.
-%
-The consequences of that choice, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,London:2018gaq}.
-%
-For the so-called \textit{Phenom} models, the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain \cite{Hannam:2013oca,London:2017bcn,Khan:2015jqa,Schmidt:2014iyl}.
+Only where $\jf \cw\lmn=0$ do $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.
+%
+The consequences of that approximation, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,Berti:2014fga,London:2018gaq}.
+%
+This approximation also applies to many of the so-called \textit{Phenom} models, where the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain \cite{Hannam:2013oca,London:2017bcn,Khan:2015jqa,Schmidt:2014iyl}.
 %

### 2018-08-27 docs/mvfits_paper/mvf.tex
misc updates

@@
 %
-The process begins by finding the single symbol (basis vector) that yields the most accurate model (e.g. in the sense of minimizing the least-squares error).
+The process begins by finding the single symbol (basis vector) that yields the most accurate model in the sense of minimizing the least-squares error.
 %
@@
 %
-In each new iteration, an all remaining symbols are added to the model one at a time, resulting in many trial models.
-%
-When considering all trial models, the single models symbol which yields the greatest increase in model accuracy is kept for the subsequent greedy iteration.
+In each subsequent iteration, remaining symbols are added to the model one at a time, resulting in many trial models, each with its own representation error.
+%
+The the trial model with smallest representation error is kept for the next greedy iteration.
 %
@@
 %
-The forward process is to end when the model accuracy, or changes thereof, pass a specified threshold.
+This forward greedy process ends when the model accuracy, or changes thereof, passes a previously specified threshold.
 %
@@
   %
-	\caption{ Spherical-spheroidal harmonic mixing coefficients. Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
+	\caption{ Spherical-spheroidal harmonic mixing coefficients.
+Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models.
+(Top Left) Mixing coefficients for cases where $(\bar{\ell},\bar{m})=(\ell,m)$.
+The dashed horizontal intersects each curve at the Schwarzschild limit where $\jf=0$.
+(Top Right) Mixing coefficients where $(\bar{\ell},\bar{m})\neq(\ell,m)$.
+(Bottom Left and Right) Factional residuals for mixing coefficient fits.
+}
   %

### 2018-08-27 docs/mvfits_paper/mvf.tex
misc updates

@@
   %
-	\caption{ Spherical-spheroidal harmonic mixing coefficients.
-Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models.
-(Top Left) Mixing coefficients for cases where $(\bar{\ell},\bar{m})=(\ell,m)$.
+	\caption{ Spherical-spheroidal harmonic mixing coefficients and percentage residual errors for spherical-spheroidal harmonic mixing coefficient fits.
+(\textit{Top Left}) Mixing coefficients for cases where $(\bar{\ell},\bar{m})=(\ell,m)$.
 The dashed horizontal intersects each curve at the Schwarzschild limit where $\jf=0$.
-(Top Right) Mixing coefficients where $(\bar{\ell},\bar{m})\neq(\ell,m)$.
-(Bottom Left and Right) Factional residuals for mixing coefficient fits.
+(\textit{Top Right}) Mixing coefficients where $(\bar{\ell},\bar{m})\neq(\ell,m)$.
+(\textit{Bottom Left and Right}) Factional residuals for mixing coefficient fits.
 }

### 2018-08-29 docs/mvfits_paper/mvf.tex
adding H to algo env to fix make
Update abstract

@@
   %
-  Towards the construction of these models, two algorithms are presented.
-  %
-  A greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method are presented for the automated modeling of polynomial and rational functions respectively.
+  Towards the construction of these models we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively.
   %
@@
 {\scriptsize
-\begin{algorithm}
+\begin{algorithm}[H]
   %

### 2018-08-29 docs/mvfits_paper/mvf.tex
Update introduction

@@
 %
-It is therefore efficient to avoid convergence issues by using accurate models for $\sigma\LMlmn$, which can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.
+It is therefore efficient to use accurate models for $\sigma\LMlmn$ which avoids convergence issues.
+These can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.
 %
@@
 %
-For consistency with the multipolar content of current ringdown models, here, we extend previous results to include the most significant multipoles with $\ell \leq 5$.
+For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$.
 %

### 2018-08-29 docs/mvfits_paper/mvf.tex
Update Methods introduction

@@
 %
-\par If we consider a scalar function, $f$, of $N$ variables sampled in $j$, $\vec{x}_j = \{x_{\alpha j}\}_{\alpha=0}^{N}$, then $f(\vec{x})_j$ can be represented (possibly inaccurately) as a sum over $K$ linearly independent basis functions, $\phi_k(\vec{x}_j)$:
+\par If we consider a scalar function, $f$, of $N$ variables sampled in $j$, $\vec{x}_j = \{x_{\alpha j}\}_{\alpha=0}^{N}$, then $f(\vec{x}_j)$ can be represented (possibly inaccurately) as a sum over $K$ linearly independent basis functions, $\phi_k(\vec{x}_j)$:
 %
@@
   \label{lin1}
-  f({\vec{x}})_j \; = \; \sum_{k=0}^{K} \; \mu_{k} \, \phi_{kj}\; .
+  f({\vec{x}}_j) \; = \; \sum_{k=0}^{K} \; \mu_{k} \, \phi_k(\vec{x}_j)\; .
 \end{align}
@@
 %
-In particular, defining $\hat{U} = \{\phi_{kj}\}$, and $\vec{f} = \{f_j\}$, then $\vec{f} = \hat{U} \; \vec{\mu}$, implies that
+In particular, defining ${U}_{jk} = \phi_k(\vec{x}_j)$, $f_j = f(\vec{x}_j)$ then $\vec{f} = \hat{U} \; \vec{\mu}$, implies that
 %
@@
 To consider these two approaches in a largely automated way (i.e.
-where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.
+where the set of possible basis functions is known, but the selected basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.
 %

### 2018-08-29 docs/mvfits_paper/mvf.tex
Revert selected qualifier to select

@@
 To consider these two approaches in a largely automated way (i.e.
-where the set of possible basis functions is known, but the selected basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.
+where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.
 %

### 2018-08-29 docs/mvfits_paper/mvf.tex
Update Methods::A+B

@@
 %
-\par Note that we will use the terms ``basis vector'' and ``model symbol'' interchangeably.
-However, in practice, it can be useful to represent basis vectors symbolically (e.g.
-with strings), and have a way of bijectively mapping between symbols and numerical basis vectors.
 %
@@
 %
-Note that in practice it may be useful to encode elements of $\mlam_{bulk}$ with strings representing their constituents (e.g. $x_0 x_0 x_1 x_2 x_2 x_4$ could be represented by the string ``001224'').
+Note that in practice it may be useful to encode elements of $\mlam_{bulk}$ with strings representing their constituents (e.g.
+$x_0 x_0 x_1 x_2 x_2 x_4$ could be represented by the string ``001224'').
+This provides a way of bijectively mapping between symbols and numerical basis vectors.
 %

### 2018-08-29 docs/mvfits_paper/mvf.tex
Update Methods::C

@@
 %
-\par However, we note that $\hat{P}$'s depending on $g$ signals that there is more to be done.
-%
-In particular, let us briefly consider the effect of zero-mean noise on $g$, e.g. $g \rightarrow g+n$.
+\par However, we note that $\hat{P}$ depends on $g$ signals.
+%
+Let us briefly consider the effect of zero-mean noise on $g$, e.g. $g \rightarrow g+n$.
 %
@@
 %
-\par Much as in the case of multivariate polynomial fitting, we are left with an un unknown number and content of basis symbols.
+\par Much as in the case of multivariate polynomial fitting, we are left with an unknown number and content of basis symbols.
 %

### 2018-08-29 docs/mvfits_paper/mvf.tex
Update Results::A
Update Results::B

@@
 %
-\par \fig{fig:gmvrtoy}'s left top and bottom panels show the convergence of Alg. (\ref{alg:A_gmvr})'s iterative refinement stage (i.e. its while-loop).
+\par \fig{fig:gmvrtoy}'s right top and bottom panels show the convergence of Alg. (\ref{alg:A_gmvr})'s iterative refinement stage (i.e. its while-loop).
 %
@@
 %
-We also wish the impose a domain transformation, $\kappa(\jf,\ell,m)$, such that $0 \leq \kappa \leq 1$ and the individual \qnm{} frequencies are made approx. polynomial in $\kappa$.
+We also wish to impose a domain transformation, $\kappa(\jf,\ell,m)$, such that $0 \leq \kappa \leq 1$ and the individual \qnm{} frequencies are made approx. polynomial in $\kappa$.
 %
@@
 %
-In particular, the domain map allows most \qnm frequencies to be well modeled by 4th order polynomials which include all lower degree terms; concurrently, the real and imaginary parts of each $\cw\lmn$ are modeled simultaneously.
+In particular, the domain map allows most \qnm{} frequencies to be well modeled by 4th order polynomials which include all lower degree terms; concurrently, the real and imaginary parts of each $\cw\lmn$ are modeled simultaneously.
 %
@@
 %
-Although each model's fractional error is within 2\%, each is error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current 2nd generation \gw{} efforts.
+Although each model's fractional error is within 2\%, each error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current 2nd generation \gw{} efforts.
 %

### 2018-08-29 docs/mvfits_paper/mvf.tex

@@
 %
-When applied to the modeling of analytically computed quantities, both algorithms perform extremely well in producing accurate and precise representations of training data, suggesting extended applicability of \gmvr{} and \gmvp{} similar problems.
+When applied to the modeling of analytically computed quantities, both algorithms perform extremely well in producing accurate and precise representations of training data, suggesting extended applicability of \gmvr{} and \gmvp{} to similar problems.
 %
@@
 %
-\par \gmvp{} has been applied to the modeling \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit.
+\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit.
 %
 The fits presented are of direct use in Ref.
-\cite{London:2017bcn}, where efficiently evaluable \qnm{} frequencies are required to general template waveforms for \gw{} searches and parameter estimation.
+\cite{London:2017bcn}, where efficiently evaluable \qnm{} frequencies are required to generate template waveforms for \gw{} searches and parameter estimation.
 %

### 2018-08-29 docs/mvfits_paper/mvf.tex
fixing regelate
clarifying method for ansatz development re sigmas

@@
 %
-In this, it may be that shown that $n$ may be entirely regelated to $\hat{P}$.
+In this, it may be that shown that $n$ may be entirely relegated to $\hat{P}$.
 %
@@
 %
-\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for \textit{all} $\sigma_{\LMlmn}$, and then apply this form to the modeling of all $\sigma_{\LMlmn}$.
+\par While it is possible to enforce extremal Kerr and Schwarzschild limiting conditions for $\sigma_{\LMlmn}$, we find it effective to first use \gmvr{} to determine a functional form that works for {individual} $\sigma_{\LMlmn}$, and then from these ansatz develop a single ansatz for all $\sigma_{\LMlmn}$.
 %

### 2018-08-29 docs/mvfits_paper/mvf.tex
minor updates to text

@@
 $%\end{align}
+, where $\omega\lmn$ is the central frequency of the ringing, and $1/\tau\lmn$ is the damping rate.
 .
@@
 %
-These frequencies and harmonic functions are the so-called \qnm{s}.
-%
-They are the eigen-solutions of the source free linearized \ee{} (i.e. \tk{'s} equations \cite{PhysRevLett.29.1114}) for a perturbed \bh{} with final mass, $\mf$, and dimensionless final spin, $\jf$.
+Together, these harmonic functions and frequencies constitute the \qnm{} solutions to \ee{}.
+%
+Specifically, they are the eigen-solutions of the source free linearized \ee{} (i.e.
+\tk{'s} equations \cite{PhysRevLett.29.1114}) for a perturbed \bh{} with final mass, $\mf$, and dimensionless final spin, $\jf$.
 %
@@
 %
-While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in the literature, there exist minor shortcomings which we wish to address here \cite{Berti:2005ys,Berti:2014fga}.
+While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in the literature (e.g. \cite{Berti:2005ys,Berti:2014fga}), there exist minor shortcomings which we wish to address here.
 %
@@
 %
-In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (See \ceqn{hlm}).
+In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (via \ceqn{hlm}).
 %
@@
 %
+Both algorithms are publicly available in \texttt{Python} via Ref. \cite{lionel_london_2018_1402516}.
+%
 %
@@
 %
-With this in mind, here, we will develop algorithms for the linear (polynomial and rational) modeling of scalar functions (real or complex valued) of many variables.
+With this in mind, here, we will develop algorithms for the linear (polynomial and rational) modeling of scalar functions (real or complex) of many variables.
 %
@@
 %
-In particular, defining ${U}_{jk} = \phi_k(\vec{x}_j)$, $f_j = f(\vec{x}_j)$ then $\vec{f} = \hat{U} \; \vec{\mu}$, implies that
+In particular, defining ${U}_{jk} = \phi_k(\vec{x}_j)$, $f_j = f(\vec{x}_j)$ and $\vec{f} = \hat{U} \; \vec{\mu}$, implies that
 %

### 2018-09-05 docs/mvfits_paper/mvf.tex
adding barusse formula for final spin with precessing BBH systems

@@
 \def\check#1{\red{#1}}
+\def\new#1{\blue{#1}}
 \def\remove#1{\hlred{#1}}
@@
   %
-  In particular, model based gravitational wave detection, and subsequent estimation of source parameters are supported by the low level modeling of information related to perturbed Kerr black holes.
-  %
-  Here, we summarize recent methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
-  %
-  Towards the construction of these models we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively.
+  On important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
+  %
+  Here, we present new methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
+  %
+  In particular, we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively.
   %
   GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to Runge's phenomenon.
+  %
+  GMVP is used to develop the first model for QNM frequencies explicitly enforces consistency with the extremal Kerr limit.
+  %
+  GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$.
+  %
+  We discuss the use of these models in current and future gravitational wave signal modeling.
 	%
@@
 %
-Concurrent with \virgo{}, the \aligo{} detectors will enter their third observing run in approximately late 2018.
+Concurrent with \virgo{}, the \aligo{} detectors will enter their third observing run in approximately early 2019.
 %
@@
 , where $\omega\lmn$ is the central frequency of the ringing, and $1/\tau\lmn$ is the damping rate.
-.
 %
@@
 %
-To this end, if we define $g^{(0)}=g$ (i.e. $g$ is the training data), with $\hat{P} = \hat{P}( \vec{g}^{\,(n)} )$, then \eqn{eq:pinv2} generalizes to
+If we define $g^{(0)}=g$ (i.e. $g$ is the training data), with $\hat{P} = \hat{P}( \vec{g}^{\,(n)} )$, then \eqn{eq:pinv2} generalizes to
 %

### 2018-09-05 positive/physics.py

@@ -328,8 +328,108 @@ def jf161100332(m1,m2,chi1,chi2):
     # Return answer
     return jf
 
+
+# Remnant Spin
+# https://arxiv.org/abs/1605.01938
+# Fabian Hofmann, Enrico Barausse, Luciano Rezzolla
+def jf160501938(m1,m2,chi1_vec,chi2_vec,L_vec=None):
+
+    '''
+    Remnant Spin
+    https://arxiv.org/abs/1605.01938
+    Fabian Hofmann, Enrico Barausse, Luciano Rezzolla
+    '''
+
+    # Import usefuls
+    from numpy import sqrt,pow,dot,array,cos,tan,arccos,arctan
+    from numpy.linalg import norm
+
+    # Handle inputs
+    if L_vec is None:
+        warning('No initial orbital angular momentum vevtor given. We will assume it is z-ligned.')
+        L_vec = array([0,0,1])
+    #
+    m1 = float(m1); m2 = float(m2)
+
+    # Table 1 (numbers copied from arxiv tex file: https://arxiv.org/format/1605.01938)
+    # bottom block
+    n_M = 3; n_J = 4
+    k = zeros( (n_M,n_N) )
+    k[0,1] = 3.39221;   k[0,2] = 4.48865;  k[0,3] = -5.77101
+    k[0,4] = -13.0459;  k[1,0] = 35.1278;  k[1,1] = -72.9336
+    k[1,2] = -86.0036;  k[1,3] = 93.7371;  k[1,4] = 200.975
+    k[2,0] = -146.822;  k[2,1] = 387.184;  k[2,2] = 447.009
+    k[2,3] = -467.383;  k[2,4] = -884.339; k[3,0] = 223.911
+    k[3,1] = -648.502;  k[3,2] = -697.177; k[3,3] = 753.738
+    k[3,4] = 1166.89;   xi = 0.474046
+
+    # Eq. 5
+    p = 1.0/3
+    Z1 = lambda a: 1 + (1-a*a)**p * (  (1+a)**p + (1-a)**p  )
+
+    # Eq. 6
+    Z2 = lambda a: sqrt( 3*a*a + Z1(a)**2 )
+
+    # Eq. 4
+    r_ISCO = lambda a: 3.0 + Z2(a) - ( a / abs(a) ) * sqrt( (3-Z1(a))*(3+Z1(a)+2*Z2(a)) )
+
[…]

### 2018-09-07 positive/physics.py
adding version of Hofmann et al fit that works for final spin

@@ -341,7 +341,7 @@ def jf160501938(m1,m2,chi1_vec,chi2_vec,L_vec=None):
     '''
 
     # Import usefuls
-    from numpy import sqrt,pow,dot,array,cos,tan,arccos,arctan
+    from numpy import sqrt,dot,array,cos,tan,arccos,arctan,zeros,sign
     from numpy.linalg import norm
 
     # Handle inputs
@@ -352,16 +352,25 @@ def jf160501938(m1,m2,chi1_vec,chi2_vec,L_vec=None):
     m1 = float(m1); m2 = float(m2)
 
     # Table 1 (numbers copied from arxiv tex file: https://arxiv.org/format/1605.01938)
-    # bottom block
-    n_M = 3; n_J = 4
-    k = zeros( (n_M,n_N) )
-    k[0,1] = 3.39221;   k[0,2] = 4.48865;  k[0,3] = -5.77101
-    k[0,4] = -13.0459;  k[1,0] = 35.1278;  k[1,1] = -72.9336
-    k[1,2] = -86.0036;  k[1,3] = 93.7371;  k[1,4] = 200.975
-    k[2,0] = -146.822;  k[2,1] = 387.184;  k[2,2] = 447.009
-    k[2,3] = -467.383;  k[2,4] = -884.339; k[3,0] = 223.911
-    k[3,1] = -648.502;  k[3,2] = -697.177; k[3,3] = 753.738
-    k[3,4] = 1166.89;   xi = 0.474046
+
+    # # bottom block -- doesnt work
+    # n_M = 3; n_J = 4
+    # k = zeros( (n_M+1,n_J+1) )
+    # k[0,1] = 3.39221;   k[0,2] = 4.48865;  k[0,3] = -5.77101
+    # k[0,4] = -13.0459;  k[1,0] = 35.1278;  k[1,1] = -72.9336
+    # k[1,2] = -86.0036;  k[1,3] = 93.7371;  k[1,4] = 200.975
+    # k[2,0] = -146.822;  k[2,1] = 387.184;  k[2,2] = 447.009
+    # k[2,3] = -467.383;  k[2,4] = -884.339; k[3,0] = 223.911
+    # k[3,1] = -648.502;  k[3,2] = -697.177; k[3,3] = 753.738
+    # k[3,4] = 1166.89;   xi = 0.474046
+    # k[0,0] = -3.82
+
[…]

### 2018-10-08 docs/mvfits_paper/mvf.tex
Fix minor typo in abstract

@@
   %
-  On important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
+  One important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
   %

### 2018-10-08 docs/mvfits_paper/mvf.tex
Update Methods intro with Marks comments
Update Methods::A with Marks comments

@@
 %
-The central player is \eqn{lin1} is the set of basis coefficients $\mu_{k}$.
+The central player in \eqn{lin1} is the set of basis coefficients $\mu_{k}$.
 %
@@
   \label{pinv1}
-  \hatP = \left( \left( \hatU^{-1} \right)^T \hatU^{-1} \right)^{-1}
+  \hatP = \left( \hatU^{*} \hatU \right)^{-1}\hatU^{*}
 \end{align}
@@
 %
-The the trial model with smallest representation error is kept for the next greedy iteration.
+The trial model with smallest representation error is kept for the next greedy iteration.
 %
@@
   %
-  \caption{A positive (forward) greedy algorithm, \pgreedy{}, \texttt{PGREEDY}.
+  \caption{A positive (forward) greedy algorithm, \pgreedy{}.
 Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error.

### 2018-10-08 docs/mvfits_paper/mvf.tex
Update Intro with Marks comments

@@
 %
-In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line.
+In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Pan:2013rra, Bohe:2016gbl, Nagar:2018zoe}.
 %
@@
 %
-This approximation also applies to many of the so-called \textit{Phenom} models, where the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain \cite{Hannam:2013oca,London:2017bcn,Khan:2015jqa,Schmidt:2014iyl}.
+This approximation also applies to many of the \textit{Phenom} models, where the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain \cite{Hannam:2013oca,London:2017bcn,Khan:2015jqa,Schmidt:2014iyl}.
 %

### 2018-10-08 docs/mvfits_paper/mvf.tex
making branch for comparison with eds recent changes

@@
   %
-  One important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
+  On important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
   %
@@
 %
-Most prominently, there is ongoing interest in signal models for \bbh{} \imr{} \cite{Blackman:2017dfb, London:2017bcn, Hannam:2013oca}.
+Most prominently, there is ongoing interest in efficient and accurate signal models for \bbh{} \imr{} \cite{Blackman:2017dfb, London:2017bcn, Hannam:2013oca}.
 %
@@
 %
-In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Pan:2013rra, Bohe:2016gbl, Nagar:2018zoe}.
+In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Cotesta:2018fcv, Buonanno:2000ef, Bohe:2016gbl}.
 %
@@
 %
-In the case of \texttt{PhenomHM} and derivative models, fits for the \qnm{} frequencies are used in the process of mapping $\tilde{h}_{22}(f)$ into other $\tilde{h}\LM(f)$ \cite{London:2017bcn}.
+In the case of the higher multipole model \texttt{PhenomHM} and its derivative models, fits for the \qnm{} frequencies are used in the process of mapping $\tilde{h}_{22}(f)$ into other $\tilde{h}\LM(f)$ \cite{London:2017bcn}.
 %
@@
 %
-In the context of \aligo{} \da{}, where source parameters are estimated using routines which sample over the space of possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit \cite{TheLIGOScientific:2016wfe}.
+In the context of \aligo{} \da{}, where source parameters are estimated using routines which sample over the space of all possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit \cite{TheLIGOScientific:2016wfe}.
 %
@@
 %
-For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$.
+For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$ \cite{London:2018gaq,London:2014cma}.
 %
@@
 %
-The description of \gmvp{} given here is complementary to similar algorithms used to model \qnm{} excitation amplitudes, $A\lmn$, as present in reference \cite{London:2018gaq,London:2014cma}.
+The description of \gmvp{} given here is complementary to similar algorithms used to model \qnm{} excitation amplitudes, $A\lmn$, as present in reference \cite{Carullo:2018sfu,London:2018gaq,London:2014cma}.
 %
@@
   \label{pinv1}
-  \hatP = \left( \hatU^{*} \hatU \right)^{-1}\hatU^{*}
+  \hatP = \left( \left( \hatU^{-1} \right)^T \hatU^{-1} \right)^{-1}
 \end{align}
@@
 %
-The trial model with smallest representation error is kept for the next greedy iteration.
+The the trial model with smallest representation error is kept for the next greedy iteration.
 %
@@
   %
-  \caption{A positive (forward) greedy algorithm, \pgreedy{}.
+  \caption{A positive (forward) greedy algorithm, \pgreedy{}, \texttt{PGREEDY}.
 Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error.
@@
   \label{eq:kappa}
-  \kappa(\jf,\ell,m) = \left( \log_3( 2 - \jf ) \right)^{1/(2-\ell+|m|)}
+  \kappa(\jf,\ell,m) = \left( \log_3( 2 - \jf ) \right)^{1/(2+\ell-|m|)}
 \end{align}

### 2018-10-08 docs/mvfits_paper/mvf.tex

@@
 %
-In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Cotesta:2018fcv, Buonanno:2000ef, Bohe:2016gbl}.
+In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Cotesta:2018fcv, Buonanno:2000ef, Bohe:2016gbl,Pan:2013rra, Bohe:2016gbl, Nagar:2018zoe}.
 %

### 2018-10-08 docs/mvfits_paper/mvf.tex
cleaning for submission

@@
 
-\input{src/definitions}
+\input{definitions}
 \def\check#1{\red{#1}}
@@
   \begin{tabular}{lr}
-    \includegraphics[width=0.49\textwidth]{fig/fits_w.pdf} & \includegraphics[width=0.49\textwidth]{fig/fits_tau.pdf}
+    \includegraphics[width=0.49\textwidth]{fits_w.pdf} & \includegraphics[width=0.49\textwidth]{fits_tau.pdf}
     \\
-    \includegraphics[width=0.49\textwidth]{fig/res_w.pdf} & \includegraphics[width=0.49\textwidth]{fig/res_tau.pdf}
+    \includegraphics[width=0.49\textwidth]{res_w.pdf} & \includegraphics[width=0.49\textwidth]{res_tau.pdf}
   \end{tabular}
@@
 %
-Worst, in cases where the underlying dataset is best described by a rational function, no polynomial order will yield satisfactory results (i.e. the well known ``Runge's phenomenon'').
+Worst, in cases where the underlying dataset is best described by a rational function, no polynomial order will yield satisfactory results (i.e.
+the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).
 %
@@
   %
-  \includegraphics[width=\textwidth]{fig/issue3_summary.pdf}
+  \includegraphics[width=\textwidth]{issue3_summary.pdf}
   %
@@
   %
-  \includegraphics[width=0.45\textwidth]{fig/issue3_pgreedy.pdf}
+  \includegraphics[width=0.45\textwidth]{issue3_pgreedy.pdf}
 	\caption{ Convergence of greedy process for \gmvr{} toy problem. }
@@
 \begin{widetext}
-	\input{src/cwfit_eqns}
+	\input{cwfit_eqns}
 \end{widetext}
@@
   \begin{tabular}{lr}
-    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf} \\
-    \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}
+    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_2.pdf} \\
+    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_4.pdf}
   \end{tabular}
@@
 
-% \section{Algorithms}
-% \label{app:algos}
-% % \begin{widetext}
-% %
-% \hspace{1cm}
-% {\scriptsize
-% \begin{algorithm}[H]
-%   %
-%   \caption{$\mathcal{A}_{\gmvr}$, the action for \gmvr. Model calculation given basis symbols, and output of model error estimate.}
-%   %
-%   \label{alg:A_gmvr}
-%   \begin{algorithmic}[1]
-%     %
-%     \State {\bf Input:} \{ $\mlam_{trial}$, $tol=10^{-3}$ \}
-%     \vskip 10pt
-%     \State Calculate $\alpha^{(1)}_k$ via \eqn{eq:pinv3}. Implicitly, $n=1$.
-%     \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
-%     \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$.
-%     \State $done = False$
-%     \While { not $done$ }
-%       \State Calculate $\alpha^{n+1}_{k}$  via \eqn{eq:pinv3}.
-%       \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
-%       \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
-%       \State $done = \epsilon^{(n-1)}-\epsilon^{(n)} < tol$
-%       \State (Implicitly, $n = n+1$)
-%     \EndWhile
-%     \vskip 10pt
-%     \State {\bf Output:} $\epsilon^{(n)}$
-%   \end{algorithmic}
-% \end{algorithm}
-% }
-% % \end{widetext}
+% 
 \newpage
@@
 \begin{widetext}
-  \input{src/ysprod_eqns}
+  \input{ysprod_eqns}
 \end{widetext}
@@
 
-% %
-% % Plots of QNM frequencies
-% \begin{figure*}[htb]
-%   %
-%   \begin{tabular}{lr}
-%     \includegraphics[width=\figfactor\textwidth]{fig/fits_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/fits_tau.pdf}
-%     \\
-%     \includegraphics[width=\figfactor\textwidth]{fig/res_w.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/res_tau.pdf}
-%   \end{tabular}
-%   %
-% 	\caption{ Fits of dimensionless \qnm{} central frequencies (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-%   %
-%   Before the application of $\kappa(\j{})$, points are spaced between -\CwFitCalibrationRegion and \CwFitCalibrationRegion according to \CwFitCalibrationRegion times the $\sin$ of a fiducial angle which is uniformly spaced between $-\pi/2$ and $\pi/2$.
-Values of $\j{}$ are shown in the upper axis for $\kappa$ at $l=m$.
-%   %
-%   The grey dashed line marks the value of $\kappa$ where $\j{}=0$.
-Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-(Bottom) Percentage residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-}
-%   %
-%   \label{fig:qnm}
-%   %
-% \end{figure*}
-%
-% % Plots of mixing coefficients
-% \begin{figure*}[htb]
-%   %
-%   \begin{tabular}{lr}
-%     \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_2.pdf} \\
-%     \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{fig/issue2_ysprod_4.pdf}
-%   \end{tabular}
-%   %
-% 	\caption{ Spherical-spheroidal harmonic mixing coefficients. Percentage residual errors for spherical-spheroidal harmonic mixing coefficient models. }
-%   %
-%   \label{fig:ys}
-%   %
-% \end{figure*}
 % %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% %
@@
 \bibliographystyle{mnras}
-\bibliography{src/mvf.bib}
+\bibliography{mvf.bib}
 \end{document}

### 2018-10-08 docs/mvfits_paper/issues/batch_compare_psi4.py

@@ -1,166 +1,0 @@
-
-# coding: utf-8
-
-# # Array Compare $\psi_4$ data with low and high level MMRDNS Models
-
-# ### Setup The Enviroment
-
-# In[6]:
-
-# Low-level import
-from numpy import array,loadtxt,linspace,zeros,exp,ones,unwrap,angle,pi
-
-# Setup ipython environment
-get_ipython().magic(u'load_ext autoreload')
-get_ipython().magic(u'autoreload 2')
-# %matplotlib inline
-
-# Import useful things from kerr
-from kerr.formula.ksm2_cw import CW as cwfit
-from kerr.formula.ksm2_sc import SC as scfit
-from kerr.pttools import leaver_workfunction as lvrwork
-from kerr import leaver,rgb
-from kerr.models import mmrdns
-
-#
-from nrutils import scsearch,gwylm,gwf
-
-# Setup plotting backend
-import matplotlib as mpl
-mpl.rcParams['lines.linewidth'] = 0.8
-mpl.rcParams['font.family'] = 'serif'
-mpl.rcParams['font.size'] = 12
-mpl.rcParams['axes.labelsize'] = 20
-from matplotlib.pyplot import *
-
-
-# ### Define master plotting function
-
-# In[19]:
-
-def plot_comparison(ll,mm,q,T0,ax):
-
-    # Load the data
-    data_file_string = '/Users/book/GARREG/Spectroscopy/Ylm_Depictions/NonPrecessing/MULTI_DATA_6/T0_%i_nmax2_Mmin97ll_Mmin_r75_qref1.50__p1_17-Mar-2014gnx_/Data_Sets/HRq-series/D9_q%1.1f_a0.0_m160/DEPICTION_INFO::NODD_INPUT_ll%i_mm%i_r75.asc'%(T0,q,ll,mm)
-    data = loadtxt(data_file_string)
-
-    # Collect raw fit data for later convenience
-    rfdata = {}
-    for k,row in enumerate(data):
-        #
-        ll,mm,q,m1,m2,x1,x2,jf,Mf,qid,rew,imw,rewfit,imwfit,reA,imA,reAmean,imAmean,minA,maxA,T1,dT,match,rmse,reB,imB,reBmean,imBmean,minB,maxB = row
[…]

### 2018-11-19 positive/learning.py
minor dradt changes

@@ -1274,6 +1274,7 @@ class mvpolyfit:
                   range_map = None,    # Operation to apply to range before fitting, and inverse. EXAMPLE: range_map = { 'forward': lambda domain,range: ..., 'backward': lambda domain,forward_range: ... }
                   plot = False,
                   data_label = None,
+                  center = False,
                   verbose = False ):   # Let the people know
 
 
@@ -1285,7 +1286,7 @@ class mvpolyfit:
         #%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#
         ''' Validate Inputs '''
         #%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#
-        this.__validate_inputs__(domain,scalar_range,basis_symbols,labels,range_map,data_label)
+        this.__validate_inputs__(domain,scalar_range,basis_symbols,labels,range_map,data_label,center)
 
         #%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#
         ''' Perform the fit '''
@@ -1353,15 +1354,34 @@ class mvpolyfit:
         # Center and adjust range values
         mapped_range = U(this.domain,this.range)
 
+        #
+        if this.center:
+            mu = mean(mapped_range)
+            sigma = std(mapped_range)
+            center_mapped_range = (mapped_range-mu)/sigma
+        else:
+            center_mapped_range = mapped_range
+
         # Estimate the coefficients of the basis symbols
-        a = dot( Q, mapped_range )
+        a = dot( Q, center_mapped_range )
+
+        #
+        if this.center:
+            a *= sigma
+            a[0] += mu
 
         # Store the fit coefficients
         this.coeffs = a
 
+
     # Create a functional representation of the fit
     def eval( this, vec ):
         '''A functional representation of the fit'''
+
+        # rc = vec.shape
+        # print '** ',rc
+        # print '** ',this.domain_dimension
+
         #
         ans_ = 0
         for k,b in enumerate(this.coeffs):
@@ -1652,9 +1672,11 @@ class mvpolyfit:
         # Plot the raw data points
         ax.scatter(this.domain[:,0],this.domain[:,1],_map(this.range),marker='o',color='k',label='Data',zorder=1, facecolors='none')
 
-        xlabel( '$x_0$' )
[…]

### 2018-11-19 positive/maths.py

@@ -927,7 +927,7 @@ def ishift( h, di ):
 
 
 # Find the interpolated global max location of a data series
-def intrp_max( y, domain=None, verbose=False, return_argmax=False, plot = False, pad = 3 ):
+def intrp_max( y, domain=None, verbose=False, return_argmax=False, plot = False, pad = 3, ref_index=None ):
 
     #
     from scipy.interpolate import UnivariateSpline as spline
@@ -975,6 +975,7 @@ def intrp_max( y, domain=None, verbose=False, return_argmax=False, plot = False,
 
         #
         k_max = argmax( y )
+        if ref_index: k_max = ref_index
         t_max = t[k_max]
         y_max = y[k_max]
 
@@ -1100,6 +1101,7 @@ def intrp_max( y, domain=None, verbose=False, return_argmax=False, plot = False,
         #
         if verbose: warning('Input is determined to be flat. A simple numerical mex will be used.')
         arg_max_dex = argmax( y )
+        if ref_index: arg_max_dex = ref_index
         arg_max = t[ arg_max_dex ]
         max_val = y[ arg_max_dex ]
 
@@ -1119,10 +1121,11 @@ def intrp_max( y, domain=None, verbose=False, return_argmax=False, plot = False,
 def intrp_argmax( y,
                   domain=None,
                   plot=False,
+                  ref_index = None,
                   verbose=False ):
 
     #
-    max_val,arg_max = intrp_max( y,domain=domain,verbose=verbose,return_argmax=True,plot=plot )
+    max_val,arg_max = intrp_max( y,domain=domain,verbose=verbose,return_argmax=True,plot=plot,ref_index=ref_index )
 
     #
     ans = arg_max
@@ -2077,6 +2080,47 @@ def reflect_unwrap( vec ):
 
                 #
                 ans[k] *= -1
+
+    #
+    return ans
+
+# Look for reflections in vector and correct
+def reflect_unwrap2( VEC, tol=0.1, domain = None ):
+    '''Look for point reflections in vector and correct'''
+
+    #
+    from numpy import array,sign,zeros_like,arange,hstack
+
+    #
+    def ru2(vec):
+
+        #
+        ans = array(vec)
+
+        #
+        for k,v in enumerate(vec):
+
+            #
+            if (k>0):
+
+                #
+                l = ans[k-1]
+                c = ans[k]
+
+                #
+                apply_reflection = abs(l+c) < tol*abs(l)
[…]

### 2019-01-28 positive/physics.py
adding berti fit function for ysprod

@@ -1694,3 +1694,95 @@ def leaver( jf,                     # Dimensionless BH Spin
 
     #
     return cw,cs
+
+
+#
+def ysprod14081860(j_,ll,mm,lmn):
+    import positive
+    '''
+    Fits for sherical-spheroidal mixing coefficients from arxiv:1408.1860 -- Berti, Klein
+
+    * The refer to mixing coefficients as mu_mll'n'
+    * their fits are parameterized by dimensionless BH spin j=a/M
+    * They model the real and imaginary parts separately as seen in Eq. 11
+    * Fitting coefficients are listed in table I
+
+    NOTE that the input format of this function is designed to be consistent with ysprod(...)
+    NOTE that tis function explicitely loads their full fit inpf from an external file
+
+    LondonL@mit.edu 2019
+    '''
+    tbl = loadtxt(parent(positive.__path__[0])+'/data/berti_swsh_fits.dat')
+    print tbl.shape
+    MM,LL,L,N,P1,P2,P3,P4,Q1,Q2,Q3,Q4,_,_,_,_ = tbl.T
+    l,m,n = lmn
+    k = (ll==LL) & (mm==MM) & (l==L) & (n==N)
+    if sum(k)!=1:
+        error('cannot find fit from Berti+ for (L,M,l,m,n) = (%i,%i,%i,%i,%)'%(L,M,l,m,n))
+    ans = (1 if ll==l else 0) + P1[k]*j_**P2[k] + P3[k]*j_**P4[k] + 1j * ( Q1[k]*j_**Q2[k] + Q3[k]*j_**Q4[k] )
+    return ans
+
+#
+def ysprod14081860_from_paper_is_broken(j,L,M,lmn):
+    '''
+    Fits for sherical-spheroidal mixing coefficients from arxiv:1408.1860 -- Berti, Klein
+
+    * The refer to mixing coefficients as mu_mll'n'
+    * their fits are parameterized by dimensionless BH spin j=a/M
+    * They model the real and imaginary parts separately as seen in Eq. 11
+    * Fitting coefficients are listed in table I
+
+    NOTE that the input format of this function is designed to be consistent with ysprod(...)
[…]

### 2019-01-28 docs/mvfits_paper/mvf.tex
minor dradt changes
updating caption for ysprods to include description of Berti comparison

@@
   Models of black hole properties play an important role in the ongoing direct detection of gravitational waves from black hole binaries.
-  %
 One important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
-  %
 Here, we present new methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
-  %
 In particular, we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively.
-  %
-  GMVR is a quasi-linear numerical method for interpolating rational functions. It therefore represents a solution to Runge's phenomenon.
-  %
+GMVR is a quasi-linear numerical method for interpolating rational functions.
+It therefore represents a solution to Runge's phenomenon.
 GMVP is used to develop the first model for QNM frequencies explicitly enforces consistency with the extremal Kerr limit.
-  %
 GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$.
-  %
 We discuss the use of these models in current and future gravitational wave signal modeling.
@@
     \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_2.pdf} \\
-    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_3.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_4.pdf}
+    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_3v2.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_4v2.pdf}
   \end{tabular}
@@
 (\textit{Bottom Left and Right}) Factional residuals for mixing coefficient fits.
+For comparison, residual errors for the fits in Ref.
+\cite{Berti:2014fga} are also shown over their region of validity in \bh{} spin.
+Note that makers match between grey and colored data points.
 }

### 2019-01-28 docs/mvfits_paper/mvf.tex
adding sentance in text to refer to Berti comparison

@@
 (\textit{Bottom Left and Right}) Factional residuals for mixing coefficient fits.
-For comparison, residual errors for the fits in Ref.
-\cite{Berti:2014fga} are also shown over their region of validity in \bh{} spin.
+For comparison, residual errors for the fits in Ref.~\cite{Berti:2014fga} are also shown over their region of validity in \bh{} spin.
 Note that makers match between grey and colored data points.
@@
 As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values.
+%
+For comparison, fractional residual error for models in Ref.~\cite{Berti:2014fga} are also shown. 
 %

### 2019-01-30 positive/physics.py
adding QNM freq fit for Cook+ 2014

@@ -1696,9 +1696,10 @@ def leaver( jf,                     # Dimensionless BH Spin
     return cw,cs
 
 
-#
-def ysprod14081860(j_,ll,mm,lmn):
+# Fit for spherica-sphoidal harmonic inner-product from Berti et al
+def ysprod14081860(j,ll,mm,lmn):
     import positive
+    from numpy import loadtxt
     '''
     Fits for sherical-spheroidal mixing coefficients from arxiv:1408.1860 -- Berti, Klein
 
@@ -1713,16 +1714,33 @@ def ysprod14081860(j_,ll,mm,lmn):
     LondonL@mit.edu 2019
     '''
     tbl = loadtxt(parent(positive.__path__[0])+'/data/berti_swsh_fits.dat')
-    print tbl.shape
-    MM,LL,L,N,P1,P2,P3,P4,Q1,Q2,Q3,Q4,_,_,_,_ = tbl.T
-    l,m,n = lmn
-    k = (ll==LL) & (mm==MM) & (l==L) & (n==N)
-    if sum(k)!=1:
-        error('cannot find fit from Berti+ for (L,M,l,m,n) = (%i,%i,%i,%i,%)'%(L,M,l,m,n))
-    ans = (1 if ll==l else 0) + P1[k]*j_**P2[k] + P3[k]*j_**P4[k] + 1j * ( Q1[k]*j_**Q2[k] + Q3[k]*j_**Q4[k] )
+
+    def lowlevel(J,__mm__):
+        MM,LL,L,N,P1,P2,P3,P4,Q1,Q2,Q3,Q4,_,_,_,_ = tbl.T
+        l,m,n = lmn
+        k = (ll==LL) & (__mm__==MM) & (l==L) & (n==N)
+        if sum(k)!=1:
+            error('cannot find fit from Berti+ for (L,M,l,m,n) = (%i,%i,%i,%i,%)'%(L,M,l,m,n))
+        lowlevel_ans = (1.0 if ll==l else 0) + P1[k]*J**P2[k] + P3[k]*J**P4[k] + 1J * ( Q1[k]*J**Q2[k] + Q3[k]*J**Q4[k] )
+        return lowlevel_ans
+
+    # from numpy import array,ndarray
+    # if not isinstance( j, ndarray ):
[…]

### 2019-01-31 positive/physics.py
adding berti fits for QNM frequencies

@@ -1699,7 +1699,7 @@ def leaver( jf,                     # Dimensionless BH Spin
 # Fit for spherica-sphoidal harmonic inner-product from Berti et al
 def ysprod14081860(j,ll,mm,lmn):
     import positive
-    from numpy import loadtxt
+    from numpy import loadtxt,array,ndarray
     '''
     Fits for sherical-spheroidal mixing coefficients from arxiv:1408.1860 -- Berti, Klein
 
@@ -1718,26 +1718,22 @@ def ysprod14081860(j,ll,mm,lmn):
     def lowlevel(J,__mm__):
         MM,LL,L,N,P1,P2,P3,P4,Q1,Q2,Q3,Q4,_,_,_,_ = tbl.T
         l,m,n = lmn
+        flip = False
+        if J<0:
+            J = abs(J)
+            __mm__ *= -1
+            flip = True
         k = (ll==LL) & (__mm__==MM) & (l==L) & (n==N)
         if sum(k)!=1:
             error('cannot find fit from Berti+ for (L,M,l,m,n) = (%i,%i,%i,%i,%)'%(L,M,l,m,n))
-        lowlevel_ans = (1.0 if ll==l else 0) + P1[k]*J**P2[k] + P3[k]*J**P4[k] + 1J * ( Q1[k]*J**Q2[k] + Q3[k]*J**Q4[k] )
-        return lowlevel_ans
+        lowlevel_ans = (1.0 if ll==l else 0) + P1[k]*J**P2[k] + P3[k]*J**P4[k] + 1j * ( Q1[k]*J**Q2[k] + Q3[k]*J**Q4[k] )
+        return (lowlevel_ans if not flip else lowlevel_ans.conj()).conj()
 
-    # from numpy import array,ndarray
-    # if not isinstance( j, ndarray ):
-    #     j = array([j])
-    # ans = []
-    # for jj in j:
-    #     if jj<0:
-    #         ans.append( lowlevel(-jj,-mm) )
-    #     else:
-    #         ans.append( lowlevel(jj,mm) )
-    # ans = array(ans)
-
-    ans = lowlevel(j,mm)
-
-    return ans
+    #
+    if isinstance(j,(list,tuple,ndarray)):
+        return array( [ lowlevel(j_,mm) for j_ in j ] )
+    else:
+        return lowlevel(j,mm)
 
 
[…]

### 2019-01-31 docs/mvfits_paper/mvf.tex
updating cw fit comparison notebooks and plots

@@
   %
-  \begin{tabular}{lr}
-    \includegraphics[width=0.49\textwidth]{fits_w.pdf} & \includegraphics[width=0.49\textwidth]{fits_tau.pdf}
+  \begin{tabular}{ll}
+    {\includegraphics[width=0.49\textwidth]{fits_w.pdf}} & {\includegraphics[width=0.49\textwidth]{fits_tau.pdf}}
+    % \\
+    % \includegraphics[width=0.49\textwidth]{res_w.pdf} & \includegraphics[width=0.49\textwidth]{res_tau.pdf}
     \\
-    \includegraphics[width=0.49\textwidth]{res_w.pdf} & \includegraphics[width=0.49\textwidth]{res_tau.pdf}
+    \hspace{0.35cm}\includegraphics[width=0.43\textwidth]{res_cw_0.pdf} & \hspace{0.3cm}\includegraphics[width=0.43\textwidth]{res_cw_1.pdf}
   \end{tabular}
@@
   %
-  \begin{tabular}{lr}
-    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_1.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_2.pdf} \\
-    \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_3v2.pdf} & \includegraphics[width=\figfactor\textwidth]{issue2_ysprod_4v2.pdf}
+  \begin{tabular}{ll}
+    \hspace{-0.21cm}\includegraphics[width=0.48\textwidth]{issue2_ysprod_1.pdf} & \includegraphics[width=0.48\textwidth]{issue2_ysprod_2.pdf} \\
+    \includegraphics[width=0.48\textwidth]{issue2_ysprod_3v2.pdf} & \hspace{0.3cm}\includegraphics[width=0.48\textwidth]{issue2_ysprod_4v2.pdf}
   \end{tabular}

### 2019-02-01 docs/mvfits_paper/mvf.tex
updating ref responses

@@
 %
-Here, the labels $\ell$ and $m$ are polar and azimuthal eigenvalues of \tk{'s} angular equations, where units of $M_i=1$ (e.g. the initial mass of the \bbh{} system), and $c=1$.
-%
-In the third line of \eqn{hrd}, we represent $h$ in terms of \textit{spherical} harmonic multipoles.
+Here, the labels $\ell$ and $m$ are polar and azimuthal eigenvalues of \tk{'s} angular equations, where total mass and the speed of light are set to unity (i.e. $M=c=1$).
+%
+Note that barred indices, namely $\bar{\ell}$ and $\bar{m}$, will refer to \textit{spherical} harmonics, leaving the unbarred indices to refer to the spheroidals.
+%
+In the third line of \eqn{hrd}, we represent $h$ in terms of {spherical} harmonic multipoles.
 %
@@
 %
-In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Cotesta:2018fcv, Buonanno:2000ef, Bohe:2016gbl,Pan:2013rra, Bohe:2016gbl, Nagar:2018zoe}.
+In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Cotesta:2018fcv, Buonanno:2000ef,
+Bohe:2016gbl,Pan:2013rra, Bohe:2016gbl, Nagar:2018zoe}.
 %
@@
 %
-Only where $\jf \cw\lmn=0$ do $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.
+Only where $\jf \cw\lmn=0$ do $_{-2}S\lmn( 0,\theta,\phi) = {_{-2}}Y_{\ell m}(\theta,\phi)$, which makes equating the spherical and spheroidal harmonics approximate at best for general values of $\jf \cw\lmn$.
 %
@@
 %
-In that setting, it is demonstrated that \qnm{} frequencies correlate with the morphology of each $h\LM$ in not only \rd{}, but also merger and late inspiral, as is implied by the source's causal connectedness pre and post merger.
+In that setting, it is demonstrated that \qnm{} frequencies are linked to the amplitude and phase of each $h\LM$ in not only \rd{}, but also merger and late inspiral, as is implied by the source's causal connectedness pre and post merger.
 %
@@
 %
-is the \textit{pseudo-inverse} \cite{Moore1920,Penrose:1955} of $\hatU$.
+is the \textit{pseudo-inverse} \cite{Moore1920,Penrose:1955} of $\hatU$, which exists if $\hatU^{*} \hatU$ is nonsingular.
 %
@@
 %
-This forward greedy process ends when the model accuracy, or changes thereof, passes a previously specified threshold.
+This forward greedy process ends when the model accuracy, and/or changes thereof, passes a previously specified threshold.
 %
@@
   \caption{A positive (forward) greedy algorithm, \pgreedy{}.
-Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error.
+Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error (e.g.
+L2 norm).
 In this setting, $\mathcal{A}$ is assumed to have access to peripheral information, such as the training data.}

### 2019-02-01 docs/mvfits_paper/mvf.tex
adding citations for stepwise

@@
 To consider these two approaches in a largely automated way (i.e.
-where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf}.
+where the set of possible basis functions is known, but the select basis functions ultimately used are \textit{learned}), we will make use of the \textit{greedy} algorithm approach \cite{Field:2011mf, GVK022791892, 1978AnSta, Pandit84}.
 %
@@
 %
-\par A well known method for finding an approximate solution to this problem is the so-called ``greedy'' algorithm:
+\par A well known method for finding an approximate solution to this problem is the so-called ``greedy'' algorithm (e.g. \cite{Field:2011mf, GVK022791892}):
 %

### 2019-02-01 docs/mvfits_paper/mvf.tex
adding more to response to second ref

@@
 %
-In the second line, the equality has been replaced by an approximation as we have limited the linear representation to $K$ terms.
+In the second line, the equality has been replaced by an approximation as we have limited the linear representation to $K+1$ terms.
 %
@@
     \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product (i.e. tensor product) of the power set of each basis symbol
     \State Define $\mathcal{A}_{\gmvp{}}$ according to Alg. (\ref{alg:A_gmvp}).
@@
 %
-Each term is an element of the $n$-fold cartesian inner-product of the power-sets of each model dimension.
-That is $\mlam_{bulk} = \{x_0,x_1 ..
-x_N, ...
-x_0^1, x_0^2, x_0^3, ...
-, (x_0^K x_1^K ...
-x_N^K) \}$.
+Each term is an element of the tensor-product of the power-sets of each model dimension. That is $\mlam_{bulk} = \{x_0,x_1 .. x_N, ... x_0^1, x_0^2, x_0^3, ...  , (x_0^K x_1^K ... x_N^K) \}$.
 %
@@
 (\textit{center top}) Same as left most panel, but in index space.
-(\textit{center bottom}) Fractional residual error (grey blocks) along with uniform (black) and gaussian (red) fits to error.
-(\textit{top right}) convergence of the L2 norm during iterative refinement.
+(\textit{center bottom}) {Percent residual error with respect to validation data (grey blocks) along with uniform (black) and gaussian (red) fits to error.
+The validation data were generated in the same manner as the training data.} (\textit{top right}) convergence of the L2 norm during iterative refinement.
 (\textit{bottom right}) Same as top right, but on log scale, where $\epsilon_0$ is the value of $\epsilon$ at the final $k^{\mathrm{th}}$ iteration of refinement.
@@
 %
-\par To generate the test data, \eqn{eq:gmvrtoy1} is evaluated with 25 points in $x_0$ and $x_1$, where each is between -3 and 3.
+\par To generate the test data, \eqn{eq:gmvrtoy1} is evaluated with 25 points along $x_0$ and $x_1$ (with $25^2$ total points), where each is between -3 and 3.
 Though not a requirement of \gmvr{}, for simplicity of presentation, domain points are equally spaced.
@@
 %
-\fig{fig:gmvrtoy}'s central bottom panel displays the distribution of fractional residuals, and demonstrates their approximately flat distribution.
+\fig{fig:gmvrtoy}'s central bottom panel displays the distribution of percentage residuals with respect to validation data generated in the same manner as training data.
 %
@@
 %
-Specifically, when considering many noise realizations, we find that sample noise and residuals have an average correlation of $99.46\%$.
+Moreover, when considering many noise realizations to generate validation data, we find that sample noise and residuals have an average correlation of $99.46\%$.
 %
@@
 %
-\par Lastly, \fig{fig:qnm}'s bottom two panels show fractional residual errors.
-%
-Although each model's fractional error is within 2\%, each error is dominated by well known nonlinear oscillations which are considered to be outside of the experimental accuracy of current 2nd generation \gw{} efforts.
+\par Lastly, \fig{fig:qnm}'s bottom two panels show absolute fractional residual errors of the complex frequency, $\cw\lmn = \omega\lmn + i/\tau\lmn$.
+%
+Although each model's fractional error is within 1\% of the perturbation theory result, each is dominated by systematic error due to the choice fitting ansatz.
+%
+For comparison, the same residual errors are shown in gray for the model presented in Ref.~\cite{Berti:2005ys}.
 %
@@
     \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product of the power set of each basis symbol.
-This is the combined bulk for numerator and denominator symbols.
+    \State Define, $\mlam_{bulk}$, the bulk symbol space using the tensor-product of the power set of each basis symbol. This is the combined bulk for numerator and denominator symbols.
     \State Define $\mathcal{A}_{\gmvr{}}$ according to Alg. (\ref{alg:A_gmvr}).

### 2019-02-02 docs/mvfits_paper/referee_reports_and_responses/Response_Ref1.txt
intermediate update prior to resubmission

Response for Referee #1
---

1. (p. 1, L17-17) The referee makes a valid, though largely semantic point regarding the use of interpolating in the abstract as it related to GMVR and Runge's phenomenon. We kindly note that GMVR is an iterative regression method that works for equally spaced grids, and constructs rational functions (equivalently, sums of rational functions) that smoothly connect or interpolate data assuming a rational ansatz.

2. (p. 1, L32) Thank you. We have added the citation.

3. (p. 1, L44) We have added this reference.

4. (p. 1, L46) We have kept only Leaver's reference at this line. There are indeed many many publications that could be cited here, but Leaver's is one of the earliest and most relevant.

5. (p. 1, L52) We have altered the language here to not mention the topic of completeness.

6. (Third Paragraph) We now no longer constrain this discussion to n=0. The text has been modified to include updated references and now state (perhaps uninformatively) that all phenom models have high frequency regions that are consistent with perturbation theory.

7. (p. 1, L49-50) Thank you. We hope that the current text will avoid any confusion.

8. (p. 1, L52-53) Thank you. We hope that the current text will avoid any confusion.

9. (p. 2, L30) Thank you. We hope that the current text will avoid any confusion.

10. (p. 2, L30) Thank you. We agree that Yang+ should be referenced here.

11. (p. 2, L39)

### 2019-02-02 docs/mvfits_paper/mvf.tex
intermediate update prior to resubmission

@@
 %
-During this period, a few to dozens of \bbh{} signals are likely to be detected \cite{Abbott:2016nhf}.
+During this period, a few to dozens of \bbh{} signals are likely to be detected \cite{Abbott:2016nhf,Abbott2018OS}.
 %
@@
 %
-These discrete frequencies have associated radial and spatial functions which are \textit{spheroidal} harmonic in nature \cite{Leaver85,London:2014cma}.
+These discrete frequencies have associated radial and spatial functions which are \textit{spheroidal} harmonic in nature \cite{Leaver85}.
 %
@@
 %
-The well known and effective completeness of these solutions allows \grad{} from generic perturbations to be well approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with the spin weight -2 spheroidal harmonics, $_{-2}S\lmn$.
+These solutions allow \grad{} from generic perturbations to be well approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with the spin weight -2 spheroidal harmonics, $_{-2}S\lmn$.
 %
@@
 %
-This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where only $n=0$ is explicitly considered, and ${_{-2}}Y_{\ell m}$ are the spins weighted -2 spherical harmonics.
+This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where ${_{-2}}Y_{\ell m}$ are the spins weighted -2 spherical harmonics.
 %
@@
 %
-The consequences of that approximation, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,Berti:2014fga,London:2018gaq}.
-%
-This approximation also applies to many of the \textit{Phenom} models, where the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain \cite{Hannam:2013oca,London:2017bcn,Khan:2015jqa,Schmidt:2014iyl}.
-%
-\par Both Phenom and \eob{} approaches directly use phenomenological models for the \qnm{} frequencies, as these fits are more computationally efficient than the underlying analytic calculations, which involve the solving of continued fraction equations \cite{Leaver85}.
+The consequences of that approximation, in particular the mixing between spherical and spheroidal harmonics, are discussed in reference \cite{London:2014cma,Berti:2014fga,London:2018gaq,Kelly:2012nd}.
+%
+This approximation also applies to the \textit{Phenom} models,
+where the frequency domain multipoles, $\tilde{h}\LM(f)$, are constructed such that their high frequency behavior is consistent with \eqn{hrd} in the time domain
+%
+\cite{ Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq, Khan:2018fmp }.
+%
+\par Both Phenom and \eob{} approaches either use phenomenological models of remnant \bh{} mass and spin to interpolate over tables of \qnm{} frequencies, or phenomenological models for \qnm{} frequencies are used directly.
+%
+Either approach typically incurs less computational cost that the direct numerical calculation of \qnm{} frequencies, which may involve, for example, the solving of continued fraction equations \cite{Leaver85}.
 %
@@
 %
-While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in the literature (e.g. \cite{Berti:2005ys,Berti:2014fga}), there exist minor shortcomings which we wish to address here.
+While models for $\cw\lmn$ and $\sigma\LMlmn$ are present in the literature (e.g. \cite{Berti:2005ys, Berti:2014fga, Cook:2014cta}), there exist minor shortcomings which we wish to address here.
+%
+\par For both the \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.
+%
+This perspective reflects the empirical observation that the remnant spin of \bbh{} mergers smoothly connects regions of positive and negative spin \cite{Husa:2015iqa,London:2018gaq}.
 %
@@
 $\jf \rightarrow 1$) some of the frequencies have zero-damping (i.e.
-$\tau\lmn \rightarrow \infty$) \cite{Zimmerman:2015trm}.
-%
-In the context of \aligo{} \da{}, where source parameters are estimated using routines which sample over the space of all possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit \cite{TheLIGOScientific:2016wfe}.
-%
-Here, we present the first models for $\cw\lmn$ that explicitly account for zero-damping in the extremal Kerr limit.
-%
-\par For the modeling of $\sigma\LMlmn$, we note that the results presented in \cite{Berti:2014fga} are limited to cases where the azimuthal indices, $\ell$ and $\bar{\ell}$, are less than or equal to 3.
-%
-As the most advanced signal models include at least $\ell$ or $\bar{\ell}$ of 3, there is use in extending current results.
-%
-In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (via \ceqn{hlm}).
-%
-For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$ \cite{London:2018gaq,London:2014cma}.
+$\tau\lmn \rightarrow \infty$) \cite{Yang:2012pj,Zimmerman:2015trm}.
+%
+In the context of \gw{} \da{}, where source parameters are estimated using routines which sample over the space of all possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit \cite{TheLIGOScientific:2016wfe}.
+%
+Here, we present the first models for $\cw\lmn$ that explicitly account for zero-damping \textit{and} non-zero-damping in the extremal Kerr limit.
+%
+% \par For the modeling of $\sigma\LMlmn$, we note that the results presented in \cite{Berti:2014fga} are limited to cases where the azimuthal indices, $\ell$ and $\bar{\ell}$, are less than or equal to 3.
+% %
+% As the most advanced signal models include at least $\ell$ or $\bar{\ell}$ of 3, there is use in extending current results.
+% %
+% In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (via \ceqn{hlm}).
+% %
+% For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$ \cite{London:2018gaq,London:2014cma}.
+%
+\par For the modeling of $\sigma\LMlmn$, we note that the \cite{Berti:2014fga} do not appear to include the \qnm{s} which rotate counter to the \bh{} spin direction (i.e. ``mirror-modes'').
+%
+In addition to our
 %

### 2019-02-03 docs/mvfits_paper/referee_reports_and_responses/Response_Ref1.txt
more additions to ref report 2 --- the ref is a bellend

@@
 
-11. (p. 2, L39)
+11. (p. 2, L39) Thank you. We have updated this section to avoid any confusion.
+
+12. (In Eq.6) Thank you. We have clarified the notation.
+
+13.
+(p.
+2, L26-27) Thank you for mentioning the Stone-Weierstrass theorem.
+We do not wish to reference this theorem in place of the series expansion as the latter is more accessible to a physics audience.
+We note that our introduction to the discussion is generally applicable given some smooth functoin and an epsilon neighborhood around a point.
+We intend primarily to motivate a general numtinobial basis perspective of our algorithms from first principles.
+he text has been modified in an effort to clarify this intention.
+
+14. (Algs. 2 and 5 ...) Thank you. We have clarified that we refer to the set of all multinomial combinations of basis vectors up to a predefined maximum order.
+
+15. (Algs. 2 and 5 ...) Thank you. We have corrected these lines to reference epsilons.
+
+16. (p. 3, L60) The current description of \lambda_{bulk} seeks to communicate the presense of the constant term.
+
+17. (p. 5, L3-4) We refer the reviewer to the introducion section here: https://en.wikipedia.org/wiki/Runge%27s_phenomenon. We have sought to clarify the text to minimize confusion.
+
+18. ( Eq. 20 ) We refer the referee to Eq 21
+
+19. Via Eq. 15, n>=1 for alpha. Here, "implicitely" n plays no real role in the algorithm and therefore need not be stored and increamented.
+
+20. (Alg. 4, step 4) Thank you. We have defined var to be the variance.
+
+21. (Alg. 4, step 4) Thank you. Yes.
+
+22. (p. 8, final line) We have clarified the text.
+
+23. (Fig. 4) We have clarified the text.
+
+24. Code: While we are appreciative of the referee's comments, we point out to the submitted draft only pertains to the GMVP and GMVR algorithms.

### 2019-02-03 docs/mvfits_paper/mvf.tex
more additions to ref report 2 --- the ref is a bellend

@@
 %
-\cite{ Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq, Khan:2018fmp }.
+\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq,Khan:2018fmp}.
 %
@@
 %
-Here, we present the first models for $\cw\lmn$ that explicitly account for zero-damping \textit{and} non-zero-damping in the extremal Kerr limit.
-%
-% \par For the modeling of $\sigma\LMlmn$, we note that the results presented in \cite{Berti:2014fga} are limited to cases where the azimuthal indices, $\ell$ and $\bar{\ell}$, are less than or equal to 3.
-% %
-% As the most advanced signal models include at least $\ell$ or $\bar{\ell}$ of 3, there is use in extending current results.
-% %
-% In particular, it is well known that $\sigma_{43330}$ can have a significant impact on the $(4,3)$ spherical multipole (via \ceqn{hlm}).
-% %
-% For consistency with the multipolar content of current ringdown models, we extend previous results to include the most significant multipoles with $\ell \leq 5$ \cite{London:2018gaq,London:2014cma}.
+Like Ref.~\cite{Cook:2014cta}, we present models for $\cw\lmn$ that explicitly account for zero-damping in the extremal Kerr limit.
+%
+We go further by presenting models that also account for non-zero-damping in modes such as $(\ell,m,n)=(2,1,0)$ and $(3,2,0)$.
+%
 %
@@
 %
-In addition to our
+Here these \qnm{} are explicitly modeled on a continuation of the positive spin line to negative spin.
 %
@@
 %
-In \sec{discuss}, we review the performance of \gmvp{} and \gmvr{}, and we discuss current and potential applications for these methods.
+Quantitative comparisons are made between our models and those presented in Refs.~\cite{Berti:2005ys, Berti:2014fga}.
+%
+In \sec{discuss}, we review the effectiveness of \gmvp{} and \gmvr{}, and we discuss current and potential applications for these methods.
 %
@@
 %
+Here ``$*$'' denotes the conjugate transpose.
+%
 \par Equations (\ref{lin1}), and related discussion through \eqn{pinv1} illustrate the most rudimentary solution to the linear modeling problem.
@@
 Note that a required input, $\mathcal{A}$, is a function that takes in a list of basis symbols, and outputs an estimator of fit error (e.g.
-L2 norm).
+$L^2$ norm).
 In this setting, $\mathcal{A}$ is assumed to have access to peripheral information, such as the training data.}
@@
 %
-given training data thought to be related to a smooth multivariate function, it may in many cases be well approximated by a truncated series expansion in an appropriate coordinate basis.
+given training data thought to be related to a smooth multivariate function, it may, particularly on small scales, be well approximated by a truncated series expansion in an appropriate coordinate basis.
 %
@@
     \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the $n$-fold cartesian inner-product (i.e. tensor product) of the power set of each basis symbol
+    \State Define, $\mlam_{bulk}$, the bulk symbol space, to be the set of all multinomial combinations of basis vectors up to a predefined maximum order.
     \State Define $\mathcal{A}_{\gmvp{}}$ according to Alg. (\ref{alg:A_gmvp}).
@@
       \State Using $\mlam_{bulk}^{(d)}$, apply Alg. (\ref{alg:pgreedy}), \pgreedy{}, with $\mathcal{A}_{\gmvp{}}$ to get symbol subset, $\mlam^{(d)}_{opt}$ and estimator val, $\epsilon^{(d)}_{opt}$
-      \If { $|\mlam^{(d)}_{opt}-\mlam^{(d-1)}_{opt}|<tol$ }
+      \If { $|\epsilon^{(d)}_{opt}-\epsilon^{(d-1)}_{opt}|<tol$ }
         \State \textbf{break}
@@
 %
-Worst, in cases where the underlying dataset is best described by a rational function, no polynomial order will yield satisfactory results (i.e.
+Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results (e.g.
 the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).
 %
-\par Of the simplest examples are rational functions of the form
+In general, the optimal polynomial basis may not be clear, and so a more general set of ansatzes may be of use.
+%
+\par Of the simplest of such ansatzes are rational functions of the form
 %
@@
 (\textit{center bottom}) {Percent residual error with respect to validation data (grey blocks) along with uniform (black) and gaussian (red) fits to error.
-The validation data were generated in the same manner as the training data.} (\textit{top right}) convergence of the L2 norm during iterative refinement.
+The validation data were generated in the same manner as the training data.} (\textit{top right}) convergence of the $L^2$ norm during iterative refinement.
 (\textit{bottom right}) Same as top right, but on log scale, where $\epsilon_0$ is the value of $\epsilon$ at the final $k^{\mathrm{th}}$ iteration of refinement.
@@
 %
-\par However, we note that $\hat{P}$ depends on $g$ signals.
+\par However, we note that $\hat{P}$'s depends on $g$.
 %
@@
 %
-The refinement process is to terminate when a measure of model error (e.g. $||g^{(0)}-g^{(n)}||$) passes a predetermined threshold.
+The refinement process is to terminate when a measure of model error (e.g. the $L^2$ norm $||g^{(0)}-g^{(n)}||$) passes a predetermined threshold.
 %
@@
     \State Calculate $\mu_k$ via \eqn{eq:linsol1}.
-    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the L-2 norm of $a$.
+    \State Calculate the model representation error, e.g.: $\epsilon = ||\hatU \vecmu - \vec{f}||/||\vec{f}||$, where $||a||$ is the $L^2$ norm of $a$.
     \vskip 10pt
@@
     \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
-    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$.
+    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$, where $var$ is the variance.
     \State $done = False$
@@
       \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
-      \State $done = \epsilon^{(n-1)}-\epsilon^{(n)} < tol$
+      \State $done = |\epsilon^{(n-1)}-\epsilon^{(n)}| < tol$
       \State (Implicitly, $n = n+1$)
@@
 %
-This is equally true in cases where $(\bar\ell,\bar{m}) \neq (\ell,m)$.
+Consistency with the Schwarzschild limit is equally true in cases where $(\bar\ell,\bar{m}) \neq (\ell,m)$.
 %
@@
     \vskip 10pt
-    \State Define, $\mlam_{bulk}$, the bulk symbol space using the tensor-product of the power set of each basis symbol. This is the combined bulk for numerator and denominator symbols.
+    \State Define, $\mlam_{bulk}$, the bulk symbol space, to be the set of all multinomial combinations of basis vectors up to a predefined maximum order.
+This is the combined symbol space for numerator and denominator symbols.
     \State Define $\mathcal{A}_{\gmvr{}}$ according to Alg. (\ref{alg:A_gmvr}).

### 2019-02-03 docs/mvfits_paper/mvf.tex
adding new ysprod model

@@
 One important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
-Here, we present new methods and models for the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
+Here, we present new phenomenological methods to model the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
 In particular, we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively.
@@
 GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$.
-We discuss the use of these models in current and future gravitational wave signal modeling.
+We discuss the potential use of these models in current and future gravitational wave signal modeling.
 	%
@@
 %
-These solutions allow \grad{} from generic perturbations to be well approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with the spin weight -2 spheroidal harmonics, $_{-2}S\lmn$.
+These solutions allow \grad{} from generic perturbations to be well approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with the spin $-2$ weighted -2 spheroidal harmonics, $_{-2}S\lmn$.
 %
@@
 %
-Note that barred indices, namely $\bar{\ell}$ and $\bar{m}$, will refer to \textit{spherical} harmonics, leaving the unbarred indices to refer to the spheroidals.
+Note that barred indices, namely $\bar{\ell}$ and $\bar{m}$, refer to \textit{spherical} harmonics of spin weight -2, leaving the unbarred indices to refer to the spheroidals.
 %
@@
 %
-It is therefore efficient to use accurate models for $\sigma\LMlmn$ which avoids convergence issues.
+It is therefore efficient to use accurate models for $\sigma\LMlmn$ to avoid convergence issues.
 These can then be used directly to calculate $h\LM$ via \eqn{hlm}, and thereby the \gw{} polarizations via \eqn{hrd}.
@@
 %
-This perspective reflects the empirical observation that the remnant spin of \bbh{} mergers smoothly connects regions of positive and negative spin \cite{Husa:2015iqa,London:2018gaq}.
+This perspective reflects the empirical observation that the remnant spin of \bbh{} mergers smoothly connects regions of positive and negative spin relative to the direction of the initial oribital angular momentum \cite{Husa:2015iqa,London:2018gaq}.
 %
@@
 %
-We go further by presenting models that also account for non-zero-damping in modes such as $(\ell,m,n)=(2,1,0)$ and $(3,2,0)$.
-%
-%
-\par For the modeling of $\sigma\LMlmn$, we note that the \cite{Berti:2014fga} do not appear to include the \qnm{s} which rotate counter to the \bh{} spin direction (i.e. ``mirror-modes'').
+The models presented here go further by applying outside of the nearly extremal Kerr regime while also accounting for non-zero-damping in modes such as $(\ell,m,n)=(2,1,0)$ and $(3,2,0)$\cite{Yang:2012pj}.
+%
+%
+\par For the modeling of $\sigma\LMlmn$, we note that the models of Ref.~\cite{Berti:2014fga} do not appear to include the \qnm{s} which rotate counter to the \bh{} spin direction (i.e.
+``mirror-modes'').
 %
@@
 %
-Results suggest that the versions of \gmvp{} and \gmvr{} presented here may have broad application in instances where training data are approximately noiseless, and an initial guess is difficult to obtain.
+Results suggest that the versions of \gmvp{} and \gmvr{} presented here may apply in instances where training data are approximately noiseless, and an initial guess is difficult to obtain.
 %
 Both algorithms are publicly available in \texttt{Python} via Ref. \cite{lionel_london_2018_1402516}.
+%
+While this paper's fits for the \qnm{} frequencies and mixing coefficients are presented in \eqns{eq:cw_fit_1}{eq:cw_fit_9} and \eqns{eq:ys22220}{eq:ys55550}  respectively, we encourage the reader to use the fits implemented in Ref.~\cite{lionel_london_2018_1402516}: \texttt{positive.physics.cw181003550} (\qnm{} frequencies) and in \texttt{positive.physics.ysprod181003550} (mixing coefficients).
 %

### 2019-02-03 positive/physics.py

@@ -1738,6 +1738,7 @@ def ysprod14081860(j,ll,mm,lmn):
 
 # Fit for spherica-sphoidal harmonic inner-product from Berti et al
 def ysprod14081860_from_paper_is_broken(j,L,M,lmn):
+
     '''
     Fits for sherical-spheroidal mixing coefficients from arxiv:1408.1860 -- Berti, Klein
 
@@ -1958,3 +1959,68 @@ def Berti0512160(jf,l,m,n):
         return array( [ lowlevel(j,m) for j in jf ] ).T[0]
     else:
         return lowlevel(jf,m)
+
+
+# Fits for spin-2 QNM frequencies from arxiv:1810.03550
+def cw181003550(jf,l,m,n):
+
+    '''
+    Fit for Kerr -2 QNMs from https://arxiv.org/abs/1810.03550
+    '''
+
+    # Import usefuls
+    from numpy import loadtxt,array,ndarray
+    from imp import load_source
+    import positive
+
+    # Load fit functions from reference module
+    module_path = positive.parent(positive.__path__[0])+'data/ksm2_cw.py'
+    cw_module = load_source( '', module_path )
+
+    # Extract dict of fit functions
+    fit_dictionary = cw_module.CW
+
+    if (l,m,n) in fit_dictionary:
+        #
+        ans = fit_dictionary[l,m,n](jf)
+    else:
+        #
+        error('this fit does not apply to (l,m,n)=(%i,%i,%i)'%(l,m,n))
+
+    #
+    return ans
+
+
+
+# Fits for spin-2 spherical-spheroidal mixing coefficients from arxiv:1810.03550
+def ysprod181003550(jf,ll,mm,lmn):
+
+    '''
+    Fit for Kerr -2 QNMs from https://arxiv.org/abs/1810.03550
+    '''
+
+    # Import usefuls
+    from numpy import loadtxt,array,ndarray
+    from imp import load_source
+    import positive
+
+    # Import ysprod models
+    data_path = positive.parent(positive.__path__[0])+'data/ysmodels.pickle'
+    with open(data_path,'rb') as f:
+        ysfits = pickle.load(f)
+
+    # Extract dict of fit functions
+    fit_dictionary = ysfits
+
+    # Extract kerr indices
+    l,m,n = lmn
+
+    # Eval fit
+    if (ll,mm,l,m,n) in fit_dictionary:
+        #
[…]

### 2019-02-03 docs/mvfits_paper/mvf.tex
about to resub mvrfits

@@
 %
-\par This truncated expansion happens to be a polynomial in at most $N$ variables.
+\par \eqn{eq:mvt}'s truncated expansion happens to be a polynomial in at most $N$ variables.
 %
@@
 Fits of dimensionless \qnm{} decay rates (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
-(Bottom) Percentage residual errors for fits of dimensionless \qnm{} central frequencies and decay times (solid lines) along with select numerical values (grey markers) computed using Leaver's method \cite{Leaver85}.
+(Bottom) Percentage absolute residual errors for fits of dimensionless \qnm{} frequencies,, $\cw\lmn$ along with select numerical values (colored markers) computed using Leaver's method \cite{Leaver85}.
+For comparison, residuals using the models in Ref.~\cite{Berti:2005ys} are shown in gray.
 }
@@
 %
-\par Despite the apparent universality of of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a multinomial.
-%
-Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results (e.g.
+\par Despite the apparent universality of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a low order multinomial.
+%
+Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results in low order (e.g.
 the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).
@@
 %
-\par However, we note that $\hat{P}$'s depends on $g$.
+\par However, we note that $\hat{P}$ depends nontrivially on $g$, and is therefore susceptible to noise in the training data.
 %
@@
 %
-\par With the conceptual tools in hand, we may proceed to constructing \gmvr{} by first defining its action, $\mathcal{A}_{\gmvr}$.
+\par With these conceptual tools in hand, we may proceed to constructing \gmvr{} by first defining its action, $\mathcal{A}_{\gmvr}$.
 %
@@
 %
-\par Lastly, \fig{fig:qnm}'s bottom two panels show absolute fractional residual errors of the complex frequency, $\cw\lmn = \omega\lmn + i/\tau\lmn$.
+\par \fig{fig:qnm}'s bottom two panels show absolute fractional residual errors of the complex frequency, $\cw\lmn = \omega\lmn + i/\tau\lmn$.
 %
@@
 %
-For comparison, the same residual errors are shown in gray for the model presented in Ref.~\cite{Berti:2005ys}.
+For comparison, the same residual errors are shown in gray for the model presented in Ref.~\cite{Berti:2005ys};
+%
+here, the sharp feature near $\jf=0$ results from their modeling counter and co-rotating \qnm{} as two different curves.
 %
@@
 %
+A \texttt{Python} implementation of \eqns{eq:cw_fit_1}{eq:cw_fit_9} is available in Ref.~\cite{lionel_london_2018_1402516} via \texttt{positive.physics.cw181003550}.
+%
 %
@@
 \eqns{eq:ys22220}{eq:ys55550} present the resulting model equations.
+%
+A \texttt{Python} implementation of \eqns{eq:ys22220}{eq:ys55550} is available in Ref.~\cite{lionel_london_2018_1402516} via \texttt{positive.physics.ysprod181003550}.
 %
@@
 %
-As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values.
-%
-For comparison, fractional residual error for models in Ref.~\cite{Berti:2014fga} are also shown.
+As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values, and largely result from the model asatz.
+%
+For comparison, fractional residual errors for models in Ref.~\cite{Berti:2014fga} are also shown.
 %
@@
 %
+%
+\par Both \gmvp{} and \gmvr{} may be used to automatically determine the functional form and model for a given dataset that is expected to be respectively polynomial or rational.
+%
+An alternative use-strategy is to use either \gmvp{} or \gmvr{} to determine a fitting ansatz for individual cases (e.g.
+individual \qnm{s}), and then use these results to develop a single ansatz for all cases.
+%
+This is what as been done for the modeling of \qnm{} frequencies and spherical-spheroidal mixing coefficients.
+%
+%
+\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature.
+%
+The fits presented here are of direct use in Ref.
+\cite{London:2017bcn}, where efficiently evaluable \qnm{} frequencies are required to generate template waveforms for \gw{} searches and parameter estimation.
+%
+The fits presented may find future use in Phenom or EOB based \gw{} models.
+%
+\par \gmvr{} has been applied to the modeling of mixing coefficients between the spherical and spheroidal harmonics.
 %
@@
 %
-\par Both \gmvp{} and \gmvr{} may be used to automatically determine the functional form and model for a given dataset that is expected to be respectively polynomial or rational.
-%
-An alternative use strategy is to use either \gmvp{} or \gmvr{} to determine a fitting ansatz for individual cases (e.g.
-individual \qnm{s}), and then use these results to develop a single ansatz for all cases.
-%
-This is what as been done for the modeling of \qnm{} frequencies and spherical-spheroidal mixing coefficients.
-%
-%
-\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit.
-%
-The fits presented are of direct use in Ref.
-\cite{London:2017bcn}, where efficiently evaluable \qnm{} frequencies are required to generate template waveforms for \gw{} searches and parameter estimation.
-%
-The fits presented may find future use in Phenom or EOB based \gw{} models.
-%
-\par \gmvr{} has been applied to the modeling of mixing coefficients between the spherical and spheroidal harmonics.
-%
 These fits are of direct use in Ref. \cite{Carullo:2018sfu}, and may be of future use in similar ringdown-only models for the purpose of testing \gr{}.

### 2019-02-04 docs/mvfits_paper/referee_reports_and_responses/Response_Ref1.txt
Add minor changes to tex and res txt for response

@@
 (p.
-1, L17-17) The referee makes a valid, though largely semantic point regarding the use of interpolating in the abstract as it related to GMVR and Runge's phenomenon.
+1, L16-17) The referee makes a valid, though largely semantic point regarding the use of interpolating in the abstract as it related to GMVR and Runge's phenomenon.
 We kindly note that GMVR is an iterative regression method that works for equally spaced grids, and constructs rational functions (equivalently, sums of rational functions) that smoothly connect or interpolate data assuming a rational ansatz.
@@
 We do not wish to reference this theorem in place of the series expansion as the latter is more accessible to a physics audience.
-We note that our introduction to the discussion is generally applicable given some smooth functoin and an epsilon neighborhood around a point.
-We intend primarily to motivate a general numtinobial basis perspective of our algorithms from first principles.
+We note that our introduction to the discussion is generally applicable given some smooth function and an epsilon neighbourhood around a point.
+We intend primarily to motivate a general multinomial basis perspective of our algorithms from first principles.
 he text has been modified in an effort to clarify this intention.
@@
 
-16. (p. 3, L60) The current description of \lambda_{bulk} seeks to communicate the presense of the constant term.
+16. (p. 3, L60) The current description of \lambda_{bulk} seeks to communicate the presence of the constant term.
 
-17. (p. 5, L3-4) We refer the reviewer to the introducion section here: https://en.wikipedia.org/wiki/Runge%27s_phenomenon. We have sought to clarify the text to minimize confusion.
+17. (p. 5, L3-4) We refer the reviewer to the introduction section here: https://en.wikipedia.org/wiki/Runge%27s_phenomenon. We have sought to clarify the text to minimise confusion.
 
@@
 
-19. Via Eq. 15, n>=1 for alpha. Here, "implicitely" n plays no real role in the algorithm and therefore need not be stored and increamented.
+19. (Alg. 3, step 3) The algorithm as stated applies to multiple definitions of the representation error. We now accentuate this point by citing the L2 norm as a possible choice.
 
-20. (Alg. 4, step 4) Thank you. We have defined var to be the variance.
+20. (Alg. 4, step 2) Via Eq. 15, n>=1 for alpha. Here, "implicitly" n plays no real role in the algorithm and therefore need not be stored and incremented.
 
-21. (Alg. 4, step 4) Thank you. Yes.
+21. (Alg. 4, step 4) Thank you. We have defined var to be the variance.
 
-22. (p. 8, final line) We have clarified the text.
+22. (Alg. 4, step 10) Thank you. Yes.
 
-23. (Fig. 4) We have clarified the text.
+23. (p. 8, final line) We have clarified the text.
 
-24. Code: While we are appreciative of the referee's comments, we point out to the submitted draft only pertains to the GMVP and GMVR algorithms.
+24. (Fig. 4) We have clarified the text.
+
+25. Code: While we are appreciative of the referee's comments, we point out to the submitted draft only pertains to the GMVP and GMVR algorithms.

### 2019-02-04 docs/mvfits_paper/mvf.tex
Add minor changes to tex and res txt for response

@@
 %
-This perspective reflects the empirical observation that the remnant spin of \bbh{} mergers smoothly connects regions of positive and negative spin relative to the direction of the initial oribital angular momentum \cite{Husa:2015iqa,London:2018gaq}.
+This perspective reflects the empirical observation that the remnant spin of \bbh{} mergers smoothly connects regions of positive and negative spin relative to the direction of the initial orbital angular momentum \cite{Husa:2015iqa,London:2018gaq}.
 %
@@
 %
-As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values, and largely result from the model asatz.
+As with the \qnm{} frequencies, residuals are dominated by small scale oscillations with amplitudes that are fractions of a percent of the central values, and largely result from the model ansatz.
 %

### 2019-02-07 docs/mvfits_paper/referee_reports_and_responses/Response_Ref1.txt
now avoiding Runges problem all together to hopefully speed thigs up!

--- 2019-02-03 docs/mvfits_paper/referee_reports_and_responses/Response_Ref1.txt
@@
 1, L17-17) The referee makes a valid, though largely semantic point regarding the use of interpolating in the abstract as it related to GMVR and Runge's phenomenon.
-We kindly note that GMVR is an iterative regression method that works for equally spaced grids, and constructs rational functions (equivalently, sums of rational functions) that smoothly connect or interpolate data assuming a rational ansatz.
+However, to avoid any confusion, we have removed discussion of Runge's problem from the text.
 
@@
 
-17. (p. 5, L3-4) We refer the reviewer to the introducion section here: https://en.wikipedia.org/wiki/Runge%27s_phenomenon. We have sought to clarify the text to minimize confusion.
+17. (p. 5, L3-4) We have sought to clarify the text to minimize confusion.
 

### 2019-02-07 docs/mvfits_paper/mvf.tex
now avoiding Runges problem all together to hopefully speed thigs up!

--- 2019-02-03 docs/mvfits_paper/mvf.tex
@@
 In particular, we present a greedy-multivariate-polynomial (GMVP) regression method and greedy-multivariate-rational (GMVR) regression method for the automated modeling of polynomial and rational functions respectively.
-GMVR is a quasi-linear numerical method for interpolating rational functions.
-It therefore represents a solution to Runge's phenomenon.
-GMVP is used to develop the first model for QNM frequencies explicitly enforces consistency with the extremal Kerr limit.
+GMVP is used to develop a model for QNM frequencies that explicitly enforces consistency with the extremal Kerr limit.
 GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$.
+Both models are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes.
 We discuss the potential use of these models in current and future gravitational wave signal modeling.
@@
 %
-Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results in low order (e.g.
-the well known ``Runge's phenomenon'' \cite{10.2307/2323093}).
+Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results in low order.
 %
@@
 %
-Nevertheless, the \gmvr{} toy problem demonstrates \gmvr{}'s ability to handle moderately noisy training data, suggesting current applicability to a variety of problems where polynomial interpolation is insufficient.
+Nevertheless, the \gmvr{} toy problem demonstrates \gmvr{}'s ability to handle moderately noisy training data, suggesting current applicability to a variety of problems where polynomial regression is insufficient.
 %

### 2019-03-25 positive/physics.py
Remove unused GPL-2.0 code to permit MIT

@@ -3,77 +3,6 @@ from positive import *
 from positive.plotting import *
 from positive.learning import *
 
-#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#
-# Here are some phenomenological fits used in PhenomD                               #
-#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#%%#
-
-
-# Formula to predict the final spin. Equation 3.6 arXiv:1508.07250
-# s is defined around Equation 3.6.
-''' Copied from LALSimulation Version '''
-def FinalSpin0815_s(eta,s):
-    eta = round(eta,8)
-    eta2 = eta*eta
-    eta3 = eta2*eta
-    eta4 = eta3*eta
-    s2 = s*s
-    s3 = s2*s
-    s4 = s3*s
-    return 3.4641016151377544*eta - 4.399247300629289*eta2 +\
-    9.397292189321194*eta3 - 13.180949901606242*eta4 +\
-    (1 - 0.0850917821418767*eta - 5.837029316602263*eta2)*s +\
-    (0.1014665242971878*eta - 2.0967746996832157*eta2)*s2 +\
-    (-1.3546806617824356*eta + 4.108962025369336*eta2)*s3 +\
-    (-0.8676969352555539*eta + 2.064046835273906*eta2)*s4
-
-
-#Wrapper function for FinalSpin0815_s.
-''' Copied from LALSimulation Version '''
-def FinalSpin0815(eta,chi1,chi2):
-    from numpy import sqrt
-    eta = round(eta,8)
-    if eta>0.25:
-        error('symmetric mass ratio greater than 0.25 input')
-    # Convention m1 >= m2
-    Seta = sqrt(abs(1.0 - 4.0*float(eta)))
-    m1 = 0.5 * (1.0 + Seta)
-    m2 = 0.5 * (1.0 - Seta)
-    m1s = m1*m1
-    m2s = m2*m2
-    # s defined around Equation 3.6 arXiv:1508.07250
-    s = (m1s * chi1 + m2s * chi2)
-    return FinalSpin0815_s(eta, s)
-
-
-# Formula to predict the total radiated energy. Equation 3.7 and 3.8 arXiv:1508.07250
[…]

### 2019-03-26 positive/maths.py
Update code to be Python3 compatible

@@ -90,7 +90,7 @@ class smooth:
 
         #
         err,smo = [],[]
-        width_range = array(range(5,min(50,int(len(this.scalar_range)/2))))
+        width_range = array(list(range(5,min(50,int(len(this.scalar_range)/2)))))
         # print lim(width_range)
 
         if method=='savgol':

### 2019-03-26 positive/physics.py
Make ysprod181003550 fits explicit as lambdas
Dependancy on a pickle file does not work well accorss Python versions.
Instread explicit lambda function representations of the fits for
ysprod181003550 replace the fits loaded from the pickle dump. This is
similar to how cw181003550 is implemented.

With 16 digiits of decimal place accuracy (allowing for scientific
notation) the evaluated fit with explicit lambdas agrees with the pickle
dump implementation to greated than 10 significant figures.

@@ -667,7 +667,7 @@ def pn_com_energy_flux(f,m1,m2,X1,X2,L=None):
     '''
 
     # Import usefuls
-    from numpy import pi,pow,array,dot,ndarray
+    from numpy import pi,pow,array,dot,ndarray,log
 
     #~-~-~-~-~-~-~-~-~-~-~-~-~-~-~-~-~-~-~-~-~-#
     # Validate inputs
@@ -1932,17 +1932,25 @@ def ysprod181003550(jf,ll,mm,lmn):
     '''
 
     # Import usefuls
-    from numpy import loadtxt,array,ndarray
+    from numpy import loadtxt,array,ndarray,log,exp
     from imp import load_source
     import positive
 
-    # Import ysprod models
-    data_path = positive.parent(positive.__path__[0])+'data/ysmodels.pickle'
-    with open(data_path,'rb') as f:
-        ysfits = pickle.load(f)
-
     # Extract dict of fit functions
-    fit_dictionary = ysfits
+    fit_dictionary = {
+        (2, 1, 2, 1, 0): lambda x0: 0.9971577101354098*exp(6.2815088293225569j)  +  6.3541921214411894e-03 * (  143454.0616281430993695*exp(4.5060813273501665j)*(x0) + 354688.4750832330319099*exp(1.7326693927013841j)*(x0*x0) + 240378.2854125543963164*exp(5.1629102848140072j)*(x0*x0*x0) + 6026.9252628974973049*exp(1.8880583980908965j) ) / ( 1.0 +  73780.2159267508977791*exp(1.4129254015451644j)*(x0) + 97493.6172260692255804*exp(4.5395814919256727j)*(x0*x0) + 34814.9777696923483745*exp(1.4206733963391489j)*(x0*x0*x0) ),
[…]

### 2019-03-26 positive/physics.py
Add docstrs for cw181003550 and ysprod181003550

@@ -1895,10 +1895,49 @@ def Berti0512160(jf,l,m,n):
 
 # Fits for spin-2 QNM frequencies from arxiv:1810.03550
 def cw181003550(jf,l,m,n):
+    """Fit for quasi-normal mode frequencies
 
-    '''
-    Fit for Kerr -2 QNMs from https://arxiv.org/abs/1810.03550
-    '''
+    Fit for the quasi-normal mode frequencies from
+    https://arxiv.org/abs/1810.03550 for Kerr under -2 spin-weighted spheroidal
+    harmonics. Fits are provided for the following indices
+
+    |  l  |  m  |  n  |
+    | --- | --- | --- |
+    |  2  |  2  |  0  |
+    |  2  | -2  |  0  |
+    |  2  |  2  |  1  |
+    |  2  | -2  |  1  |
+    |  3  |  2  |  0  |
+    |  3  | -2  |  0  |
+    |  4  |  4  |  0  |
+    |  4  | -4  |  0  |
+    |  2  |  1  |  0  |
+    |  2  | -1  |  0  |
+    |  3  |  3  |  0  |
+    |  3  | -3  |  0  |
+    |  3  |  3  |  1  |
+    |  3  | -3  |  1  |
+    |  4  |  3  |  0  |
+    |  4  | -3  |  0  |
+    |  5  |  5  |  0  |
+    |  5  | -5  |  0  |
+
+    Parameters
+    ----------
+    jf: float
+         Dimensionless final spin
+    l: int
+        Polar index
+    m: int
+        Azimuthal index
+    n: int
+        Overtone index
+
+    Returns
+    -------
+    float
+        Evaluation of the fit at `jf` for the requested Kerr -2 QNM
+    """
 
     # Import usefuls
     from numpy import loadtxt,array,ndarray
@@ -1926,10 +1965,43 @@ def cw181003550(jf,l,m,n):
 
 # Fits for spin-2 spherical-spheroidal mixing coefficients from arxiv:1810.03550
 def ysprod181003550(jf,ll,mm,lmn):
+    """Fit for spherical-spheroidal mixing coefficients
 
-    '''
-    Fit for Kerr -2 QNMs from https://arxiv.org/abs/1810.03550
-    '''
+    Fit for the spherical-spheroidal mixing coefficients from
+    https://arxiv.org/abs/1810.03550 for Kerr under -2 spin-weighted harmonics.
[…]

### 2019-03-26 positive/physics.py
Move required data under package

@@ -1576,7 +1576,7 @@ def leaver( jf,                     # Dimensionless BH Spin
         p = sign(jf) + int( jf==0 )
     # NOTE that the norm of the spin input will be used to interpolate the data as the numerical data was mapped according to jf>=0
     # Given l,m,n,sign(jf) create a RELATIVE file string from which to load the data
-    cmd = parent(  parent(os.path.realpath(__file__))  )
+    cmd = parent(os.path.realpath(__file__))
     #********************************************************************************#
     m_label = 'm%i'%abs(m) if (p>=0) or (abs(m)==0) else 'mm%i'%abs(m)
     #********************************************************************************#
@@ -1645,7 +1645,7 @@ def ysprod14081860(j,ll,mm,lmn):
 
     LondonL@mit.edu 2019
     '''
-    tbl = loadtxt(parent(positive.__path__[0])+'/data/berti_swsh_fits.dat')
+    tbl = loadtxt(parent(os.path.realpath(__file__))+'/data/berti_swsh_fits.dat')
 
     def lowlevel(J,__mm__):
         MM,LL,L,N,P1,P2,P3,P4,Q1,Q2,Q3,Q4,_,_,_,_ = tbl.T
@@ -1854,7 +1854,7 @@ def Berti0512160(jf,l,m,n):
     import positive
 
     # Load fit coefficients
-    data_path = positive.parent(positive.__path__[0])+'data/berti_kerrcw_fitcoeffsWEB.dat'
+    data_path = parent(os.path.realpath(__file__))+'/data/berti_kerrcw_fitcoeffsWEB.dat'
     data = loadtxt(data_path)
 
     # Unpack: l,m,n,f1,f2,f3,q1,q2,q3
@@ -1945,7 +1945,7 @@ def cw181003550(jf,l,m,n):
     import positive
 
     # Load fit functions from reference module
-    module_path = positive.parent(positive.__path__[0])+'data/ksm2_cw.py'
+    module_path = parent(os.path.realpath(__file__))+'/data/ksm2_cw.py'
     cw_module = load_source( '', module_path )
 
     # Extract dict of fit functions

### 2019-03-27 positive/maths.py
Adding reference to scipys factorial funciton

@@ -1,6 +1,9 @@
 #
 from positive import *
 
+# Reference factorial from scipy
+from scipy.misc import factorial
+
 # Smooth 1D data
 class smooth:
     '''

### 2019-03-27 positive/plotting.py
explicitely importing custom unwrap function to surdace plotting in splot()

@@ -141,6 +141,7 @@ def splot( domain,
     # Import usefult things
     from matplotlib.pyplot import figure,plot,scatter,xlabel,ylabel,savefig,imshow,colorbar,gca
     from numpy import linspace,meshgrid,array,angle,unwrap
+    from positive.maths import sunwrap
     from matplotlib import cm
 
     #

### 2019-03-27 docs/mvfits_arxiv/mvf.tex
Adding source tex files for mvfits doc arxiv version

--- 2019-02-03 docs/mvfits_paper/mvf.tex
@@
 It therefore represents a solution to Runge's phenomenon.
-GMVP is used to develop the first model for QNM frequencies explicitly enforces consistency with the extremal Kerr limit.
+GMVP is used to develop a model for QNM frequencies that explicitly enforces consistency with the extremal Kerr limit.
 GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$.
+Both models are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes.
 We discuss the potential use of these models in current and future gravitational wave signal modeling.

### 2019-03-28 docs/mvfits_paper/mvf.tex
Correct SH degree claim in abstract [1]
Add wf efficiency cite + accuracy requirment [2]

@@
 GMVP is used to develop a model for QNM frequencies that explicitly enforces consistency with the extremal Kerr limit.
-GMVR is used to develop a model for harmonic mixing coefficients that extends previous results to dominant multipoles with $\ell \le 5$.
+GMVR is used to develop a model for harmonic mixing coefficients for the dominant multipoles with $\ell \le 5$.
 Both models are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes.
@@
 %
-As the merger of isolated \bh{s} is expected to result in a perturbed Kerr \bh{}, there is related interest in having computationally efficient models for perturbative parameters, namely those that enable evaluation of the related \rd{} radiation \cite{Berti:2005ys}.
+As the merger of isolated \bh{s} is expected to result in a perturbed Kerr \bh{}, there is related interest in having accurate and computationally efficient models for perturbative parameters, namely those that enable evaluation of the related \rd{} radiation \cite{Berti:2005ys,TheLIGOScientific:2016wfe}.
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Weaken Kerr pertubation approximation statment [3]

@@
 %
-These solutions allow \grad{} from generic perturbations to be well approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with the spin $-2$ weighted -2 spheroidal harmonics, $_{-2}S\lmn$.
+Following the usual treatment, these solutions allow \grad{} from a perturbed Kerr BH at sufficiently late times to be approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with spheroidal harmonics, $_{-2}S\lmn$, of spin weight -2.
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Add suggested EOB ringdown reference [4]
Correct spelling of orbital

@@
 In the \eob{} formalism, $h\LM$ is modeled such that, after its peak (near merger), the effective functional form reduces (asymptotically) to \eqn{hrd}'s second line \cite{Cotesta:2018fcv, Buonanno:2000ef,
-Bohe:2016gbl,Pan:2013rra, Bohe:2016gbl, Nagar:2018zoe}.
+Bohe:2016gbl,Pan:2013rra, Bohe:2016gbl, Nagar:2018zoe,Babak:2016tgq}.
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Fix K -> K+1 lin. indi. basis function in Methods

@@
 %
-\par If we consider a scalar function, $f$, of $N$ variables sampled in $j$, $\vec{x}_j = \{x_{\alpha j}\}_{\alpha=0}^{N}$, then $f(\vec{x}_j)$ can be represented (possibly inaccurately) as a sum over $K$ linearly independent basis functions, $\phi_k(\vec{x}_j)$:
+\par If we consider a scalar function, $f$, of $N$ variables sampled in $j$, $\vec{x}_j = \{x_{\alpha j}\}_{\alpha=0}^{N}$, then $f(\vec{x}_j)$ can be represented (possibly inaccurately) as a sum over $K+1$ linearly independent basis functions, $\phi_k(\vec{x}_j)$:
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Reword symbol space and lambda_bulk defs [5,6]
Add note for kappa mapping orientation change [7]

@@
 %
-Each term is an element of the tensor-product of the power-sets of each model dimension. That is $\mlam_{bulk} = \{x_0,x_1 .. x_N, ... x_0^1, x_0^2, x_0^3, ...  , (x_0^K x_1^K ... x_N^K) \}$.
+Each term is an element of the tensor-product of the sets of powers of each coordinate of a chosen representation of the models domain.
+That is $\mlam_{bulk} = \{x_0^{d_0} x_1^{d_1} \ldots x_N^{d_N} \mid d_i \in \{0,\ldots,K\}, i \in \{0,\ldots,N\}\}$.
 %
@@
 appropriately linearizes the sharp behavior of each frequency near $\jf=1$ while also mapping $-1 \le \jf \le 1$ onto $0 \le \kappa \le 1$.
+Note that under the mapping $j_f \mapsto \kappa$ the orientation is reversed such that as $j_f \rightarrow 1$ from below $\kappa \rightarrow 0$ from above.
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Fix Eq.(20,21) indexing and up claimed order [8]

@@
   \label{eq:zd}
-  \cw_{\lmn} = m/2 + \kappa \sum_{j=1}^{J} c_j \kappa^k \; .
+  \cw_{\lmn} = m/2 + \kappa \sum_{j=0}^{J} c_j \kappa^j \; .
 \end{align}
@@
   \label{eq:nzd}
-  \cw_{\lmn} = \sum_{j=0}^{J} c_j \kappa^k \; .
+  \cw_{\lmn} = \sum_{u=0}^{U} c_u \kappa^u \; .
 \end{align}
@@
 %
-In particular, the domain map allows most \qnm{} frequencies to be well modeled by 4th order polynomials which include all lower degree terms; concurrently, the real and imaginary parts of each $\cw\lmn$ are modeled simultaneously.
+In particular, the domain map allows most \qnm{} frequencies to be well modeled by 5th order polynomials which include all lower degree terms; concurrently, the real and imaginary parts of each $\cw\lmn$ are modeled simultaneously.
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Fix reference for QNM j_f +/- branches [9]

@@
 %
-In particular, it is shown that the two branches (namely $\jf>0$ and $\jf<0$) naturally form a single family of solutions when accounting for the sign of the \bh{}'s oriented spin \cite{Husa:2007hp}.
+In particular, it is shown that the two branches (namely $\jf>0$ and $\jf<0$) naturally form a single family of solutions when accounting for the sign of the \bh{}'s oriented spin \cite{Husa:2015iqa}.
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Make sample index explicit in later GMVR

@@
 %
-where, $\hat{P}$ is the pseudo-inverse of the matrix whose elements are $\psi_k(\vec{x}_j)$, $\vec\alpha = ( z_0, z_1, ... z_{R+V-1},z_{R+V} )$, and $\vec{g} = ( g_0, g_1, ... g_{R+V-1},g_{R+V} )$.
+where, $\hat{P}$ is the pseudo-inverse of the matrix whose elements are $\psi_k(\vec{x}_j)$, $\vec\alpha = ( z_0, z_1, ... z_{R+V-1},z_{R+V} )$, and $\vec{g} = ( g_j )$.
 %
@@
 %
-In practice, one solves \eqn{eq:pinv3} for $\vec{\alpha}^{(n+1)}$, and then uses the related $a_r^{(n+1)}$ and $b_v^{(n+1)}$ to calculate $g^{(n+1)}$ via
+In practice, one solves \eqn{eq:pinv3} for $\vec{\alpha}^{(n+1)}$, and then uses the related $a_r^{(n+1)}$ and $b_v^{(n+1)}$ to calculate $g_j^{(n+1)}$ via
 %
@@
   \label{eq:rat4}
-  g^{(n+1)} =  \frac{ \sum_{r=0}^{R} a^{(n+1)}_r \, \phi_{r}(\vec{x}) }{ 1\;-\;  \sum_{v=1}^{V} b^{(n+1)}_v \, \phi_{v}(\vec{x}) } \; .
-\end{align}
-%
-Subsequently, $g^{(n+1)}$ is then fed back into \eqn{eq:pinv3} for further refinement.
+  g_j^{(n+1)} =  \frac{ \sum_{r=0}^{R} a^{(n+1)}_r \, \phi_{r}(\vec{x_j}) }{ 1\;-\;  \sum_{v=1}^{V} b^{(n+1)}_v \, \phi_{v}(\vec{x_j}) } \; .
+\end{align}
+%
+Subsequently, $g_j^{(n+1)}$ is then fed back into \eqn{eq:pinv3} for further refinement.
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Refactor indexing in Alg. 4 psudocode [10]

@@
     \vskip 10pt
-    \State Calculate $\alpha^{(1)}_k$ via \eqn{eq:pinv3}. Implicitly, $n=1$.
-    \State Calculate the current model prediction $g^{(1)}$ via \eqn{eq:rat4}.
-    \State Calculate the model representation error, e.g.: $\epsilon^{(1)}  = ||var(g^{(n)} - g^{(0)})||/||g^{(0)}||$, where $var$ is the variance.
-    \State $done = False$
+    \State \textbf{Let} $n=0$
+    \State Calculate $\vec{\alpha}^{(1)}$ via \eqn{eq:pinv3}.
+    \State Calculate the model prediction $\vec{g}^{(1)}$ via \eqn{eq:rat4}.
+    \State Calculate the model representation error $\epsilon^{(1)}$.
+    \State \textbf{Let} $done = False$
     \While { not $done$ }
-      \State Calculate $\alpha^{n+1}_{k}$  via \eqn{eq:pinv3}.
-      \State Calculate the current model prediction $g^{(n)}$ via \eqn{eq:rat4}.
-      \State Calculate the model representation error, e.g. $\epsilon^{(n)} = ||g^{(n)} - g^{(0)}||/||g^{(0)}||$.
-      \State $done = |\epsilon^{(n-1)}-\epsilon^{(n)}| < tol$
-      \State (Implicitly, $n = n+1$)
+      \State $n=n+1$
+      \State Calculate $\vec{\alpha}^{(n+1)}$  via \eqn{eq:pinv3}.
+      \State Calculate the model prediction $\vec{g}^{(n+1)}$ via \eqn{eq:rat4}.
+      \State Calculate the model representation error $\epsilon^{(n+1)}$.
+      \State $done = |\epsilon^{(n)}-\epsilon^{(n+1)}| < tol$
     \EndWhile

### 2019-03-28 docs/mvfits_paper/mvf.tex
Def choice of model rep err used for positive [11]
Define r distance to source [30]

@@
 %
-\par In the first and second lines of \eqn{hrd}, we relate the observable \gw{} polarizations, $h_+$ and $h_\times$, to the analytically understood morphology of the time domain \rd{} waveform.
+\par In the first and second lines of \eqn{hrd}, we relate the observable \gw{} polarizations, $h_+$ and $h_\times$, to the analytically understood morphology of the time domain \rd{} waveform where $r$ is the distance from the source.
 %
@@
 %
-The refinement process is to terminate when a measure of model error (e.g. the $L^2$ norm $||g^{(0)}-g^{(n)}||$) passes a predetermined threshold.
-%
-%
+The refinement process is to terminate when a measure of model error (e.g.
+the $L^2$ norm $||\vec{g}^{(0)}-\vec{g}^{(n)}||$) passes a predetermined threshold.
+For \cite{lionel_london_2018_1402516} the following model representation error was used
+%
+\begin{align}
+  \label{eq:raterr}
+  \epsilon^{(n)}  = \left|\frac{\operatorname{Var}\left(\vec{g}^{(n)} - \vec{g}^{(0)}\right)}{\operatorname{Var}\left(\vec{g}^{(0)}\right)}\right|
+\end{align}
+%
+where $\operatorname{Var}$ is the variance defined as
+%
+\begin{align}
+  \label{eq:ratvar}
+  \operatorname{Var}\left(\vec{a}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(g_j - \frac{1}{J}\sum_{u=0}^{J}g_j\right)^2
+\end{align}
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Fully define geometric units [31]

@@
 %
-Here, the labels $\ell$ and $m$ are polar and azimuthal eigenvalues of \tk{'s} angular equations, where total mass and the speed of light are set to unity (i.e. $M=c=1$).
+Here, the labels $\ell$ and $m$ are polar and azimuthal eigenvalues of \tk{'s} angular equations, where total mass, the speed of light and the gravitational constant are set to unity (i.e. $M=c=G=1$).
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Reorder spin weight qualification [32]

@@
 %
-This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where ${_{-2}}Y_{\ell m}$ are the spins weighted -2 spherical harmonics.
+This view currently comes with the added assumption that ${_{-2}}S_{\ell m n} = {_{-2}}Y_{\ell m}$, where ${_{-2}}Y_{\ell m}$ are the spherical harmonics of spin weight -2.
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Mv 150914PE cite before extreme spin statment [33]

@@
 %
-In the context of \gw{} \da{}, where source parameters are estimated using routines which sample over the space of all possible \bh{} masses and spins, it is useful to have accurate physical behavior in the extremal limit \cite{TheLIGOScientific:2016wfe}.
+In the context of \gw{} \da{}, where source parameters are estimated using routines which sample over the space of all possible \bh{} masses and spins \cite{TheLIGOScientific:2016wfe}, it is useful to have accurate physical behavior in the extremal limit.
 %

### 2019-03-28 docs/mvfits_paper/mvf.tex
Fix claim of variable count from N to N+1 [34]

@@
 %
-\par If we consider a scalar function, $f$, of $N$ variables sampled in $j$, $\vec{x}_j = \{x_{\alpha j}\}_{\alpha=0}^{N}$, then $f(\vec{x}_j)$ can be represented (possibly inaccurately) as a sum over $K+1$ linearly independent basis functions, $\phi_k(\vec{x}_j)$:
+\par If we consider a scalar function, $f$, of $N+1$ variables sampled in $j$, $\vec{x}_j = \{x_{\alpha j}\}_{\alpha=0}^{N}$, then $f(\vec{x}_j)$ can be represented (possibly inaccurately) as a sum over $K+1$ linearly independent basis functions, $\phi_k(\vec{x}_j)$:
 %

### 2019-03-31 docs/mvfits_paper/mvf.tex
Fix set notation in Alg. 1 [35]
Fix indexing for Var definition [11]
Updating affiliations and addin jupyter notebooks for plots creation.
Up abstract to clarify first of kind claim [15]

@@
 \author{L. London}
+\affiliation{MIT-Kavli Institute for Astrophysics and Space Research and LIGO Laboratory, 77 Massachusetts Avenue, 37-664H, Cambridge, MA 02139, USA}
 \affiliation{\Cardiff}
@@
 GMVR is used to develop a model for harmonic mixing coefficients for the dominant multipoles with $\ell \le 5$.
-Both models are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes.
+The models for the mixing coefficients and $(l,m)\neq(2,2)$ QNM frequencies are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes.
 We discuss the potential use of these models in current and future gravitational wave signal modeling.
@@
       \For { $\mlam$ in $\mlam^{bulk}$ }
-        \State $\mlam_{trial} = \mlam_{kept} \cup \mlam$ {\hskip0.525in} (add $\mlam$ to $\mlam_{kept}$)
+        \State $\mlam_{trial} = \mlam_{kept} \cup \{\mlam\}$ {\hskip0.525in} (add $\mlam$ to $\mlam_{kept}$)
         \State $\epsilon = \mathcal{A}(\mlam_{trial})$ {\hskip0.70in} (action returns fit error)
@@
     \vskip 10pt
-    \State {\bf Output:} $\{ \mlam_{kept} \}$ (the Greedy Basis)
+    \State {\bf Output:} $\mlam_{kept}$ (the Greedy Basis)
     %
@@
 %
-where $\operatorname{Var}$ is the variance defined as
+where $\operatorname{Var}$ is the variance defined for a vector $\vec{d} = (d_j)$ as
 %
@@
   \label{eq:ratvar}
-  \operatorname{Var}\left(\vec{a}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(g_j - \frac{1}{J}\sum_{u=0}^{J}g_j\right)^2
+  \operatorname{Var}\left(\vec{a}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(d_j - \frac{1}{J}\sum_{u=0}^{J}d_u\right)^2
 \end{align}
@@
 For comparison, residual errors for the fits in Ref.~\cite{Berti:2014fga} are also shown over their region of validity in \bh{} spin.
-Note that makers match between grey and colored data points.
+Note that markers match between grey and colored data points.
 }

### 2019-03-31 docs/mvfits_paper/mvf.tex
Up to describe w220 comp with Nagar et al. [15]

@@
 (Bottom) Percentage absolute residual errors for fits of dimensionless \qnm{} frequencies,, $\cw\lmn$ along with select numerical values (colored markers) computed using Leaver's method \cite{Leaver85}.
-For comparison, residuals using the models in Ref.~\cite{Berti:2005ys} are shown in gray.
-}
+For comparison, residuals using the models in Ref.~\cite{Berti:2005ys} are shown in gray and a single residual using a fit for $\cw_{220}$ from \cite{Nagar:2018zoe} is shown as an orange dashed line.}
   %
@@
 here, the sharp feature near $\jf=0$ results from their modeling counter and co-rotating \qnm{} as two different curves.
+A residual error is also shown as an orange dashed line for the $\cw_{220}$ model presented in Ref.~\cite{Nagar:2018zoe}.
+This is a rational model with 14 fitted parameters compared to the polynomial model with 10 fitted parameters defined in \eqn{eq:cw_fit_1}.
+We observe that Ref.~\cite{Nagar:2018zoe} performs better overall while performing worse for higher $\jf$.
 %
@@
 %
-\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature.
+\par \gmvp{} has been applied to the modeling of \qnm{} frequencies.
+The resulting polynomial models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature.
+We note our comparison of $\cw_{220}$ from Ref.~\cite{Nagar:2018zoe} suggests even better fits for $(l,m,n)\neq(2,2,0)$ QNM frequencies might be achievable using a rational ansatz.
+We leave this extension to future modeling work.
 %

### 2019-03-31 docs/mvfits_paper/mvf.tex
Fix Zimmerman citation for asym. deg. [12]

@@
 %
-\par For both the \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.
+\par For both the $(l,m)\neq(2,2)$ \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.
 %
@@
 %
-We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Zimmerman:2015rua}.
+We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Zimmerman:2015trm}.
 %

### 2019-03-31 docs/mvfits_paper/mvf.tex
Add citation for GWTC-1 paper [16]

@@
 %
-In the coming years, expectations for frequent \gw{} detections of increasing \snr{} are high \cite{TheLIGOScientific:2016pea,Abbott:2016nhf}.
+In the coming years, expectations for frequent \gw{} detections of increasing \snr{} are high \cite{TheLIGOScientific:2016pea,Abbott:2016nhf,LIGOScientific:2018mvr}.
 %

### 2019-03-31 docs/mvfits_paper/mvf.tex
Add citation for Mehta et al. (2019) [17]

@@
 %
-\par In this combined context, it is clear that the modeling of \qnm{} frequencies, $\cw\lmn$, and spherical-spheroidal mixing coefficients, $\sigma\LMlmn$, are relevant for a range of \gw{} signal models.
+\par In this combined context, it is clear that the modeling of \qnm{} frequencies, $\cw\lmn$, and spherical-spheroidal mixing coefficients, $\sigma\LMlmn$, are relevant for a range of \gw{} signal models (e.g.
+\cite{Mehta:2019wxm}).
 %

### 2019-03-31 docs/mvfits_paper/mvf.tex
Add EOB+surrogate citations to IMR discussion [19]

@@
 %
-Most prominently, there is ongoing interest in efficient and accurate signal models for \bbh{} \imr{} \cite{Blackman:2017dfb, London:2017bcn, Hannam:2013oca}.
+Most prominently, there is ongoing interest in efficient and accurate signal models for \bbh{} \imr{} \cite{Blackman:2017dfb, London:2017bcn, Hannam:2013oca, Varma:2018mmi, Pan:2013rra, Cotesta:2018fcv}.
 %

### 2019-04-01 docs/mvfits_paper/mvf.tex
Rm Schmidt et al. (2015) modeling citation [20]
Fix typos [11]

@@
 %
-\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq,Khan:2018fmp}.
+\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Mehta:2017jpq,Khan:2018fmp}.
 %
@@
 %
-In section \sec{meth}, we outline the \gmvp{} and \gmvr{} algorithms.
+In \sec{meth}, we outline the \gmvp{} and \gmvr{} algorithms.
 %
@@
 the $L^2$ norm $||\vec{g}^{(0)}-\vec{g}^{(n)}||$) passes a predetermined threshold.
-For \cite{lionel_london_2018_1402516} the following model representation error was used
+For the results presented in \sec{results} the following model representation error was used
 %
@@
   \label{eq:ratvar}
-  \operatorname{Var}\left(\vec{a}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(d_j - \frac{1}{J}\sum_{u=0}^{J}d_u\right)^2
+  \operatorname{Var}\left(\vec{d}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(d_j - \frac{1}{J}\sum_{u=0}^{J}d_u\right)^2
 \end{align}

### 2019-04-01 docs/mvfits_paper/mvf.tex
Reorder role of remnant quantities sentance [21]

@@
 %
-\par Both Phenom and \eob{} approaches either use phenomenological models of remnant \bh{} mass and spin to interpolate over tables of \qnm{} frequencies, or phenomenological models for \qnm{} frequencies are used directly.
+\par Phenomenological models of remnant \bh{} mass and spin are used by both Phenom and \eob{} approaches either to interpolate over tables of \qnm{} frequencies or in the evaluation of phenomenological models for \qnm{} frequencies.
 %

### 2019-04-01 docs/mvfits_paper/mvf.tex
Replace Taylor series statments with S-W [22,23]

@@
 %
-The study of smooth scalar functions (e.g. $f(\vec{x})$) often centers about the Taylor series expansion.
-%
-In that instance, it is clear that any infinitely differentiable scalar function of many variables can be represented in terms of its derivatives by
+The study of continuous scalar functions often centers about their expansion in terms of monomials.
+%
+This is made rigorous by the Generalised Stone-Weierstrass Theorem \cite{Hassani:2013}.
+Consider a continuous function $f(\vec{x}) \equiv f(x_0, x_1, ..., x_N)$ in $N+1$ variables.
+Then $f(\vec{x})$ can be represented as
 %
@@
   \label{eq:mvt}
-  f( \vec{x} + \vec{h} ) &= e^{ \vec{x} \cdot \vec{\nabla}' } \, f(\vec{x}\,') |_{\vec{x}\,'=\vec{h}}
+  f( \vec{x}) &= \sum_{\substack{d_i=0 \\ i \in \{0 \ldots N\}}}^{\infty} c_{d_0 d_1 \ldots d_N} x^{d_0} x^{d_1} \ldots x^{d_N}
   \\ \nonumber
-  &\approx \sum_{k=0}^{K} \, \frac{1}{k!} \, (\vec{x} \cdot \vec{\nabla}')^{k} \, f(\vec{x}\,') |_{\vec{x}\,'=\vec{h}}
-\end{align}
-%
-From the first to second line of \eqn{eq:mvt}, we have used the definition of the exponential function (i.e. its series expansion).
-%
-In the second line, the equality has been replaced by an approximation as we have limited the linear representation to $K+1$ terms.
-%
-\par This latter point is key to the perspective of \gmvp{}:
-%
-given training data thought to be related to a smooth multivariate function, it may, particularly on small scales, be well approximated by a truncated series expansion in an appropriate coordinate basis.
+  &\approx \sum_{\substack{d_i=0 \\ i \in \{0 \ldots N\}}}^{K} c_{d_0 d_1 \ldots d_N} x^{d_0} x^{d_1} \ldots x^{d_N}
+\end{align}
+%
+From the first to second line of \eqn{eq:mvt} the equality has been replaced by an approximation as we have limited the linear representation to monomials with combined exponents no greater than $KN$.
+This implication follows from the Stone-Weierstrass Theorem \cite{Lang:1983} and tells us that a continuous function may be uniformly approximated by a polynomial.
+%
+\par This is key to the perspective of \gmvp{}:
+%
+given training data thought to be related to a continuous multivariate function, it may, particularly on small scales, be well approximated by a polynomial in an appropriate coordinate basis.
 %
@@
 %
-\par \eqn{eq:mvt}'s truncated expansion happens to be a polynomial in at most $N$ variables.
-%
-In this setting, the uncertainty of which and how many basis terms to include makes this a problem ripe for the application of linear modeling driven by a greedy process, namely \eqn{eq:linsol1} and Alg.
+\par In this setting, the uncertainty of which and how many basis terms to include makes this a problem ripe for the application of linear modeling driven by a greedy process, namely \eqn{eq:linsol1} and Alg.
 (\ref{alg:pgreedy}) .

### 2019-04-01 docs/mvfits_paper/mvf.tex
Fix N->N+1 for S-W equation representation [22,23]

@@
 %
-From the first to second line of \eqn{eq:mvt} the equality has been replaced by an approximation as we have limited the linear representation to monomials with combined exponents no greater than $KN$.
+From the first to second line of \eqn{eq:mvt} the equality has been replaced by an approximation as we have limited the linear representation to monomials with combined exponents no greater than $K(N+1)$.
 This implication follows from the Stone-Weierstrass Theorem \cite{Lang:1983} and tells us that a continuous function may be uniformly approximated by a polynomial.

### 2019-04-01 docs/mvfits_paper/mvf.tex
Rephrase polynomial ansatz inapplicability [24]

@@
 %
-\par Despite the apparent universality of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a low order multinomial.
-%
-Worst, in cases where the underlying dataset is best described by a rational function, no polynomial of the same family describing the numerator and denominator will yield satisfactory results in low order.
+\par Despite the apparent universality of \eqn{eq:mvt}, there are many cases where $K$ must be orders of magnitude greater than 1 in order for $\vec{f}$ to be accurately represented by a polynomial.
+%
+Worst, in cases where the underlying dataset is best described by a rational function, a rational model with maximum monomial degree $K$ will typically outperform a polynomial model of maximum degree $K$ with the same number of coefficients as the rational model.
 %

### 2019-04-02 docs/mvfits_paper/mvf.tex
Add note about Berti+Klein fit transformation [26]

--- 2019-04-01 docs/mvfits_paper/mvf.tex
@@
 GMVR is used to develop a model for harmonic mixing coefficients for the dominant multipoles with $\ell \le 5$.
-The models for the mixing coefficients and $(l,m)\neq(2,2)$ QNM frequencies are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes.
+Both models are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes.
 We discuss the potential use of these models in current and future gravitational wave signal modeling.
@@
 %
-In the coming years, expectations for frequent \gw{} detections of increasing \snr{} are high \cite{TheLIGOScientific:2016pea,Abbott:2016nhf,LIGOScientific:2018mvr}.
+In the coming years, expectations for frequent \gw{} detections of increasing \snr{} are high \cite{TheLIGOScientific:2016pea,Abbott:2016nhf}.
 %
@@
 %
-Most prominently, there is ongoing interest in efficient and accurate signal models for \bbh{} \imr{} \cite{Blackman:2017dfb, London:2017bcn, Hannam:2013oca, Varma:2018mmi, Pan:2013rra, Cotesta:2018fcv}.
+Most prominently, there is ongoing interest in efficient and accurate signal models for \bbh{} \imr{} \cite{Blackman:2017dfb, London:2017bcn, Hannam:2013oca}.
 %
@@
 %
-\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Mehta:2017jpq,Khan:2018fmp}.
-%
-\par Phenomenological models of remnant \bh{} mass and spin are used by both Phenom and \eob{} approaches either to interpolate over tables of \qnm{} frequencies or in the evaluation of phenomenological models for \qnm{} frequencies.
+\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq,Khan:2018fmp}.
+%
+\par Both Phenom and \eob{} approaches either use phenomenological models of remnant \bh{} mass and spin to interpolate over tables of \qnm{} frequencies, or phenomenological models for \qnm{} frequencies are used directly.
 %
@@
 %
-\par In this combined context, it is clear that the modeling of \qnm{} frequencies, $\cw\lmn$, and spherical-spheroidal mixing coefficients, $\sigma\LMlmn$, are relevant for a range of \gw{} signal models (e.g.
-\cite{Mehta:2019wxm}).
+\par In this combined context, it is clear that the modeling of \qnm{} frequencies, $\cw\lmn$, and spherical-spheroidal mixing coefficients, $\sigma\LMlmn$, are relevant for a range of \gw{} signal models.
 %
@@
 %
-\par For both the $(l,m)\neq(2,2)$ \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.
+\par For both the \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.
 %
@@
 %
-In \sec{meth}, we outline the \gmvp{} and \gmvr{} algorithms.
+In section \sec{meth}, we outline the \gmvp{} and \gmvr{} algorithms.
 %
@@
 %
-The study of continuous scalar functions often centers about their expansion in terms of monomials.
-%
-This is made rigorous by the Generalised Stone-Weierstrass Theorem \cite{Hassani:2013}.
-Consider a continuous function $f(\vec{x}) \equiv f(x_0, x_1, ..., x_N)$ in $N+1$ variables.
-Then $f(\vec{x})$ can be represented as
+The study of smooth scalar functions (e.g. $f(\vec{x})$) often centers about the Taylor series expansion.
+%
+In that instance, it is clear that any infinitely differentiable scalar function of many variables can be represented in terms of its derivatives by
 %
@@
   \label{eq:mvt}
-  f( \vec{x}) &= \sum_{\substack{d_i=0 \\ i \in \{0 \ldots N\}}}^{\infty} c_{d_0 d_1 \ldots d_N} x^{d_0} x^{d_1} \ldots x^{d_N}
+  f( \vec{x} + \vec{h} ) &= e^{ \vec{x} \cdot \vec{\nabla}' } \, f(\vec{x}\,') |_{\vec{x}\,'=\vec{h}}
   \\ \nonumber
-  &\approx \sum_{\substack{d_i=0 \\ i \in \{0 \ldots N\}}}^{K} c_{d_0 d_1 \ldots d_N} x^{d_0} x^{d_1} \ldots x^{d_N}
-\end{align}
-%
-From the first to second line of \eqn{eq:mvt} the equality has been replaced by an approximation as we have limited the linear representation to monomials with combined exponents no greater than $KN$.
-This implication follows from the Stone-Weierstrass Theorem \cite{Lang:1983} and tells us that a continuous function may be uniformly approximated by a polynomial.
-%
-\par This is key to the perspective of \gmvp{}:
-%
-given training data thought to be related to a continuous multivariate function, it may, particularly on small scales, be well approximated by a polynomial in an appropriate coordinate basis.
+  &\approx \sum_{k=0}^{K} \, \frac{1}{k!} \, (\vec{x} \cdot \vec{\nabla}')^{k} \, f(\vec{x}\,') |_{\vec{x}\,'=\vec{h}}
+\end{align}
+%
+From the first to second line of \eqn{eq:mvt}, we have used the definition of the exponential function (i.e. its series expansion).
+%
+In the second line, the equality has been replaced by an approximation as we have limited the linear representation to $K+1$ terms.
+%
+\par This latter point is key to the perspective of \gmvp{}:
+%
+given training data thought to be related to a smooth multivariate function, it may, particularly on small scales, be well approximated by a truncated series expansion in an appropriate coordinate basis.
 %
@@
 %
-\par In this setting, the uncertainty of which and how many basis terms to include makes this a problem ripe for the application of linear modeling driven by a greedy process, namely \eqn{eq:linsol1} and Alg.
+\par \eqn{eq:mvt}'s truncated expansion happens to be a polynomial in at most $N$ variables.
+%
+In this setting, the uncertainty of which and how many basis terms to include makes this a problem ripe for the application of linear modeling driven by a greedy process, namely \eqn{eq:linsol1} and Alg.
 (\ref{alg:pgreedy}) .
@@
 (Bottom) Percentage absolute residual errors for fits of dimensionless \qnm{} frequencies,, $\cw\lmn$ along with select numerical values (colored markers) computed using Leaver's method \cite{Leaver85}.
-For comparison, residuals using the models in Ref.~\cite{Berti:2005ys} are shown in gray and a single residual using a fit for $\cw_{220}$ from \cite{Nagar:2018zoe} is shown as an orange dashed line.}
+For comparison, residuals using the models in Ref.~\cite{Berti:2005ys} are shown in gray.
+}
   %
@@
 the $L^2$ norm $||\vec{g}^{(0)}-\vec{g}^{(n)}||$) passes a predetermined threshold.
-For the results presented in \sec{results} the following model representation error was used
+For \cite{lionel_london_2018_1402516} the following model representation error was used
 %
@@
   \label{eq:ratvar}
-  \operatorname{Var}\left(\vec{d}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(d_j - \frac{1}{J}\sum_{u=0}^{J}d_u\right)^2
+  \operatorname{Var}\left(\vec{a}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(d_j - \frac{1}{J}\sum_{u=0}^{J}d_u\right)^2
 \end{align}
@@
 %
-We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Zimmerman:2015trm}.
+We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Zimmerman:2015rua}.
 %
@@
 here, the sharp feature near $\jf=0$ results from their modeling counter and co-rotating \qnm{} as two different curves.
-A residual error is also shown as an orange dashed line for the $\cw_{220}$ model presented in Ref.~\cite{Nagar:2018zoe}.
-This is a rational model with 14 fitted parameters compared to the polynomial model with 10 fitted parameters defined in \eqn{eq:cw_fit_1}.
-We observe that Ref.~\cite{Nagar:2018zoe} performs better overall while performing worse for higher $\jf$.
 %
@@
 %
-\par \gmvp{} has been applied to the modeling of \qnm{} frequencies.
-The resulting polynomial models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature.
-We note our comparison of $\cw_{220}$ from Ref.~\cite{Nagar:2018zoe} suggests even better fits for $(l,m,n)\neq(2,2,0)$ QNM frequencies might be achievable using a rational ansatz.
-We leave this extension to future modeling work.
+\par \gmvp{} has been applied to the modeling of \qnm{} frequencies. The resulting models have been constrained in the extremal Kerr limit, and perform well compared to similar fits in the literature.
 %

### 2019-04-02 docs/mvfits_paper/mvf.tex
Remove QNM first of kind claim from abstract [15]

--- 2019-04-01 docs/mvfits_paper/mvf.tex
@@
 GMVR is used to develop a model for harmonic mixing coefficients for the dominant multipoles with $\ell \le 5$.
-The models for the mixing coefficients and $(l,m)\neq(2,2)$ QNM frequencies are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes.
+The models for the mixing coefficients are the first of their kind to consider black hole spin to vary between -1 and 1, thus naturally connecting the pro and retrograde modes.
 We discuss the potential use of these models in current and future gravitational wave signal modeling.
@@
 For comparison, residual errors for the fits in Ref.~\cite{Berti:2014fga} are also shown over their region of validity in \bh{} spin.
-Note that markers match between grey and colored data points.
-}
+Note that markers match between grey and colored data points and the fits in Ref.~\cite{Berti:2014fga} are conjugated and multiplied by $(-1)^{\bar{l}+l}$ to correct for the different choice of spherical harmonic conventions.}
   %

### 2019-04-02 docs/mvfits_paper/mvf.tex
Up text describing Nagar et al. (2018) comp [15]

@@
 %
-\par For both the $(l,m)\neq(2,2)$ \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.
+\par For $(l,m)\neq(2,2)$ \qnm{} frequencies and the spherical-sphoidal mixing coefficients, we present the first models which treat \qnm{s} rotating with and against the rotation of the \bh{} as being a part of a single solution parameterized by dimensionless \bh{} spin ranging from -1 to 1.
 %
@@
 A residual error is also shown as an orange dashed line for the $\cw_{220}$ model presented in Ref.~\cite{Nagar:2018zoe}.
-This is a rational model with 14 fitted parameters compared to the polynomial model with 10 fitted parameters defined in \eqn{eq:cw_fit_1}.
-We observe that Ref.~\cite{Nagar:2018zoe} performs better overall while performing worse for higher $\jf$.
+We observe that the rational model of Ref.~\cite{Nagar:2018zoe} performs better overall while performing worse for higher $\jf$ compared to our model.
+While we use a polynomial ansatz, the comparison with Ref.~\cite{Nagar:2018zoe} highlights the potential of rational ansatzes.
 %
@@
 We note our comparison of $\cw_{220}$ from Ref.~\cite{Nagar:2018zoe} suggests even better fits for $(l,m,n)\neq(2,2,0)$ QNM frequencies might be achievable using a rational ansatz.
-We leave this extension to future modeling work.
+This is a possible avenue for future improvement.
 %

### 2019-04-02 docs/mvfits_paper/mvf.tex
Reintroduce Schmidt et al (2015) [20]
Update def of rep. error. used for results [11]

--- 2019-04-02 docs/mvfits_paper/mvf.tex
@@
 %
-\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Mehta:2017jpq,Khan:2018fmp}.
+\cite{Hannam:2013oca, London:2017bcn, Khan:2015jqa, Schmidt:2014iyl, Mehta:2017jpq,Khan:2018fmp}.
 %
@@
 %
-where $\operatorname{Var}$ is the variance defined for a vector $\vec{d} = (d_j)$ as
-%
-\begin{align}
-  \label{eq:ratvar}
-  \operatorname{Var}\left(\vec{d}\right)  = \frac{1}{J}\sum_{j=0}^{J}\left(d_j - \frac{1}{J}\sum_{u=0}^{J}d_u\right)^2
-\end{align}
-%
+where $\operatorname{Var}$ is the variance. This model representation error is similar to the square of the root-mean-squared-deviation normalized by the variance of the data set.
 % \hspace{1cm}

### 2019-04-04 docs/mvfits_paper/mvf.tex
Specifying how training data are computed; ie Leaver

@@
 %
-Worst, in cases where the underlying dataset is best described by a rational function, a rational model with maximum monomial degree $K$ will typically outperform a polynomial model of maximum degree $K$ with the same number of coefficients as the rational model.
-%
 In general, the optimal polynomial basis may not be clear, and so a more general set of ansatzes may be of use.
@@
 %
-\eqns{eq:cw_fit_1}{eq:cw_fit_9} display the resulting polynomial models.
+\eqns{eq:cw_fit_1}{eq:cw_fit_9} display the resulting polynomial models to numerical results of Leaver's method~\cite{Leaver85}.
 %
@@
 %
-\par \fig{fig:ys} displays fits, training data and related residuals.
+\par \fig{fig:ys} displays fits, training data and related residuals. The training data were compute using Leaver's representation for the spheroidal harmonics to evaluate \eqn{sigma}.
 %

### 2019-04-04 docs/mvfits_paper/mvf.tex
adding short statement to further explain physical meaning of negative spin QNMs
Tightening discussion of QNMs as good approx for ringdown

@@
 %
-Following the usual treatment, these solutions allow \grad{} from a perturbed Kerr BH at sufficiently late times to be approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with spheroidal harmonics, $_{-2}S\lmn$, of spin weight -2.
+These solutions allow \grad{} from a perturbed Kerr BH at sufficiently late times to be approximated by a spectral (multipolar) sum which combines the complex \qnm{} amplitude, $A\lmn$, with spheroidal harmonics, $_{-2}S\lmn$, of spin weight -2.
 %
@@
 This perspective reflects the empirical observation that the remnant spin of \bbh{} mergers smoothly connects regions of positive and negative spin relative to the direction of the initial orbital angular momentum \cite{Husa:2015iqa,London:2018gaq}.
+%
+Outside of \bbh{} mergers, these negative spin \qnm{s} generally correspond to perturbations that are counter-rotating relative to the \bh{} spin.
 %

### 2019-04-04 setup.py
Bump version

@@ -11,7 +11,7 @@ with open('README.md', 'r') as f:
 #
 setup(
     name='positive',
-    version='0.1.0',
+    version='0.2.0',
     description='Low level python API for NR+LIGO packages.',
     long_description=readme,
     long_description_content_type='text/markdown',

### 2019-04-09 docs/mvfits_paper/mvf.tex
clarifying 4th vs 5th order polynomials for QNM fitting

@@
   \begin{tabular}{ll}
-    {\includegraphics[width=0.49\textwidth]{fits_w.pdf}} & {\includegraphics[width=0.49\textwidth]{fits_tau.pdf}}
+    {\includegraphics[width=0.49\textwidth,trim={0 0.2in 0 0.4in},clip]{fits_w.pdf}} & {\includegraphics[width=0.49\textwidth,trim={0 0.2in 0 0.4in},clip]{fits_tau.pdf}}
     % \\
@@
     \\
-    \hspace{0.35cm}\includegraphics[width=0.43\textwidth]{res_cw_0.pdf} & \hspace{0.3cm}\includegraphics[width=0.43\textwidth]{res_cw_1.pdf}
+    {\includegraphics[width=0.49\textwidth,trim={0 0.25in 0 0.9in},clip]{res_cw_0.pdf}} & {\includegraphics[width=0.49\textwidth,trim={0 0.25in 0 0.9in},clip]{res_cw_1.pdf}}
   \end{tabular}
@@
 In particular, the domain map allows most \qnm{} frequencies to be well modeled by 5th order polynomials which include all lower degree terms; concurrently, the real and imaginary parts of each $\cw\lmn$ are modeled simultaneously.
+%
+For the zero-damped \qnm{s}, we note that 4th order polynomials were actually modeled, with the remaining power of $\kappa$ resulting from explicit enforcement of the zero-damped condition.
 %

### 2019-04-09 docs/mvfits_paper/mvf.tex
Mixing Talor series argument with Generalised Stone-Weierstrass Theorem

@@
 %
-The study of continuous scalar functions often centers about their expansion in terms of monomials.
-%
-This is made rigorous by the Generalised Stone-Weierstrass Theorem \cite{Hassani:2013}.
-Consider a continuous function $f(\vec{x}) \equiv f(x_0, x_1, ..., x_N)$ in $N+1$ variables.
-Then $f(\vec{x})$ can be represented as
+The study of continuous scalar functions often centers about their Taylor series expansion.
+%
+In that instance, it is clear that any infinitely differentiable scalar function of many variables can be represented in terms of its derivatives by
 %
@@
   \label{eq:mvt}
-  f( \vec{x}) &= \sum_{\substack{d_i=0 \\ i \in \{0 \ldots N\}}}^{\infty} c_{d_0 d_1 \ldots d_N} x^{d_0} x^{d_1} \ldots x^{d_N}
+  f( \vec{x} + \vec{h} ) &= e^{ \vec{x} \cdot \vec{\nabla}' } \, f(\vec{x}\,') |_{\vec{x}\,'=\vec{h}}
   \\ \nonumber
-  &\approx \sum_{\substack{d_i=0 \\ i \in \{0 \ldots N\}}}^{K} c_{d_0 d_1 \ldots d_N} x^{d_0} x^{d_1} \ldots x^{d_N}
-\end{align}
-%
-From the first to second line of \eqn{eq:mvt} the equality has been replaced by an approximation as we have limited the linear representation to monomials with combined exponents no greater than $K(N+1)$.
-This implication follows from the Stone-Weierstrass Theorem \cite{Lang:1983} and tells us that a continuous function may be uniformly approximated by a polynomial.
-%
-\par This is key to the perspective of \gmvp{}:
-%
-given training data thought to be related to a continuous multivariate function, it may, particularly on small scales, be well approximated by a polynomial in an appropriate coordinate basis.
+  &\approx \sum_{k=0}^{K} \, \frac{1}{k!} \, (\vec{x} \cdot \vec{\nabla}')^{k} \, f(\vec{x}\,') |_{\vec{x}\,'=\vec{h}}
+\end{align}
+%
+From the first to second line of \eqn{eq:mvt}, we have used the definition of the exponential function (i.e. its series expansion).
+%
+In the second line, the equality has been replaced by an approximation as we have limited the linear representation to $K+1$ terms.
+%
+Formally, the applicability of the truncated expansion over a local region is made rigorous by the Generalised Stone-Weierstrass Theorem \cite{Hassani:2013}.
+%
+\par These ideas are key to the perspective of \gmvp{}:
+%
+given training data thought to be related to a smooth multivariate function, it may, particularly on small scales, be well approximated by a truncated series expansion in an appropriate coordinate basis.
+%
 %

### 2019-05-06 positive/physics.py
adding new models for QNM frequencies of Kerr, adding functions for Kerr Light-Ring and ISCO radii and frequencies

@@ -27,6 +27,121 @@ def rISCO_14067295(a):
     return 3+z2 - np.sqrt((3.0-z1)*(3.0+z1+2.0*z2))*a_sign
 
 
+# Calculate Kerr ISCO Radius
+def rKerr_ISCO_Bardeen(j,M=1):
+    '''
+
+    Calculate Kerr ISCO Radius
+
+    USAGE:
+    rKerr_ISCO_Bardeen(Dimensionless_BH_Spin,BH_Mass)
+
+    ~ londonl@mit.edu
+
+    '''
+
+    #
+    from numpy import sign,sqrt
+
+    #
+    a = M*j
+
+    #
+    p13 = 1.0/3
+    jj = j*j
+
+    #
+    Z1 = 1 + ( 1-jj )**p13 * ( (1+j)**p13 + (1-j)**p13 )
+    Z2 = sqrt( 3*jj + Z1*Z1 )
+
+    #
+    rKerr_ISCO = M * (  3 + Z2 - sign(j) * sqrt( (3-Z1)*(3+Z1+2*Z2) )  )
+
+    #
+    return rKerr_ISCO
+
+
+# Calculate Kerr ISCO Angular Frequency
+def wKerr_ISCO_Bardeen(j,M=1):
+    '''
+
+    Calculate Kerr ISCO Angular Frequency
+
+    USAGE:
+    wKerr_ISCO_Bardeen(Dimensionless_BH_Spin,BH_Mass=1)
+
+    ~ londonl@mit.edu
+
+    '''
+
+    #
+    from numpy import sin,sign,sqrt
+
+    #
+    a = M*j
+
+    # Bardeen et al 2.21, Ori Thorn 2.5
+    r = M * rKerr_ISCO_Bardeen(j,M=M) # rISCO_14067295(j)
+
+    # 2.16 of Bardeen et al, ( 2.1 of Ori Thorn misses physics )
+    wKerr_ISCO = sqrt(M) / ( r**(3.0/2) + a*sqrt(M) )
+
+    # Return Answer
+    return wKerr_ISCO
+
+
+# Calculate Kerr Light-Ring Radius
+def rKerr_LR_Bardeen(j,M=1):
+    '''
+
+    Calculate Kerr Light-Ring Radius
+
+    USAGE:
+    rKerr_LR_Bardeen(Dimensionless_BH_Spin,BH_Mass)
+
+    ~ londonl@mit.edu
+
+    '''
+
+    #
[…]

### 2019-06-25 docs/mvfits_paper/mvf.tex
adding new models for QNM frequencies of Kerr, adding functions for Kerr Light-Ring and ISCO radii and frequencies
adding reference for ysmodel training data
moving citation of LIGO systematics paper

@@
 %
-In this context, signal detection and subsequent inference of physical parameters hinges upon efficient models for source properties and dynamics \cite{Abbott:2016wiq}.
+In this context, signal detection and subsequent inference of physical parameters hinges upon efficient models for source properties and dynamics \cite{Abbott:2016wiq,TheLIGOScientific:2016wfe}.
 %
@@
 %
-As the merger of isolated \bh{s} is expected to result in a perturbed Kerr \bh{}, there is related interest in having accurate and computationally efficient models for perturbative parameters, namely those that enable evaluation of the related \rd{} radiation \cite{Berti:2005ys,TheLIGOScientific:2016wfe}.
+As the merger of isolated \bh{s} is expected to result in a perturbed Kerr \bh{}, there is related interest in having accurate and computationally efficient models for perturbative parameters, namely those that enable evaluation of the related \rd{} radiation \cite{Berti:2005ys}.
 %
@@
 %
+We note that the related training data is available online at reference~\cite{ys_training_data}.
+%
 %
@@
 % \bibliographystyle{ieeetr}
-\bibliographystyle{mnras}
+% \bibliographystyle{mnras}
 \bibliography{mvf.bib}

### 2019-06-25 docs/mvfits_paper/mvf.tex
adding Yang:2012pj ref near mention of asymptotic degeneracy

@@
 %
-We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Zimmerman:2015trm}.
+We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Yang:2012pj,Zimmerman:2015trm}.
 %

### 2019-06-25 docs/mvfits_paper/mvf.tex
adding Yang:2012he ref near mention of asymptotic degeneracy

--- 2019-06-25 docs/mvfits_paper/mvf.tex
@@
 %
-We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Zimmerman:2015trm}.
+We note that, in the asymptotic vicinity of $\jf=1$, the \qnm{} frequencies and decay times are known to have solutions that are asymptoticly degenerate \cite{Yang:2012he,Zimmerman:2015trm}.
 %

### 2019-07-01 docs/mvfits_paper/mvf.tex
refining leaver_needle and related code

@@
   Models of black hole properties play an important role in the ongoing direct detection of gravitational waves from black hole binaries.
-One important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, are the low level modeling of information related to perturbed Kerr black holes.
+One important aspect of model based gravitational wave detection, and subsequent estimation of source parameters, is the low level modeling of information related to perturbed Kerr black holes.
 Here, we present new phenomenological methods to model the analytically understood gravitational wave spectra (quasi-normal mode frequencies), and harmonic structure of Kerr black holes (mixing coefficients between spherical and spheroidal harmonics).
@@
   %
-	\caption{ Spherical-spheroidal harmonic mixing coefficients and percentage residual errors for spherical-spheroidal harmonic mixing coefficient fits.
+	\caption{ Spherical-spheroidal harmonic mixing coefficients and percentage residual errors for spherical-spheroidal harmonic mixing coefficient fits made using the training data in Ref.~\cite{ys_training_data}.
 (\textit{Top Left}) Mixing coefficients for cases where $(\bar{\ell},\bar{m})=(\ell,m)$.

### 2019-07-01 positive/physics.py

@@ -3834,7 +3834,7 @@ def lvrsolve(jf,l,m,guess,tol=1e-8):
 
 
 # Extrapolative guess for gravitational perturbations. This function is best used within leaver_needle which solves leaver's equations for a range of spin values.
-def leaver_extrap_guess( j, cw, sc, l, m, tol = 1e-3, d2j = 1e-6, step_sign = 1, verbose=False, plot=False ):
+def leaver_extrap_guess( j, cw, sc, l, m, tol = 1e-3, d2j = 1e-6, step_sign = 1, verbose=False, plot=False, spline_order=3, monotomic_steps=False, boundary_spin=None ):
 
     '''
     Extrapolative guess for gravitational perturbations. This function is best used within leaver_needle which solves leaver's equations for a range of spin values.
@@ -3843,7 +3843,7 @@ def leaver_extrap_guess( j, cw, sc, l, m, tol = 1e-3, d2j = 1e-6, step_sign = 1,
     '''
 
     #
-    from numpy import complex128,polyfit,linalg,ndarray,array,linspace,polyval,diff,sign,ones_like,linalg
+    from numpy import complex128,polyfit,linalg,ndarray,array,linspace,polyval,diff,sign,ones_like,linalg, hstack
     if plot: from matplotlib.pyplot import figure,show,plot,xlim
     from scipy.interpolate import InterpolatedUnivariateSpline as spline
 
@@ -3873,14 +3873,17 @@ def leaver_extrap_guess( j, cw, sc, l, m, tol = 1e-3, d2j = 1e-6, step_sign = 1,
     # print current_err
     if current_err>tol:
         print j
+        print current_j
         print initial_solution
         print current_err
         error('Initial solution does not satisfy the input tolerance value.')
 
     # Determine the polynomial order to use based on the total number of points
     nn = len(j)
-    order = min(nn-1,3) # NOTE that 4 and 5 don't work as well, especially near extremal values of spin
+    order = min( nn-1, spline_order ) # NOTE that 4 and 5 don't work as well, especially near extremal values of spin; 3may also have problems
     place = -order-1
+    # if m<0: tol *= 1e-4
+    # print 'm,tol = ',m,tol
     # print 'nn,order,place = ',nn,order,place
 
     xx = array(j)[place:]
[…]

### 2019-07-31 positive/physics.py
updating bib for mvfits paper

@@ -1673,14 +1673,31 @@ def leaver( jf,                     # Dimensionless BH Spin
             Mf = 1.0,               # BH mass. NOTE that the default value of 1 is consistent with the tabulated data. (Geometric units ~ M_bare / M_ADM )
             verbose = False ):      # Toggle to be verbose
 
+    #
+    from numpy import ndarray,array
+
+    #
+    if isinstance(jf,(tuple,list,ndarray)):
+        #
+     cw,sc = array( [ __leaver_helper__(jf_, l, m, n, p , s, Mf, verbose) for jf_ in jf ] )[:,:,0].T
+     return cw,sc
+    else:
+        #
+        return __leaver_helper__(jf, l, m, n, p , s, Mf, verbose)
+
+
+def __leaver_helper__( jf, l, m, n =  0, p = None, s = -2, Mf = 1.0, verbose = False):
+
+
     # Import useful things
     import os
     from scipy.interpolate import InterpolatedUnivariateSpline as spline
-    from numpy import loadtxt,exp,sign,abs
+    from numpy import loadtxt,exp,sign,abs,ndarray,array
     from numpy.linalg import norm
 
     # Validate jf input: case of int given, make float. NOTE that there is further validation below.
-    if isinstance(jf,int): jf = float(jf)
+    if isinstance(jf,(int,float)): jf = [float(jf)]
+    if not isinstance(jf,ndarray): jf = array(jf)
     # Valudate s input
     if abs(s) != 2: raise ValueError('This function currently handles on cases with |s|=2, but s=%i was given.'%s)
     # Validate l input
@@ -1690,7 +1707,7 @@ def leaver( jf,                     # Dimensionless BH Spin
     # Define a parity value to be used later:
     # NOTE that is p>0, then the corotating branch will be loaded, else if p<0, then the counter-rotating solution branch will be loaded.
     if p is None:
-        p = sign(jf) + int( jf==0 )
+        p = sign(jf) + ( jf==0 )
     # NOTE that the norm of the spin input will be used to interpolate the data as the numerical data was mapped according to jf>=0
     # Given l,m,n,sign(jf) create a RELATIVE file string from which to load the data
     cmd = parent(os.path.realpath(__file__))
@@ -1709,12 +1726,12 @@ def leaver( jf,                     # Dimensionless BH Spin
     # Extract spin, frequencies and separation constants
     JF = data[:,0]
[…]

### 2019-09-21 positive/maths.py
updates to kerr QNM freq workflows to generalize s

@@ -5,9 +5,65 @@ from positive import *
 from scipy.misc import factorial
 
 
+'''
+Useful Method for estimating QNM locations in leaver solution space: Estimate the
+local minima of a 2D array
+'''
+def localmins(arr,edge_ignore=False):
+
+    import numpy as np
+    import scipy.ndimage.filters as filters
+    import scipy.ndimage.morphology as morphology
+
+    # http://stackoverflow.com/questions/3684484/peak-detection-in-a-2d-array/3689710#3689710
+    """
+    Takes an array and detects the troughs using the local maximum filter.
+    Returns a boolean mask of the troughs (i.e. 1 when
+    the pixel's value is the neighborhood maximum, 0 otherwise)
+    """
+    # define an connected neighborhood
+    # http://www.scipy.org/doc/api_docs/SciPy.ndimage.morphology.html#generate_binary_structure
+    neighborhood = morphology.generate_binary_structure(len(arr.shape),2)
+    # apply the local minimum filter; all locations of minimum value
+    # in their neighborhood are set to 1
+    # http://www.scipy.org/doc/api_docs/SciPy.ndimage.filters.html#minimum_filter
+    local_min = (filters.minimum_filter(arr, footprint=neighborhood)==arr)
+    # local_min is a mask that contains the peaks we are
+    # looking for, but also the background.
+    # In order to isolate the peaks we must remove the background from the mask.
+    #
+    # we create the mask of the background
+    background = (arr==0)
+    #
+    # a little technicality: we must erode the background in order to
+    # successfully subtract it from local_min, otherwise a line will
+    # appear along the background border (artifact of the local minimum filter)
+    # http://www.scipy.org/doc/api_docs/SciPy.ndimage.morphology.html#binary_erosion
+    eroded_background = morphology.binary_erosion(
+        background, structure=neighborhood, border_value=1)
+    #
+    # we obtain the final mask, containing only peaks,
+    # by removing the background from the local_min mask
+    detected_minima = local_min ^ eroded_background
+    # detected_minima = local_min - eroded_background
+    __localmin__ =  list( np.where(detected_minima) )
+
+    # Option: Ignore mins on domain boundaries
+    if edge_ignore:
+        isonedge0 =  lambda x: (x==0) or (x==(len(arr[:,0])-1))
[…]

### 2019-09-21 positive/physics.py

@@ -2245,13 +2245,20 @@ def mass_ratio_convention_sort(m1,m2,chi1,chi2):
 
 # Equation 27 of Leaver '86
 # Characteristic Eqn for Spheroidal Radial Functions
-def leaver27( a, l, m, w, A, s=-2.0, vec=False, mpm=False, **kwargs ):
+def leaver27( a, l, m, w, A, s=-2.0, vec=False, mpm=False, adjoint=False, tol=1e-10, **kwargs ):
 
     '''
     Equation 27 of Leaver '86
     Characteristic Eqn for Spheroidal Radial Functions
     - LLondon
     '''
+
+    from numpy import complex256 as dtyp
+
+    # Enforce Data Type
+    a = dtyp(a)
+    w = dtyp(w)
+    A = dtyp(A)
 
     #
     pmax = 5e2
@@ -2262,7 +2269,7 @@ def leaver27( a, l, m, w, A, s=-2.0, vec=False, mpm=False, **kwargs ):
     else:
         from numpy import sqrt
 
-    global c0, c1, c2, c3, c4, Alpha, Beta, Gamma, l_min
+    # global c0, c1, c2, c3, c4, Alpha, Beta, Gamma, l_min
 
     #
     l_min = l-max(abs(m),abs(s)) # VERY IMPORTANT
@@ -2282,6 +2289,10 @@ def leaver27( a, l, m, w, A, s=-2.0, vec=False, mpm=False, **kwargs ):
                     + (2.0+b)*1j*w - A + ((4.0*w+2.0j)/b) * c_param
     c4    =         s + 1.0 - 2.0*w*w - (2.0*s+3.0)*1j*w - ((4.0*w+2.0*1j)/b)*c_param
 
+    # If the related equations for the adjoint radial operator are requested, take conjugates
+    if adjoint:
+        c0,c1,c2,c3,c4 = [ q.conj() for q in (c0,c1,c2,c3,c4) ]
+
     Alpha = lambda k:	k*k + (c0+1)*k + c0
     Beta  = lambda k:   -2.0*k*k + (c1+2.0)*k + c3
     Gamma = lambda k:	k*k + (c2-3.0)*k + c4 - c2 + 2.0
@@ -2294,7 +2305,7 @@ def leaver27( a, l, m, w, A, s=-2.0, vec=False, mpm=False, **kwargs ):
     #
[…]

### 2019-09-21 positive/physics.py
importing mkdir into leaver_workflow subroutine

@@ -4562,6 +4562,9 @@ class leaver_solve_workflow:
     #
     def __validate_inputs__( this, initial_spin, final_spin, l, m, tol, verbose, basedir, box_xywh, max_overtone, output, plot, initial_box_res, spline_order, s ):
 
+        #
+        from positive import mkdir
+
         # Save inputs as properties of the current object
         alert('Found inputs:',verbose=verbose)
         for k in dir():

### 2019-09-21 positive/physics.py
minor refinements to leaver workflow

@@ -3131,7 +3131,6 @@ class cwbox:
                              this.center[1]+this.height/2.0])     # imag max
         this.wr_range = linspace( this.limit[0], this.limit[1], res )
         this.wc_range = linspace( this.limit[2], this.limit[3], res )
-        print 'wc_range limits = ',lim(this.wc_range)
         # Set patch object for plotting. NOTE the negative sign exists here per convention
         if None is pec: pec = 'k'
         this.patch = patches.Rectangle( (min(this.limit[0:2]), min(-this.limit[2:4]) ), this.width, this.height, fill=False, edgecolor=pec, alpha=0.4, linestyle='dotted' )
@@ -4516,7 +4515,7 @@ class leaver_solve_workflow:
         #
         j,cw,sc,err,retry = leaver_needle( this.initial_spin, this.final_spin, l,abs(m), initial_solution, tol=this.tol*exp(-n), verbose=this.verbose, spline_order=this.spline_order, s=this.s )
         #
-        j,cw,sc,err,retry = greedy_leaver_needle( j,cw,sc,err,retry, l, abs(m), plot = False, verbose=False, spline_order=this.spline_order, s=this.s )
+        # j,cw,sc,err,retry = greedy_leaver_needle( j,cw,sc,err,retry, l, abs(m), plot = False, verbose=False, spline_order=this.spline_order, s=this.s )
         #
         this.results[z]['j'],this.results[z]['cw'],this.results[z]['sc'],this.results[z]['err'],this.results[z]['retry'] = j,cw,sc,err,retry
 
@@ -4524,7 +4523,7 @@ class leaver_solve_workflow:
         # Calculate the error of the resulting spline model between the boundaries
         # ------------------------------------------------------------ #
         alert('Calculating the error of the resulting spline model between the boundaries',verbose=this.verbose)
-        lvrwrk = lambda J,STATE: linalg.norm(  leaver_workfunction( J,l,abs(m),STATE )  )
+        lvrwrk = lambda J,STATE: linalg.norm(  leaver_workfunction( J,l,abs(m),STATE,s=this.s )  )
         js = linspace(min(j),max(j),1e3)
         cwrspl = spline(j,cw.real,k=this.spline_order)
         cwcspl = spline(j,cw.imag,k=this.spline_order)
@@ -4562,9 +4561,6 @@ class leaver_solve_workflow:
     #
[…]

### 2019-09-21 positive/physics.py
commenting out frame plotting in leaver_workflow

@@ -4364,8 +4364,8 @@ class leaver_solve_workflow:
         # ------------------------------------------------------------ #
         # Plot the QNM solution space at an initial spin value
         # ------------------------------------------------------------ #
-        alert('Plotting 2D start frame',verbose=this.verbose,header=True)
-        if this.plot: this.__plot2Dframe__()
+        # alert('Plotting 2D start frame',verbose=this.verbose,header=True)
+        # if this.plot: this.__plot2Dframe__()
 
         #
         if not initialize_only:
